\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{and-so-we-make-an-end.html}{And So We Make An End}}
First Published: 2018 December 13
\section{Draft 1}
For those of you who are unaware, last spring Grinnell College's Collegium Musicum\footnote{early music group} performed a piece entitled \say{The Cries of London.}
As the piece comes to a close, each of the independent parts begins singing \say{and so we make an end,} until the entire group is singing it, and then the piece ends.
Only partially because of the title, I'm feeling that song as extremely relevant to me right now.

Last night at diving, I had to say goodbye to the wonderful and amazing people I've met at diving this semester.
They expressed sadness that I would be gone, and assured me I'd be back soon.\footnote{one of them commented that they've felt much more comfortable wiping out since I showed up which was a little less nice but}
A couple of them shared contact information with me, so maybe we'll stay in touch.

Today, I took my final at Queen Mary.
It was\footnote{is} worth all of my grade in the class, so I hope I did well.

Today, I also had my last class of the semester.
And, as I write this document, I've just finished packing\footnote{most of} my stuff into its suitcase.
Oddly, other than the pile of books I'm going to have to fit into my backpack, I don't appear to have gained many things.
It's also odd because it only took around 45 minutes to pack all of my belongings.
In contrast, it took around 3 hours to pack and remove all of the items from my room last semester.
But, my semester here is coming to an end.
Potentially never again will I be in London, and almost certainly never again will I be living here.
I'm excited to be home, if only so that the next phase of my life begins.

As this page in my\footnote{both metaphorical and literal} journal turns over, I begin a new one.
In fact, I'm going to look at my first few posts, to see if there's anything that I thought about then that I'm thinking about now.

In my journal, I mentioned that I would miss seeing some friends.\footnote{and obviously my family}
I'm certainly excited to see them, especially since some of them will be abroad in the spring.

On my \href{hello-world.html}{first post}, I said that I would be sharing \say{updates about travel, my life abroad, and whatever else happens to be on my mind when I sit down to write.}
I certainly did some of those, whether the reviews of shows that I saw, the places I went to,\footnote{sometimes} or the random things I wrote about.

In \href{first-56-hours.html}{my second post}, I said that \say{London feels a lot like Grinnell so far,} and that's still certainly true.
Of the six points mentioned, the first is still somewhat true, though I've learned how to use Google Maps without data, the second I've managed to avoid doing again.
I've still only heard bagpipes twice and only seen them once.
London weather is now\footnote{apparently} far warmer than Grinnell, so I debate wearing a jacket some days.
I was able to find a Catholic church.\footnote{well, two churches}
Finally, underground is still easy, buses are still magic that takes you from a-b.

My \href{street-music-in-london}{third} post\footnote{yes I intentionally hrefed them all differently} deals with street music, and I've lately seen far more accordions.
I take that as a sign that I'm really supposed to learn them next semester.
Also, tonight as I left the end of semester dinner, there were two guys walking around playing Christmas carols on the alto saxophone, which was nice.
I was a public musician once, which was when we were on a train coming home and had a long stop at a station.
Some train employees came and listened and said they appreciated it when I finished, which was nice.

Finally, my fourth \href{how-im-keeping-track-of-my-time-abroad.html}{post} deals with how I thought I would journal.
I said I'd be on social media a lot, which was true.
I stopped updating Facebook about this, mostly because I stopped being proud of what I'd written.
I managed to\footnote{with one exception} do this daily.
And, I did continue the hybrid journal.
As a printed document, the digital portion was around 100 double sided pages, and the analog one is currently around 120 pages.
So, that's nice to know.
I also continued to have more free time than I wanted, which was kind of nice.
I needed time to destress and decompress, if only from city life, and had that chance.
That meant that I may not have made it to every single concert or museum that I could've gone to, but I'm ok with that, especially since I've never really loved museums.\footnote{I could write about that sometime}

So yeah, while I'm not headed home just yet,\footnote{my amazing older brother came to visit and we're going exploring!} I am done with the Grinnell in London program, and that feels nice.
\end{document}