\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{atonal-precomposition-2.html}{Atonal Preomposition, Chord Progressions}}
First Published: 2018 December 18

Prereading note: If you look at the html, you may notice that this is labeled \say{2.}
There is a first essay about this, but it's nearly 2000 words and needs some cleaning.
It'll be good for a day I don't feel like writing
\section{Draft 1}
Yesterday, my brother and I were eating together.
While doing so, I flipped through my notebook, because he and I were bored.
I saw that I had made a map of all 24 major and minor chords, connected by the movements of a single note in a triad.\footnote{so, Am can become CM (A-G), FM (E-F) or AM (C-C\#)}
I was wondering if there was a better way to represent it than the interlocking circle I'd made.
While the answer appears to be no,\footnote{or at least without 3 dimensions} it still sparked an idea.

Today, we\footnote{loosely using \say{we} here} made a program to auto-generate a chord progression that moves along the three valid Neo-Riemannian steps, P,R, and L.
As is often the case, none of the code in the initial working model ended up in the final.
Using the input of the beginning chord and desired number of changes, it pseudo\footnote{I assume}-randomly\footnote{I observed and was told} generates a progression.
One example that I just generated, using 25 chords from CM is: CM->Cm->EbM->Cm->CM->Am->CM->Am->CM->Am->CM->Cm->AbM->Abm->AbM->Abm->AbM->Abm/G\#m->EM->Em->GM->Gm->EbM->Ebm->EbM.
If you'd like to hear what that sounds like as generated by a midi keyboard, or if you'd like to try the program yourself, feel free to mail me at \mailto{flyingrebelpipes@gmail.com}{flyingrebelpipes@gmail.com}.
\end{document}