\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{bad-ideas.html}{Bad Ideas}}
First Published: 2022 March 5


\section{Draft 1}
\href{quick-post}{Yesterday} I mentioned that I had an idea for the blog post today.
As is too often the case, the ideas I had late at night while half asleep didn't seem so nice in the light of day.

I was going to blog about, as mentioned bagpipes in funerals, which is a thought that I've had for a few years.
As I started to talk my way through the post, though\footnote{If this isn't how you write I have questions} I realized that the way I wanted to express the idea in many respects cheapened the idea.
So, instead I get to meta-blog about how I write nowadays.

I was finding this week that I lacked the motivation and direction to keep writing my story.
For a few days I thought it might be that I was just tired of writing, but as I started this weekend, I realized it's that I haven't given my mind time to process the story.

I spent about half an hour before bed two nights ago thinking about where the story could go, and when I went to write the story again, the words started flowing out.
I guess it's a good reminder that my mind needs time to sit and think without external stimuli, or at least without mental stimuli.
Walking without music or praying has also worked for me, as does driving without music.
In the future I should try scheduling more time for silent thought.
\end{document}