\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{bagels-23.html}{Bagels!}}
First Published: 2023 November 23
\section{Draft 1 (22 Nov)}
I'm writing this post tonight, but I know that I won't get around to posting it until the morning.
On the bright side, that means that I can write a second draft of it.
Today, for the first time since starting the family tradition of Thanksgiving bagels, I made the dough before the morning of.
I don't know if that will end up being a good idea, but I'm glad that I no longer have to start waking up at 3 in the morning to begin all the prep work for the morning, especially since Thanksgiving is always a long day.

This year's attempt at bagels included potato starch, bread flour, and vital gluten, which made for a very springy dough.
I'm excited to see what it becomes.

Daily Reflection:
\begin{itemize}
\item Did I write 1700 words for NaNoWriMo? Started too late but did it.
\item Did I write a chapter of Jeb? I might start slowing down Jeb writing, because my mind is blank.
\item Did I blog? did it. it's right here, for all that the post isn't going up on time.\footnote{there is something interesting in the fact that a reader looking back has no real way to know when, exactly, a post was written or even published.
Artifice on artifice}
\item Did I stretch? made bagels, which is at least exercise. I was well into a cardio heart rate through the kneading.
\item Am I doing better at prayer than a rushed and thoughtless rosary? Not even a little. I didn't pray it last night.
\item Am I doing a good job writing letters to friends? Nope.
\end{itemize}

\end{document}