\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``\#1''}
\newcommand{\nsay}[1]{`\#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{baking-take-four.html}{Baking Competition Prep 4th Attempt}}
First Published: 2019 January 07
\section{Draft 1}
As those of you who've been following the progress of the baking competition might know, I've been working hard to perfect my recipe.
Now that I'm at the training trip, I thought it important to try making the recipe here, as the oven and stove might behave differently.
Oddly enough, the butter seems to behave differently, though that may just be my failure to cook.

I've learned that if you boil butter, it will eventually incorporate a lot of air.
If you wait until that point to fold in chocolate, you end up with a more stable final project.
It received positive reviews from all, including my alleged competition.

For the sake of not trying to remember, below is the recipe.

\begin{enumerate}
\item Combine 1 egg, 1 egg yolk, 2 tablespoons and 2 teaspoons sugar, and 1 tablespoon flour in a bowl.
\item Mix until fully incorporated
\item Grease a cupcake tin and wipe\footnote{the wiping makes the end result smoother}
\item Melt 1/2 stick butter in pan, stirring often
\item When butter has boiled and begins to rapidly expand in size, remove from heat
\item Stir in 2.7 oz bittersweet chocolate pieces, and when fully mixed, add the egg mixture.
\item Once fully incorporated together, pour into muffin tin and cook at 350 F.
\item Remove from oven when the sides have begun to pull away and feel mostly solid when touched.
\item While still warm, flip onto plate to remove from trays.
\end{enumerate}
\end{document}