\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{baking-reflection.html}{Baking Reflection}}
First Published: 2023 May 02
\section{Draft 1}
So the last time I can find that I mused about baking, I mused about \href{baking-take-four.html}{a recipe I was working on.}
Today is sort of the opposite.

I've found that\footnote{in a very limited sample size} when I bake bread in the morning, I feel better about the day and I am more productive.
To test that, I made bread dough last night and woke up slightly early to bake it this morning.
It came out really well, which was great.

While I was making it, though, I considered what I was doing.
Something that popped into my mind was a meme format I've seen going around a lot for the past few years.
The general conceit is that someone is reflecting on how excited their ancestors would be of the quality of their living conditions.

I thought about the fact that I was actively choosing to make bread, not out of any need, but simply with the desire to feed my friends.
I worked with finely ground white flour, which I was able to mix using drinkable water that is within my home.
When I decided to bake it, I have an oven within my home.

It was a nice feeling, though I think the productivity was a little overstated.
I didn't end up doing as much as I wanted throughout the day, though I did get an early start, which was nice.
Maybe my day wasn't going to be productive regardless of my choices, in which case what I did was the best I could do.

In any case, I got to share fresh baked bread with friends, and that made me happy.\footnote{a fun anecdote from sharing. Someone asked me about my recipe. I replied, \say{I put water in the bowl, added flour, realized it wasn't enough dough, so added more of each.} which even I recognized was not a helpful recipe.}
\end{document}