Anne pressed herself against Jim's hard lines.

\say{Please James,} she said, in a voice like velvet, \say{won't you stay the night?}

Jim's body strained as his two halves fought.
One side wanted nothing more than to accept Anne's invitations, both spoken and implied.
The other, saner piece of him began listing the litany of reasons why he couldn't stay and needed to leave.
As Anne pressed her lips to his, however, the voice of reason got quieter and quieter, as if drowned out by the roar in his ears.

James broke away from the kiss, leaving Anne to gape wildly.
But, before she could form a single thought, James had picked her up and replaced his lips on hers.
With his strong arms wrapped around her waist, her legs instinctively wrapped around his jeans.
She pulled his chest to hers, noticing how tightly the shirt was stretched over his broad shoulders.

\textit{It's a good thing I took my heels off earlier,} she thought.

As James kissed her, she felt a wave of desire run through her body.
He set her on the countertop, and immediately moved his hands.
One went in her hair, stroking it and massaging her scalp.
The other went to the zipper of her dress, and began to pull it down.

Not wanting to feel left out, Anne reached down to his fly.
Pulling the belt out, she noticed that the belt seemed to be somehow sharp.
But, as his lips followed the path of her dress on the way down, all rational thought went away.

Each kiss left a trail of burning passion behind.
His rough cheeks added to the effect, pushing her desire higher than she'd ever felt it.
When his kisses got down to her navel, he took hold of her two knees, and pushed them apart as he moved his mouth lower.

Seeing that she had worn underwear that night, and seemingly coming out of trance, James shot up.

\say{I'm so sorry, am I taking things too quickly?} he asked, looking worried.
Anne, normally the most passive of souls, forced his head back down to where it was, before burying her hands in his hair.

She'd never felt hair like his.
Each curl seemed as if it was almost moving on its own, circling around her hands before pulling away.
