\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{book-of-mormon.html}{Book of Mormon Review}}
First Published: 2018 November 7
\section{Draft 1}
As I mentioned \href{feeling-lucky.html}{earlier}, I saw the \textit{Book of Mormon} a little bit ago.
It was a fun show, and somewhat interesting.

I already knew the main storyline, plot, and music, because I live a life in proximity to musical theatre.
Sadly, I remember only a few bits from the actual production.\footnote{for some reason it was overshadowed by a different show I saw}

First, it was interesting that, other than Jesus, who had what I think was meant to be a California Surfer accent, all of the characters spoke with East Coast accents.
Second, I didn't realize how explicit the innuendo was in \say{Baptize Me.}
Finally, the characters were almost over the top in how stereotypically American they sounded and acted at times.
It was an interesting reminder that America is viewed differently from the outside looking in as from the inside looking in.
Overall, however, it was a wonderful production.
The cast and crew did a great job.
\end{document}