\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{book-club.html}{Family Book Club}}
First Published: 2023 August 28
\section{Draft 1}
Apparently I've never written about my family's book club.\footnote{based on the search of book-club.html not turning anything up}
That doesn't necessarily mean that I haven't but I can't find it, so it doesn't count right now.

So, what is the family book club?\footnote{technically there's an opening word, which is our last name (which is, I guess, absolutely obvious if you're on this site. Nonetheless, I shan't be explicit about it}
Well, you need to come with me back to the far off time of 2018?\footnote{I think}
My father messaged one of our family group chats\footnote{because we have far too many} about a book he thought we should all read.\footnote{Mindset, for those curious}
I\footnote{I think at least, others may claim that another member of the family said it instead} then replied that we should have a family book club.
The rest of my family agreed, and so we have all taken turns\footnote{going from oldest to youngest} choosing a book for us all to read.


Each book club begins with a few standard questions.\footnote{statements, I suppose}

We all give a thumbs up, down, or to the side for whether we enjoyed the book or not.
The one who chose the book says why they picked it.
We all give our big picture opinions on the book.


Then, because we exclusively read digitally, we go through the ebook that we have all annotated\footnote{which makes being the slow reader in the family rewarded, because you get to see everyone else's takes on the book} and read through each comment and highlight.
We usually have pizza while we do our club, though that is not mandatory.
Reading through all the comments almost always takes far longer than the pizza does to be consumed, and it often ends in a bit of a drag.

In total, we've read twenty five books for book club.\footnote{well, we've had 25 entries. One of the entries was books 2 through five in a series, and another was six-ten, so I don't know if that's really *a* book. One was also two children's books}
Ten of them have been what I would classify as self help books, which is kind of fun, I suppose.
Since we've now gone through 25 in about five years, I suppose we do each really have an average of a single book per person per year, wow.
There's been one non-fiction, and the rest of the books are all fantasy.\footnote{that probably says something about my family, though I'm not sure what}

Most recently, we did a marathon of three book clubs back to back to back in a single night.
It was really fun, for all that the books were not all universally loved.\footnote{mine, in particular, was panned}
Well, c'est la vie.
I'm excited for our next book club, whenever it happens.

\begin{itemize}
\item Another person whose job is actually science outreach sent me their slides.
They're really helpful, so I'll probably base mine heavily off of his.
\item I did a fair amount of cleaning, if only out of necessity.
\item Streaks come and go.
I don't regret spending time with my family instead of blogging.
\item I ended up with 3/4 chapters last week.
Yesterday and today I wrote another, 1/4+
\item No poetry since last posting
\item No journaling since last post
\item Whoops, no stretch
\item I have continued making sleep a priority.
\item Prayer has once more ceased to be a priority.
\end{itemize}
\end{document}