\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{bound-moon-rising-1.html}{Bound Moon Rising Campaign First Session Recap}}
First Published: 2023 January 12

Prereading note: After each section of the \href{dungeons-dragons-rex-0.html}{DnD campaign} I'm playing in, I'm going to have an in-character journal log about the events of the session.
Hopefully it'll help me develop the character's voice and remember what's happening.
\section{Draft 1}
I fear what my dreams will bring tonight.

Today began like any other lately.
My companions and I sat in the Nail and Board, waiting for a job offer that we all knew was not going to arrive.
Brent clearly took some pity on us, because he offered us a job.

His opener hadn't shown up today.
Of course, Kaeden had never been the most reliable employee, so it was not concerning that he wasn't there.
Still, he offered to stand us a round of drinks if we found his lost employee.

We looked in Kaeden's usual haunts, only to find that this was not an innocuous case of oversleeping.
After nearly a full day of investigating, we found that he had been kidnapped and taken to a barn in the nearby woods.
Shockingly, the people who had kidnapped Kaeden did not have his best interest in mind.

Jenna scoped the barn out, which seemed to be a cultic ritual.
Neither Stygia nor I have ever had much fondness for unknown cults, so we elected to free Kaeden and correct these poor souls from their error.

Of course, with everything else that had gone wrong today, it should not have been a surprise that the lead cultist was himself a necromancer.
We eventually felled him, with my own starlight landing the final blow.
Kaeden was otherwise unharmed, but we learned that this ritual was only the first of terrible events to happen.

Tomorrow, the lead cultist was apparently going to hand off the dagger Kaeden was to be killed with at the Swamp Lily.
Some of the cultists we returned to their stars were regulars at the Nail and Board, people we had known, if only vaguely.

As worried as I am about tomorrow, I am glad that the skies will be clear.
The stars will watch over me, should I fall or succeed.
I just hope that they will carry the message to my family if we should fail tomorrow.
\end{document}