\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{broken-nose.html}{A Broken Nose}}
Prereading note: There's mentions of injury and blood, so if you don't want to read about that, avoid today.
\section{Draft 1}
As some of you know, I'm somewhat\footnote{read: I still don't believe in injury} non-risk-averse.\footnote{I hope I hyphenated that correctly}
And, that often results in some fun stories.

My favorite stories are probably: the time I scalped myself,\footnote{maybe a future post} the time I set my hair on fire,\footnote{which, honestly, was pretty cool} the time I bled through fiberglass,\footnote{honestly, a surprisingly funny story} and the time that I found out that all of the not brown\footnote{the green} in my eye can fall to the bottom if I hit my eye correctly.
Today, I get to have a new one!
The time I broke my nose.

All things considered, it's somewhat surprising to me that I've never broken it before.
But, I was learning new skills today, and then misinterpreted a direction.
I was on my hands, trying to learn a handstand forward roll, when I heard \say{go into a ball}.
Now, I normally just pull my legs to my chest when I'm supposed to do that, so I did.

As you might expect, that threw me off balance.
My knee came crashing down, and I heard a crunch.
There was a lot of blood coming out.

But, small blessings still exist.
I didn't get any other injuries.
Because of how I fell, my nose didn't get bent out of place.
I was surrounded by friends who helped me mop up the blood and start recovery.

But, I can now report on what a broken nose feels like.\footnote{yay!}
It felt almost entirely like an ice cream headache.
My nose still hurts to touch, but that's fine.
Up at the bridge, it was really slidy, and I could move it from side to side and up and down.\footnote{yes mom, I stopped doing it after medical advice advised me to not do it}
Here's hoping it heals well!
\end{document}