\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}   
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{bullet-journal.html}{Trying Bullet Journals}}  
First Published: 2025 July 20

\section{Daily Reflection: 20 July 2025}

As my post the other day implies, I am someone who easily loses track of time and place.  
I want that not to be the case, but don't know how to make that happen.

Historically most methods haven't worked for me.

I've found pretty good and continuous luck over the past month doing a clipboard, so I'm hoping that it continues with a bullet journal.  
Rather than having pages for each thing, I will go back to the method I used when I began journaling: strict chronology.  
Each day gets one full page, and I have a few other pages for reminders and notes.

Since, for all intents and purposes, my planning ends in a month and a few days, I don't really care if this method means that I lose track of events that would happen in three or so months.  
It is very important to me that I get through this thesis, and I realized today that it is also really important to me that it be long.  
With that in mind, I think that the new method is something that I can force myself to be doing for the next thirtyish days.

So, what is bullet journaling?

Great question

Came from a guy with ADHD, has become an entire aesthetic.  
Generally as far as I can tell the idea is to have an externalization of the brain in one place with dedicated time and space to clean the thoughts into something reasonable.

I've got a page where I have the day and day of the week for the remainder of my schedule, when I'm traveling and where, and this week's goals for habits.  
This week's habit goals are: stretch twice, meditation of some sort, blogging, writing poetry, penmanship, typing, and reading.  
I want to do most of them daily, but penmanship and typing are both effectively every other day events.

This page and the following cleaned pages are stored in a folder.

Following that, I have a page with my ideas for blogs.  
I'm currently reading a book about women in science and it's sparked some great blog ideas.\footnote{mostly about the idea of the liberal arts and what it means to be a scientist or do science}

Behind that, List of all Tasks!  
I plan to update that daily

Behind that, list of books that seem interesting, so that I don't forget they exist

Behind that I currently have a weekly plan/reality log?  
I'm not sure what this will do for me, and it's likely that I'll ignore and or get rid of it.

Behind that I have the daily pen choice, whose main idea is that it will help me figure out when I wrote things based on the pen they're written in.  
The six pens I'm currently working through mean that it will be just over weekly that each one repeats, so anything that's less than a week away is uniquely identified by when I wrote it.

Behind that I have an empty page for each day until next Monday\footnote{because I'm traveling R-M, so won't be able to make the next week in the morning of Sunday or Monday}, except for today's and tomorrow's, because I'm planning on actively writing those.

Outside of the folder, I have the rest of the clipboard.

Right now that's my notes on the book I'm reading, an optimistic page for me to write poetry on\footnote{optimistic in the sense that I'm not sure the poetry will go there, not its actual mental state}, today's messy page, which has some tasks and a bunch of notes, and the penmanship page, which I've done some work to fill.  
I know that most of the books I've been flipping through with a friend don't just have repetition of letters, because it's both too much of a task, being multiple actions, and also too little, not being a full word.  
Still, I think that my e is slightly more consistent and that my \say{a} is maybe a little better?  
I realize I don't know what I want the a to look like or write like though.\footnote{these are shockingly distinct. I think that I want a single stroke, but what that stroke is is important to me almost independent of what the output looks like and vice versa}

Somewhere I've also tomorrow's page, and my hope and plan is to write it tonight and then journal and confirm it tomorrow morning before getting outside.

Aha it is in the back of the folder.

Well, let's hope this works!

\begin{enumerate}

\item Did you journal today?

Yeah! I spent some time in the early afternoon, when I started doing my things for the day.  
I then also started getting through some ideas of work, and so started a bullet journal! I think that's what it is, at least, and will discuss it in the post\footnote{which is above this, so I guess you'll have already read}

\item What ink/pen did you use, and what were your thoughts on it?

Today's pen was the Kaweko Sport, and I have almost finished its ink. I think that it was the private reserve chocolat or potentially vampire red. it is not quite empty, but I'm planning on practicing penmanship until it is empty. Wait no, because I wanted to do some journaling and poetry tonight with it. Whoop.

\item How's prayer?

Eh. I tried to go through a rosary and I don't remember what stopped me.

\item How's focus?

Eh. I got through the rest of the introduction, but wow I have no motivation for the apparatus section. Writing that down now, I guess that's absolutely something that I can just push through, so I should plan on that tomorrow.

\item How's sleep?

Generally fine. I didn't get to sleep until like 1 this morning, but then woke up on my own at like half past eight.   
I haven't napped today, but I'm planning to go to bed before 2200.

\item How many meals, and how balanced?

Since yesterday's, I had dinner at a supper club, which was a ribeye, \say{irish potatoes}\footnote{deep friend small whole}, and salad.  
This morning I made what I think can be described as congee: handful of frozen onion and celery, some peas, green beans, three brats cut small and then a large handful of water which I put on the stove until it made a nice pasty thing.  
Tasted fine, probably full of nutrients.

Since then I've had an espresso tonic, a peppermint French soda, some tea, and will be eating a polish sausage\footnote{maxwell street brand}

\item How's the posture?

I kept catching myself hunching over while reading this afternoon.  
My upper shoulders and lower neck remain so very tight, though.

\item How's the breath?

I honestly think pretty good! I've been reminding myself to breathe, especially on the long drive back home.

\item How's the movement?

Eh! I walked the mile and a half to a coffee shop this early afternoon, and then walked to work, which is effectively back home.  
That's still about three miles total, though, which is not nothing!

\item How's the physical flexibility?

I stretched a bunch.   
Oof I am tight and tender.  
I might try stretching more tomorrow, especially if I remember.

\item How's keeping up with the family obligations?

Called the brothers! Will listen to the album while walking home.

\item How's the thesis?

Last night I read through the RebelFit chapter, and then today I finished editing the introduction, printed it out again to make sure it seems fine\footnote{and because I want to add pictures at some point soon, because 12 pages of single spaced text can probably balloon really quickly with many pretty pictures}.  
As mentioned above, have not been able to force myself onto the apparatus, even though it's one of two remaining chapters, and the other remaining chapter requires me to have finished calculations, which is yet to happen.  
Then again, I can probably make at least some of the charts? Something to think about for tomorrow.

\item How's the poetry?

None, but I made a new sheet for it.

\item How're the interpersonal relationships?

Keep messaging people. I am getting lunch with someone tomorrow, so it's important that I pack myself something reasonable for lunch, because the gaze of the other is terrifying to me.

\item How's the music?

Listened to some! A new current favorite song is Babylon by the Dirt Poor Robins.  
Otherwise, I've agreed to make a playlist of folk music to trade someone for a playlist of house music.  
I have no idea how long or crafted that playlist will be, but can make one soon. Might be a good topic of folly, depending on timing.

\item How's the other writing?

Started a bullet journal! THat's pretty cool, and even did some penmanship work too.  
I don't know how well externalizing thoughts is going to go, especially with the nightly camping thing, but it'll be something to try, at least.

\item How's the cleaning?

Eh, minorly better.

\item How's ordering the life?

Decent! We'll see if the bullet journaling works.

\item Water?

Ok! I drank a fair amount last night and then had some today.

\end{enumerate}

Current Pen List\footnote{for my own posterity, mostly}

\begin{itemize}

\item Hongdian Black with Blade Nib: Missing  
\item Hongdian Black with Fude Nib: Private Reserve Neon Yellow (since pre-June I think)  
\item Shark: Purple of some sort, unsure which right now (I think since late june)  
\item Kaweko: Chocolate Brown? (I think since late June). Almost empty  
\item Pilot Preppy: Private Reserve Electric DC Blue I think (I think since late june)  
\item Conklin: Montverde Fire Opal (since 7/17)  
\item Sheaffer: Private Reserve Spearmint (since 7/15)

\end{itemize}

\section{Daily Reflection 19 July 2025}

\begin{enumerate}

\item Did you journal a full page today?

Not a full page, but about half of one!

\item What ink/pen did you use, and what were your thoughts on it?

I used the Pilot Preppy, which I think still has the Private Reserve Blue.  
I continue to really like the color, but for some reason I noticed that my writing was far messier today than it has tended to be lately.  
I'm not sure if that's a function of starting writing after a full breakfast and coffee, the fact that my chair is so low, or something in the nib itself, but it is interesting to note regardless.

I do also think that the Pilot is my finest nib. I'm somewhat curious how large it ends up being.  
Looks like somewhere between a .2 and .3 mm stroke, which makes sense, because that is the thickness that I do in general really like, and the minor flex means that they won't all be the same width.  
The others pens are, of course thicker.  
The job that I'm taking offers pens in 0.5 and 0.7 mm, so that's probably also good for me to get used to.

Still, I don't like how messy the penmanship was today, so it might behoove\footnote{I feel like this is a past tense of behave? Huh wild, it is actually Old English and comes from \say{to need}} me to practice some penmanship.

\item How's prayer?

Not really happening. Probably worthwhile to set a reminder to do it.  
I have to move my car soon\footnote{darn 2 hour parking limits} so that might be a great time to go ahead and say a quick prayer.  
Then again, I've also been at this coffee shop for the better part of the parking limit, so maybe I should also get something else if I'm coming back...

\item How's focus?

Generally decent.

I read a full book this morning which is just absolutely wild\footnote{oh, that could have been the folly for the day. Alas, I guess}  
Since being at the coffee shop, I've managed to get some journaling, a full hand-edit\footnote{read: I have a printed copy which I looked through and made changes as needed, including doing a bit of research because I had some hand waving that I didn't notice in a derivation} and about a third of the typed edits for the Introduction chapter.  
I got so burned out\footnote{burnt out? maybe just lost focus is the better term} at that point, and so now I'm going to do this until it's time for me to move my car.\footnote{my main reader expressed a preference for less polished folly writing, and so, at the very least, I'm going to try to have the daily reflection and draft 0/1 of things be so}

I assume that getting up and walking a bit will help.

\item How's sleep?

Since last post, I went to bed at around 1230\footnote{I did not, in fact, delete all the games. Or rather, I did, but then I redownloaded one of them, which is a Majong (sp) roguelite, and it's so much fun and so addicting and I'm sure that I am absolutely horrid at it}, and then woke up for a fun two or three hours at around 2.  
I was up before the 830 alarm I set, even if it did take me a while to accept that and longer to leave bed.

Right now I don't feel tired, and I didn't feel bad about driving home from the talk last night, which is two great signs.

\item How many meals, and how balanced?

Uh I had some fried chicken for dinner last night. I'll say that's probably fine-ish, since it is still primarily fat and protein, with some non-sugar carbs.

This morning, the hotel breakfast\footnote{my beloved} was a thing of chobani strawberry yogurt, a disposable cup of coffee, two things of chocolate milk, two what they called beignets\footnote{nutella filled dense donuts. As delicious as it sounds, if you can believe it}, eggs with cheese I added, some bacon\footnote{pork, to be as clear as the hotel was}, a thing of orange juice, and a waffle with butter and syrup.

That's honestly much more food than I think that it felt like at the time, and also far more food than it seems now.  
Oh! Also some berries.

One of the milks and the yogurt technically got consumed about two hours after the rest of the food, but who's keeping track?\footnote{me, as it turns out}

At the cafe, I've had a raspberry italian soda, but yesterday I got a sweet crepe here and it was delicious. I'm tempted to get another today, and might do on of their savory options.

\item How's the posture?

Generally fine.

I'm sitting with my legs crossed and was spending some time not so much sitting up, but that's partially to be blamed on how tall this table is relative to its chair.  
Then again, not having my forearms needing to arc down as much is also pretty nice.

\item How's the breath?

Eh, I just took. am taking fie deepish breaths, and they're nice.

The more I do intentional breath, the better I feel, which does imply it is something that I should be focusing on more than I do.  
Then again, the more things that I focus on, the less that I can focus on any individual thing.

\item How's the movement?

I move minimally, and haven't really stood up since sitting down for to start writing.  
That's not great, so let's actually call it here, stand up, move the car a little early, and then return to our seat and get a little more work done, this time around taking a break every hourish.  
Or, at least, we can treat that as a goal\footnote{love that this writing site keeps trying to get me to write just a few more words (legitimately)}

Little bit of walking did really do a lot to perk me back up\footnote{and the chocolate flavored coffee (I don't know what they mean by this, it came like any other batch brew, but wow there's an intense amount of chocolate in it) certainly didn't hurt}.

\item How's the physical flexibility?

Eh, could be better.  
I stretched in the shower this morning\footnote{meaning mostly toe touch and a little bit of shoulders/hips} and just did another forward fold during the walk.  
Little bit of neck stretching as I sit here.

The fact that my legs are crossing is more proof I should stretch my hips out more.  
Probably a thing to do at the park tonight.

\item How's keeping up with the family obligations?

Honestly and legitimately decent!

I call the brothers tomorrow and I have the new album as of last night, so could do that while doing some stretching today/tonight/tomorrow.

\item How's the thesis?

Oof, as yesterday's folly points out, I am nowhere near where I wanted to be\footnote{the terrible thing about having a relatively quick turnaround means that you go from ahead to behind in a matter of days}.  
However, I got through what I wanted to do yesterday, I think.  
I printed out the chapter this morning\footnote{thank you hotel!} and also the introduction.

Working through intro right now, it does honestly feel pretty solid, but of course the more pictures I put in the better, as always\footnote{Before latest round of edits, on the current page layout (one inch borders except left, which is a one half inch border for some reason, 12 point font, .5 inch footnote separation) Intro just barely touches (kisses, one might say) the seventh page.}

Oh! I keep wanting to do the whole \say{use a layout that I didn't make myself} thing, so this could be a great time to do that!

Despite my claim that the motivation is back, maybe it isn't as close to back as I wanted.

\item How's the poetry?

Didn't write any yesterday or this morning, but would like to today after finishing with work\footnote{I will not go to the arcade. Arcade is the time killer. Last week when I found the arcade and got more than a 1:1 free game ratio on the pinball machines was an exception because that bar set them absurdly low and also I was hot. This will not occur again (and other mantras I repeat)}, if nothing else ends up taking the time.

\item How're the interpersonal relationships?

I chatted with the other people at the talk yesterday, including the no-longer-solely-volunteer who coordinated it\footnote{one might say a coordinator, if they were slightly more coherent than me}

\item How's the music?

Uh I don't really think I did any since last time I've been writing.  
I don't even think that I listened to any music last night.  
I did walk into a music store and resist the urge to buy anything, so if anything, one might be accurate in saying that I did negative music.

\item How's the other writing?

Uh, I think that's really it. Haven't texted too many people, the hand edits on my thesis are thesis.

\item How's the cleaning?

Wow I'm good at getting the hotel room packed in just a matter of seconds.  
I was completely spread out\footnote{as one might expect when checking into a hotel with the express intention of getting a lot of work done} and even still managed to get everything in its

\item How's ordering the life?

Uh, I don't really think that I've done any of that.  
Yesterday's post was helpful in that regard, to be certain.  
Otherwise, I think that prayer\footnote{shoot forgot during car swap} and finishing this are the big ones.  
Oh, planning travel, but I think that I'm doing that tomorrow.

Also, I want a nicer clicker, so I just got it.\footnote{for some reason my clicker doesn't really work at all. Not sure if it's the wireless receiver or if it's a \say{when you put a USB-A into a USB-A to USB-C converter nothingn works}}

\item Water?

Really good! I've had to refill the monster jug, and I even am occasionally remembering to just like drink it.

\end{enumerate}

Current Pen List\footnote{for my own posterity, mostly}

\begin{itemize}

\item Hongdian Black with Blade Nib: Missing  
\item Hongdian Black with Fude Nib: Private Reserve Neon Yellow (since pre-June I think)  
\item Shark: Purple of some sort, unsure which right now  
\item Kaweko: Chocolate Brown?  
\item Pilot Preppy: Private Reserve Electric DC Blue I think  
\item Conklin: Montverde Fire Opal  
\item Sheaffer: Private Reserve Spearmint

\end{itemize}

\end{document}