\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{candidate.html}{Announcement}}
First Published: 2023 April 6

\section{Draft 1}
In the time since I stopped writing this blog, there have been a number of changes in my life.\footnote{I'm almost certain N>1}
One of the most notable of which is that I am now a PhD candidate.
I haven't quite figured out how that changes my own life, but I understand that it generally comes with a few changes in a PhD student's life.

It often means that you're beginning work on your thesis.
In theory I've been working on that for a while.

It often means that you're done with classes, but I've been done needing classes for more than a year and done taking classes for a semester or so.

It often means that your PhD project has been approved, but at least in my program, we never actually get a formal approval for our PhD project from our committee.

Where does that leave me?
More or less in the same place, except that I've changed my LinkedIn profile to say \say{PhD Candidate} instead of \say{PhD Student.}
As I write this, I've already found a second use case for that!
Someone asked me to write a bio for the public talks I'll be giving again this summer.\footnote{I was going to hyperlink again, but I apparently never wrote about them last year}

\end{document}