\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{christmas-2024.html}{Christmas 2024}}
First Published: 2025 January 6
\section{Draft 1: 6 January 2025}

I started to write this musing on Christmas morning.  
It was a Christmas unlike I've ever had before, though for almost no positive reasons.  
I woke up alone in my empty home, with neither tree nor any decorations.

Last \href{christmas-2023.html}{Christmas}\footnote{I gave you my heart (song reference)} I mused about the different Christmas traditions my family had.\footnote{has? It's hard to use tenses when discussing anything with my family any longer}  
This Christmas, we abandoned most of the traditions, for a few different reasons.

We kept the pajama exchange, though it felt far less homey, given that I had to walk a few blocks in them in order to sit with my father and brothers.  
We kept the photo with Santa and the family selfie, though I no longer had to angle the camera far down.  
We kept the generally low energy vibes, though with a flavor of sorrow rather than joy underpinning it.

Having spent a year without the traditions, my family and I all agree that we do, in fact, like all the traditions we have and want to bring them back next year.  
Of course, there will be a gigantic hole in the midst of that\footnote{and every} celebration, but that is something that we're going to have to work around.  
I don't know what metaphor will end up being the most true here, whether the hole will grow smaller in time, be covered over by new threads of life experiences, or simply avoided, as a scar in the ground.  
Regardless, I am grateful for the past year, the coming year, and whatever time I have left on this world.  


\section{Draft 0: 25 December 2024}  

As much as I'm glad that last year's musing about Christmas contained our traditions, because I have already forgotten them, reading them was very difficult.  
So much has changed from last year, and some of it was even my fault.  
We are not at home  
\end{document}