\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{class-day-ii.html}{Class Day Two}}
Today, I had the second day of my class.
It went much better than the first.
At one point, someone else was unsure of what functional groups was on the molecule, and I made a new friend by telling him.\footnote{GC Organic Chemistry still haunts me}
I feel much more like I belong.

But, the whole experience made me realize some things.
For as quickly as I got over it, there was a non-zero amount of time where I seriously considered dropping the class, and finding something else to take instead.
If I, a stereotypically normal STEAM\footnote{Science, Technology, Engineering, Agriculture (yes I'm from Iowa, how'd you know?), and Mathematics} person, who never feels out of place in STEAM classes, or really any classes at my home school,\footnote{almost typed University. London is getting to me} felt out of place because I didn't know something, how much worse must it be for people who come in already feeling like they don't belong?

I don't know, and I'm pretending that my experience with this is comparable to those who are from traditionally underrepresented groups.
Instead, this really showcased for me the importance of the different outreach programs that exist to encourage these groups to continue with STEAM.

But, before I ramble on too much, I did really enjoy this class.
I'm really excited to learn about polymers, and I hope that I'll be able to take some of the knowledge back with me.\footnote{not that I think it'll get confiscated at the border, just that I'm not sure if it'll be relevant to my life at any point while the memory is fresh}
\end{document}