\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{cocktail-catechesis.html}{Cocktails and Catechesis}}
First Published: 2022 June 28


\section{Draft 1}
Tonight I went to my first cocktails and catechesis in a while.
More or less, it's a happy half hour followed by around an hour of discussion about the content in the past few weeks of the CCCiaY.
This week's topic was Baptism and Confirmation.

It was a great time, though more sparsely attended than I remember.
Between that and leaving work late, though, I didn't end up doing the writing I wanted to today.

\begin{itemize}
\item I made arguably negative progress.
\item Blogging streak day four! wow!
\item Air quality got somehow even worse, so I took another day off of exercise. I did walk a friend home, though, so I'm counting that
\item I got up at six! Wow! Starting a streak just in time to end it.
\item I listened to a lot of CCCiaY today. Once more, bedtime rosary is the plan
\item I wrote none chapters today.\footnote{boo} I'm still two ahead, though, which is really nice.\footnote{arguably one, since I need a post for Friday, but}
\item Two days of no sonnets
\item Two days of no letters. I think tomorrow morning is a great time to write one though.
\end{itemize}
176/11
\end{document}