\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{conference.html}{Conference (etc.) Recap}}
First Published: 2023 June 25
\section{Draft 1}
So I've been absent another week and a half or so.
In my defense, I was watching someone graduate, and then at a conference.
In my offense,\footnote{that seems like the wrong phrasing, but it is a nice antonym here} I could have made time for this.
Anyways, in the interest of not doxxing my family\footnote{which I may have done in the past, but now seems like as good of a time as any to try having a bit of CS literacy,} I won't be talking about the graduation here\footnote{even though I'm nearly positive everyone who has or will read this blog will know who graduated from where and when}.
Instead, I'd like to talk about a conference I went to last week.

Despite being the most important conference that my group goes to,\footnote{a feeling that seems to be shared among a number of people} the conference is nearly unheard of.
Even my friend who goes to the university that hosted it didn't know it was happening.
But, it was a great time to bond with my group, reconnect with old friends,\footnote{read: people I met last year at this conference and then forgot about for a calendar year} meet new friends, and, of course, listen to a ton of incredible research talks.
I also gave a talk, but it was far from incredible. 


\begin{itemize}
\item I did a bit of cleaning.
\item I blogged today! Planning to again tomorrow
\item I did a 5K today.\footnote{though i did need to walk for parts of it} That wasn't fun, but it was probably healthy for me
\item I am still in recovery mode from the conference, and so I have slept in the past two days and will likely sleep in tomorrow.
\item I did a rosary during the 5K.\footnote{which does remind me of a joke. the short version is two priests smoke together. One asks if it's ok to smoke while you pray, and is told no. The other asks if it's ok to pray while smoking and is obviously told yes. Moral of the joke: make sure prayer is what you add to other activities, rather than vice versa. (or I suppose, find ways to sanctify anything you do, etc)}
\item I'm more ahead on the book than I have been for the past week or so.\footnote{i.e. I'm not writing the chapter an hour before it's posted. I don't really want to finish it before going to bed, but I know I'll be grateful tomorrow if I do it today.}
\item I added another verse to the dumb song between the last posting of this blog. Now it feels like a complete song, because I don't personally always love bridges.
\item I've given up on posting\footnote{read last musing for a rant about this word in the footnotes} the first letter I wrote. I did get a bulk pack of blank cards, though. I've addressed them to the people I've made a mental or verbal commitment to send mail to, in hopes that it will inspire me to write the letters.\footnote{read (I wonder if there's a meaning behind when I use read versus i.e.): I'm hoping it lowers the activation barrier enough that I am actually able to do so.}
\end{itemize}

290/249
\end{document}