\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{conference-2.html}{Conference Recap}}
First Published: 2023 July 20
\section{Draft 1}
Once more, I've made it back from a conference where I didn't blog at all.
This is \href{conference.html}{the other important} conference my group goes to.
It happens\footnote{nominally} bidecadally\footnote{so every five years}, which means this is likely going to be the only time that I attend it.
In part because I was exhausted from beforehand, I don't know if I retained as much science at this conference as I would have liked.
But, I do absolutely think that I had a lot more professional networking than I expected to

This conference was for the entirety of my\footnote{admittedly tiny} field.
There were two poster sessions and otherwise almost exclusively invited talks.
The talks really ran the gamut for the entirety of the field.

External to the explicit conference but related because I was there at the geographical location in the specific time, I also had some fun experiences.
They took us on a hike to a national lakeshore.\footnote{where I went too far and then had a lovely rosary power walk (where I prayed rosary slower than normal, interestingly enough)}
I bought two supplies for brewing.\footnote{tannins and malic acid.
I don't know when I'll use either, though the lemon wine recipe I use does recommend some tannins.}
I also learned\footnote{remembered?} that I love pinball.
I don't really know what to make of that.

\begin{itemize}
\item I did clean a little. More importantly, though, I made minimal mess, which means that I'm further ahead. A lot of that comes from closing a few cabinets that I perpetually leave open.
\item I wrote another chapter today! I did minimal poetry, though I am ok with that.
\item I'm accepting and embracing that I won't really have time to exercise before Tuesday next.\footnote{a construction that I prefer to next Tuesday}
\item I set an alarm for half seven today and woke up around six anyways. I'm now getting to bed too late, but will still be up bright\footnote{I hope} and early.
\item I listened to more CCCiaY, and I managed to find time to go to chapel to pray a rosary. It was really nice.
\item Today's chapter was still longer than normal\footnote{between thirty and fifty percent so}, but shorter than yesterday's. I've finished the first arc in my story, which is funny, because it took twice as many chapters as expected.
\item I'm not going to write explicit poetry today.
\item I wrote a letter and posted it. I remembered one person I was supposed to address a letter to, addressed it, and hopefully am not forgetting anyone. I also queued another letter to be addressed and then written.
\end{itemize}

366/68
\end{document}