\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{dietary-needs-3.html}{Dietary Needs}}

First Published: 17 January 2025 (because I forgot to hit post)




\section{Draft 1: 10 January 2025}  
\href{dietary-needs-2}{Yesterday} I went through some of the different ways that I could get sufficient protein.\footnote{as also kind of pointed out, though mostly implicitly, fat and carbohydrates are so minimal as to be trivially consumed.}  
Since I'm\footnote{after much counseling from friends} not going to just consume all of my protein from a single source, I do technically have an NP problem, which is a variant of the \href{https://en.wikipedia.org/wiki/Knapsack\_problem}{knapsack problem}.  
However, I'm looking for solutions that do not fit neatly into the normal computational framework, if only because more or less everything I could consume is functionally continuous, and the knapsack problem is meant for discrete entries.

Chicken, fish, and cheese are all similar in that I need to be eating about a pound a day of them in order to get my nutritional needs met.  
That's a fair amount of volume, if nothing else.  
I can't really imagine sitting down and eating a pound of any of them in a single sitting\footnote{which is probably something that I would be told is bad.}

However, one piece of advice a friend gave me was to speak to a dietician at my school, which is apparently free.  
Rather than continue to worry about all of this, I'm going to try to do that instead.

Daily:  
\begin{itemize}  
\item Practiced guitar? Not yet today  
\item Twice daily stretching? The five minutes at night seems so much harder than the one in the morning. Making an actual list of what I do for how long is almost certainly my best option going forward.  
\item Poetry? I've generally been doing two or so stanzas, and usually working on a different ideal each time. Yesterday I was trying for an ABBA rhyme scheme.  
\item Blog? Look at this right here!  
\item Net cleaner home?  
\end{itemize}

\end{document}