\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{doubting-myself.html}{Doubting Myself}}
First Published: 2018 October 24
\section{Draft 1}
As I've mentioned more than a few times, I do music.
However, I doubt myself a lot when it comes to music.
Part of this is that I have a bad ear, especially among my music friends.

Now, this isn't a disparagement of myself in an attempt to get sympathy.
Rather, it's a prelude for what follows.
As we all know, it's horrible when you have a song stuck in your head.
As I've learned, it's even worse when the song is written in Irish Gaelic, and so you can't search for the song by lyrics.
But recently, I realized that the worst way to have a song stuck in your head is a melody that you haven't heard.

That is, a tune started playing in my head, coming from the sounds I've heard and wanted to hear.
But, although I believed the melody was a certain series of notes, I didn't believe that it would be true, and so changed the notes when I transcribed it.
When I eventually played it back to myself, I realized I'd written a different melody.

It took me just ignoring my mind, and trusting my instincts to get the melody I'd heard.
And, now the tune isn't stuck in my head anymore.
Yay!
\end{document}