\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{dungeons-dragons-5.html}{Dungeons and Dragons Again}}
First Published: 2023 November 6

\section{Draft 1}
Oh gosh, it's been a long time since \href{dungeons-dragons-5.html}{the last time I blogged about dnd.}
I had a fun campaign with that druid, though it fizzled out for reasons.\footnote{people got busy and then moved away, to be exact}

Since then, I've started playing pathfinder with another set of friends, and I just had the session zero for another dnd campaign that's about to start.
I've realized that I really enjoy playing a simple character in DnD, probably because my own life is less than simple.
Barbarian is a class that tends to take a direct path to the solution of each of its goals, which is something that I really like.

This character is a plasmoid\footnote{which is a race I'd never heard of in 5e.
Wildly, it also is not a humanoid, which I suppose makes sense like explicitly, but is a fun thing because of how many low level spells explicitly only target humanoids} zealot barbarian\footnote{a subclass I'd never heard of.
Tl;dr, it gives me extra damage on the first attack of each turn.}
For my background, I took something that was called like raised by giants, which has the fun effect of making my first attack each turn do even more damage.
It's going to be a fun character to role play and roll play\footnote{get it?}, and I'm excited to hang out with these friends more.

One consequence of session zero just happening today, though, is that I lost the evening, which is when I tend to do a majority of my writing.
I was told that the event would end by half past eight at the latest, but then we started chatting and playing other games.
I certainly don't regret the time I spent with them, for all that it will absolutely make getting to my writing goal today a little more difficult.

I don't have much more to add about this, so I may as well start brainstorming some information about my character.
I randomly rolled myself into Neutral Evil, which I think means that I'm intrinsically selfish but have a normal attachment to the laws.
I think that works well with the background I gave my character, who I'm realizing probably deserves a name.
Let's go with Goob.

Goob landed in the wild mountains outside of (insert setting's mountains)\footnote{I legitimately have no idea, it's some homebrew campaign, so this whole story is of course only as canon as the DM wants it to be.
I think it's good to consider what my character's motivations are, on a slightly more visceral (fundamental? low?) level than the DMG often recommends}
when it was a small creature.\footnote{Using it here, because I'm going to say that plasmid has no gender/sex.
Given that I'm explicitly an amorphous blob that can change shapes if I want to, I don't think it's that unreasonable to think that I wouldn't have any explicit sexual characteristics.}
As I grew, surrounded by the giants, they adopted me as one of their own.

I always knew that I was different than the other children.
For one, they never seemed to relax quite as much as I did, always holding onto their weird bones.
For another, they were all much larger than me.
Still, I grew up loved and supported, as much as my parents were capable of expressing what that meant.

In time, I grew older and chose a path for myself.
Something about the stark beauty of the mountains called to me, and I found myself meditating on the beauty that I saw.
One day, some goblins\footnote{n.b. I'm happy to switch this for whatever other cannon (or canon I suppose) fodder mook we're going to be killing by the million in the campaign} came up to our mountain and disturbed the peace.
I felt a divine presence guiding my blows as I grew more enraged, throwing the goblins off of the cliff.

When the fight was over, I found that I had gone into what my people called a battle trance.
It did not seem safe for me to stay among them any more, for what if I did something I would later regret while under the throes of a trance?
I went down the mountain to learn to control the urges that called me towards violence.

While in the (insert name of whatever political entity the campaign starts in)\footnote{wow this is a fun game of madlibs}, I began to make a name for myself as a sword for sale.
Well, to be more accurate, as a battleaxe for hire.
I joined with\footnote{or am about to join with? Not totally sure what the party is getting together over} my party because (insert whatever plot reason here).
My dream is to control my rage well enough that I am once again safe to live with the other giants.\footnote{hmm not a great character motivation, but I suppose it's as good as I'll get.}

Daily Reflection:
\begin{itemize}
\item Did I write 1700 words for NaNoWriMo? I did! I don't love the way that the story is going still, but I'm hopeful that it'll start to turn around.
If not, eh, I will finish it anyways because I want to practice some skills that writing it will help me practice.
Maybe if I start each session with what I hope to learn, I'll do a better job of writing.
\item Did I write a chapter of Jeb? I'm about a fifth to a sixth of the way through.
I'm planning to finish the chapter after posting this blog, since writing the blog felt easier when I got home.
\item Did I blog? Wow! Another day with another blog post.\footnote{I keep forgetting to type 'blog, but I also don't know if the two words are identical to me.
Might be worth thinking about at some point}
\item Did I stretch? Whoops! Need to stretch still.
\item Am I doing better at prayer than a rushed and thoughtless rosary?
My rosary wasn't rushed last night, but it wasn't particularly good.
I did the Angelus at around noon, but it was somewhat thoughtless.\footnote{it's kind of cool that I now know the prayer well enough for it to ever feel thoughtless, not going to lie}
\item Am I doing a good job writing letters to friends? I did end up addressing another letter to a friend last night, and I posted the letter that I wrote on Saturday this morning.
That's technically progress, so I'm counting it.

\end{itemize}
\end{document}