\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{dungeons-dragons.html}{Dungeons and Dragons Again}}
First Published: 2022 February 5

\section{Draft 1}
First, an apology to my\footnote{apparently real} readership.
I got a message this morning\footnote{I really don't know whether to hope morning or night from the sender, because they should have been sleeping in any case} asking me where the post for February fourth is.
As with so many lovely things, I ended up losing track of time playing Dungeons and Dragons last night, and by the time I got home, was too tired to write a blog.
We were told it would end around nine, but it instead ended around 11.

Anyways, excuses about being tired aside, playing Dungeons and Dragons again last night was incredibly fun!
A friend and member of my group\footnote{this is the same person} set up a one-shot\footnote{with maybe option to continue? It's unclear} for a few of the people in the group\footnote{due to interest, not exclusivity} and a friend from the department.\footnote{but not the group, if that was unclear}

The game was incredibly fun, in some part because it was my first time playing in almost a year, but also because the group and dungeon master were both really fun.
Most of the people in the adventuring group were new to Dungeons and Dragons, which was really fun.
I forgot how much of a learning curve the game had, which led to a fun conversation in the car ride back where one of the other players asked about the ending, and what happened.
I explained that the game is like writing a book together, where authors sometimes just stop writing the book, and so the ending may not be as good as people want.
Conversely, people can continue campaigns\footnotes{the term for a long-term game of Dungeons and Dragons (or other TTRPGs [Table Top Role Playing Games], usually spanning many encounters} almost indefinitely.

Anyways, on to the campaign.
We six brave adventurers were hunting down a cultist as a nominal group.
My half of the group made a drunken promise to one person to help hunt down the cultist for rejecting their entry into the cult.
The other half said that they were hired by a professor to hunt him down because he stole from that professor.

I played a tabaxi rogue, which is very different than my normal character choices, which was really fun!
The dungeon master had a fun mechanic in the game where our adventuring packs have sort of three use plot convenient items.
I used one of mine for a tap to tap a barrel of whiskey, while I think everyone else in the group who used a use used theirs to make rope.
I followed a side quest of trading lots of items, going from an onion to a rock to a belt to a necklace which is almost certainly\footnote{out of character} cursed.
Unfortunately, I don't know if we're going to continue the story, so I will imagine that it's not cursed until that point.
At the end of the session, we had caught the cultist, and one of the people assigned to retrieve the scrolls had done so.
The three of us who were on a drunken adventure jumped into the portal that opened as the session ended.
Who's to say where we end up next!

496/52
\end{document}