\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{dungeons-dragons-2.html}{Dungeons and Dragons Again}}
First Published: 2022 July 9

\section{Draft 1}
I just reread \href{dungeons-dragons.html}{my\footnote{I think} last reflection on DnD} and it's funny.
Apparently the last I wrote about Dnd was also a one shot hosted by one of my friends.\footnote{the same one, coincidentally.}
This was a much smaller group, only the three of us.

As before, we claimed we would end at 9, but really ended at 9:30ish.
It was one of the group's first time playing which is always really interesting.
The way that people who aren't super familair with the mechanics of the game approach it is far different from the way I\footnote{admittedly inherently metagaming} do, often in really positive ways.

We three people met in the City of Arches, where we were hired by a Celf\footnote{Cow Elf, from the Haywilds. Yes I love my DM} to find a chest of his and destroy it.
Due to various shenanigans,\footnote{both in and out of character} we only got to a reasonable clue for where the chest was likely to be before we ran out of time.

I played a half-elf sorcerer with the gold-dragon sorcerous bloodline.
It was funny because the other two PC's were a high elf and a gold dragonborn, so in a way we were a fun little spectrum.
I really enjoyed the session, and I think it's more likely we continue this into a multi-shot, if only because there are fewer of us.
\end{document}