\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{dungeons-dragons-8.html}{Dungeons and Dragons Again}}
First Published: 2023 December 18

\section{Draft 1}
As I mentioned in \href{dungeons-dragons-7}{my last musing about dnd}, I made a character whose goal is rolling more dice more often.
I don't know if I actually optimized it, especially because a number of friends pointed out that spell slots are functionally infinite, especially in the kinds of combat that I'm likely to see.
Next session I get to fifth level, which doubles the number of attacks I can use, potentially doubling the number of dice I roll a turn.
That's pretty nice.

This session, however, was also a great time.
We began with a quick little combat, where we saw some demons\footnote{I think? I'm honestly not entirely sure what their exact bestiary entry was, in part because I am trying to meta game less often} and began to fight.
I missed on my first attack, which was sad, so used an action surge to swing again.

Once more, I missed.

That set me up to be flanked, which did almost all of my remaining hit points\footnote{the blood sacrifice is a feat that I need to play around with to find the most optimal usage I think}.
However, I managed to kill one monster on my next turn, and got another with an attack of opportunity.
At that point, it was more or less cleanup.

After we defeated the monsters, we were led into a room with puzzles.
The puzzles were all fun, and done more or less completely out of character.
It's always fun to have to actually think, rather than simply saying \say{my character thinks}.

When we managed to solve the riddles, we were given the ability to teleport to waypoints, which feels like it could be a fun mechanic.
We were offered the choice to return to the city we had come from, or to teleport further west.
Our group chose to go to the West.\footnote{we were explicitly told that we have to all agree to go in order to transport.}

Once there, we discovered a town of tieflings that were being plagued by spirits.
The story, as we dug into it, seemed to be that there was a chief who committed abominations\footnote{killing turtles and whales}, and something something punishment.
One of the consequences was that their harvests would rot.\footnote{like in the Disney film Moana}
We are currently split, staking out the properties overnight to see what happens.\footnote{spoiler, we level up but not much else}

Daily Reflection:
\begin{itemize}
\item Hobbies:
\begin{itemize}
\item Did I embroider today? Shoot! I forgot to pick it up from work. Need to remember to do that before leaving.
\item Did I play guitar today? I took today off, because I'm busy.
\item Did I practice touch typing today? At some point goals go from being something which frees by virtue of giving me order to something that causes stress. Right now this goal feels like that.
\end{itemize}
\item Reading
\begin{itemize}
\item Have I made progress on my Currently Reading Shelf? I listened to more of the second and restarted a series with my writing buddy.
\item Did I read the book on craft? I got a fantastic holiday present! It's an annotated\footnote{by my friend!!!} copy of a book on writing that they were recommended.
I'm very excited to start reading it.
\item Have I read the library books? I found the one I had misplaced, which is like reading.
\end{itemize}
\item Writing
\begin{itemize}
\item Did I write a sonnet? I'm about halfway through, will finish after this musing.
\item Did I revise a sonnet? Once again, had to restart a few times.
\item Did I blog? Eh, kind of technically.
\item Did I write ahead on Jeb? I finished today's chapter. Tomorrow I'll try to write Wednesday's chapter.
\item Letter to friends? Nope!
\item Paper? I did! I spent all day trying to figure out how distortion constants practically affect the computations I do. I think that I'm making progress, but I also think that I need to start doing more fancy machine learning/ optimizations.
\end{itemize}
\item Wellness
\begin{itemize}
\item How well did I pray? I have a vague memory of praying a rosary last night, but I don't know how real it is.
\item Did I clean my space? I tried to!
\item Did I spend my time well? Eh! I think that there is always room for growth, but I'm generally ok with it today.
\item Did I stretch? Still no.
\item Did I exercise? I walked a fair amount today, which felt like exercise with how windy it was.
\item Water? I started drinking more water once I got back to my apartment.
\end{itemize}
\end{itemize}\end{document}