\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}   
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{emptiness.html}{On Emptiness}}  
First Published: 

\section{Draft 2: 22 September 2025}
What does it mean to be empty?

Is it an absence?
The absence of my mother weighs on me daily.
The absence of food in my stomach or water in my system cries out to be sated.

Is it a void?
Atoms in the interstellar medium can go centuries or millenia without encountering another.
On days when I feel most alone, I feel like one of those atoms.

Is it clarity?
Only by emptying the space between viewer and object can the object be seen.
To empty oneself of doubt and fear is a power spiritual experience.

Is it calmness?
In the modern society, life is defined by motion and excess.
To stop, then, and simply be, feels as though it carries with it a sense of emptiness.

What does it mean to be empty?
Where is the line between numbness and emotional stability?
What are the words I can use to express the feeling of depression, where the weight of some unknowable and uncaring burden drags each motion.
Unlike the suffering of the martyr, there is no sense of purpose.

What does it mean to rest?
Is rest another form of emptiness?
Should I think of it as laying down the burdens I carry?
Should I think of it as a way to refill myself after carrying a heavy load?

When I write to the point no more words are there, have I created an emptiness?
I often refer to the feeling as having run my well dry.
Have I not, rather, filled the page and my mind with the ideas in the writing?

Thermodynamics assures that energy cannot be created nor destroyed.
Relativity assures that matter and energy can be interchanged.
In order to empty one location, another must be filled.

Is emptiness, then, a matter of perspective?

Is it possible to empty a space without filling another?
What about the void of space?
As space itself grows, the distances between stars grows as well.
Is that emptiness?

What does it mean to be empty, except to be removed from what is dear?

\section{Draft 1: 22 September 2025}
I don't entirely know what my goal is here.
Yesterday I started reading \say{Bluets}, a reflection on the color blue and a semi-memoir, at the recommendation of the bookseller.\footnote{What's the term for a person who works at a bookstore}
Near the beginning, it mentions that there was a French author\footnote{Stefane Mallarme} who, upon coming to athiesm, started referring to the sky as the blue, rather than the heavens.\footnote{literally l'azul, la ciel}
I thought about that, and the fact that I too find the use of words more meaningful than they may at first seem.
Does English's general usage of sky rather than heavens point to the general athiesm of modern Anglophone culture?

Then, I got on a train.
During the train ride, I did not reflect, I did not muse, I did not craft follies.
Instead, I played a new video game I got.\footnote{spellcrafter university}
While playing, the hours did pass away.
However, rather than ending the game feeling accomplished, or even satisfied, I mostly felt numb.

I went for a short walk after reading the opening 50 pages of \say{Bluets}, and I reflected on my own emotions.\footnote{opening section has a lot about blue and sorrow or whatnot}
I recalled that, when depressed, there's a painful sense of emptiness.
When I feel strong emotions, it can be tempting to say that I would rather feel nothing.
Remembering the words I used while feeling nothing, however, I am able to take the emotions more easily.

I do not think that I could write a long exploration of the color blue.
I think that, if I was to write a color-memoir, I would use the color red.

What does it mean to be empty?

As someone who frequently forgets to eat or drink, there exists the immediate physical meaning.
My stomach growls, my throat gets parched, and my body tells me that there is a void to be filled.

When I am able to meditate, or wake up from a blissful sleep, I find that my mind has nothing within it.
Unlike the negative emptiness of unmet physical needs, this is an emptiness of negatives.

When I finished playing the game yesterday, my mind was empty in a neutral to negative way.
The emptiness inside was not because I had only vague senses of positive sentiment, but because everything had been pushed down.

What does it mean to be empty?

I think that emptiness is a hard word, because to me it feels connotatively neutral.
That's good, insofar as like often we want a neutral word to describe both the positive and negative ways to have an absence.

My life for almost a year now has been marked by a pretty dramatic absence.

Is no longer being a student an absence, a void, an emptiness?

What is the positive way to say an absence?

Is it a calmness?
Is it idleness?
Is it clarity?

After all, in order for something to be clearly seen, it cannot have obstructions in its way.

Can I seek emptiness without filling myself to void?

\section{Daily Reflection: 22 September 2025}

\begin{itemize}

\item Did you journal by hand today?

Not today, nor the past few days. Might after doing this.

\item Did you do a folly?

Not for a few days.

\item Did you in some way, shape, or form advance the web novel?

See above.

\item Did you work on music, whether education or creation?

See above.

\item Did you work on book binding?

I think that this will leave the daily reflection, because I have enough things to read right now.

\item Did you work on another hobby?

Went on a hike with a friend!

\item Did you stretch? Really?

Not in too long.

\item Prayer?

...

\item Meditation?

Generally!

\item Reading?

Eh.
Did go to a bookstore and got some really interesting seeming books, and read part of one of them.

\item Minimizing screen time?

Ehhhhhh.

\end{itemize}

Current Pen List\footnote{for my own posterity, mostly}

\begin{itemize}  
\item Hongdian Black with Fude Nib: Diplomat Caribbean (8/30ish)  
\item Jinhao Shark: Diplomat Caribbean (8/30ish)  
\item Pilot Preppy: Private Reserve Electric DC Blue I think (I think since late june. I think)  
\item Sheaffer: Private Reserve Spearmint (since 7/15) (I Think)
\end{itemize}

\end{document}