\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{fasting.html}{On Fasting}}
First Published: 2022 February 23

\section{Draft 1}
Today is Ash Wednesday, which is a traditional day of fasting in the Catholic Church.\footnote{in case a single one of my readers was unaware}
Additionally, the Pope dedicated today as a day of fasting and prayer for peace in Ukraine.
So, I found myself fasting today.

Something major that I've noticed about my fasting self is that I struggle to focus far more.
I guess less so I struggle to focus and moreso that I struggle to begin working.
Once I start working, I have been able to finish at least as much as normal, though maybe at a slower rate.

This gives me some interesting knowledge.
Apparently if I am feeling unfocused and hazy in the future I should consider whether I've eaten enough recently.

Moving past my own experience of how fasting is less than ideal\footnote{which is not really the point of Ash Wednesday} for my work life\footnote{wow there are so many commentaries I could make here about American Grindset Culture}, I do think that fasting helps me refocus my days.
I haven't done as good of a job today recentering myself when I feel hungry on faith, and I think that's something that I can work about in the future.
That's something I could work on in the future I think, and it would probably make my life better for doing so.
\end{document}