\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\begin{document}
\doublespacing

\section{\href{feeling-safe.html}{Feeling Safe}}

As many of you know, I am a large white man. There are many aspects of these two identities that are incredibly beneficial. What I didn't really realize today, though, was how important that first identity is.

While getting ready to leave for a theatre show that we were both seeing\footnote{huge shoutout to my study abroad program for making it so available. It was an absolutely amazing show, \textit{Julie} by Polly Stenham, after the Strindberg show \textit{Miss Julie}}, I mentioned that I thought I might walk there, since I had time. It was around a 2.5 mile walk\footnote{4 km for those of you who believe in a different set of arbitrary units}, so I thought there might be an objection due to the length. However, the person I was talking to, who was also a white man, said he wouldn't feel safe walking there alone.

Now, I'm not sure whether it's that living in a census-defined \say{rural} area makes me unafraid and trusting of my fellow person\footnote{probably and not really, respectively}, or whether he grew up in a far different place, which led him to his comment. Nonetheless, it struck me that maybe the most important of my three identities is, in fact, large. It goes first when I describe myself\footnote{as you can read in the opening}, and maybe it belongs there. Where before I thought it was just the white man portion that made me feel safe, I'm reevaluating now to believe that it's a combination of all three characteristics that lets me feel safe in any situation I find myself in.

But, since the goal of my blog is to be happy and cheerful\footnote{partially in opposition to one of my inspirations}, I'll mention the walk. It was a beautiful walk across and then along the River Thames. I got there at sunset, so the river looked amazing. The show was fabulous, with amazing sounds and a flawless set. The acting was of the highest caliber, as was to be expected from its cast.

\end{document}

