\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{feeling-lucky.html}{Feeling Lucky}}
First Published: 2018 October 31
\section{Draft 2}
If I've learned anything these past few days, it's that I broke a mirror a little more than seven years ago.
For those of you who don't have superstitious family, legend says that breaking a mirror causes seven years of bad luck.
Now, I'm not saying this as a comment about my lack of luck these past seven years.
As far as I can remember,\footnote{not that my memory means much. I have great selection bias for memories} I've had a pretty great seven years.
However, these past few days have been somehow so much better.

To begin: yesterday afternoon I found out that I had won the Hamilton lottery.\footnote{i.e. I got the chance to purchase two front row tickets for 10 pounds each}
Of course, this was a slightly double-edged sword,\footnote{cue small violins} because I was seeing Book of Mormon earlier in the afternoon.
But, when I went to the first show, it was great.
I got free gummis, and had a great view of the stage.

After the show, I checked my email.
I found out that I had been accepted to a reception at Parliament a professor had applied for on my behalf.
That's super exciting.

Then I went to Hamilton.
I was in the middle of the front row, and was tall enough that I could still see most of the show.
At the end of the show, I got to take a photo with the conductor!

I love taking photos with techies, because they're always so much nicer than actors when I ask to take photos with them.
So, here's to another seven years of apparently good luck.
\section{Draft 1}
Apparently I broke a mirror a little over seven years ago.
Now, this isn't to say that I have had poor luck before this, but these past few days I've felt uniquely lucky.
First, yesterday I found out that I had won the lottery for Hamilton.\footnote{i.e. I had the chance to purchase two front row tickets for ten pounds each}
Today at Book of Mormon,\footnote{yes I was watching two shows} I was given free gummi bears.
Then, I found out that I had a great view of the stage for the show.
When I left the show, I learned that I would get to attend a reception at Parliament in two weeks.
At Hamilton, I learned that I was in the center of the front row.
Then, to end it, I got to take a photo with the conductor!
Overall, life is going great.
\end{document}