\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{first-day-of-class.html}{First Day of Class!}}
\section{Draft 2}
As those of you keeping up with my life may know, today was my first day of class at the British University I'm studying\footnote{partially} at this semester.\footnote{the anti-terrorism sheet the other place I'm studying at made us read says not to post identifying information on the internet}
It looks to be a really fun class!
The professor seems nice and helpful,\footnote{although he did comment on the fact that I was taking a lot of notes} the topic seems interesting,\footnote{and some of the information I learned in my summer research. Weird how the things you learn on a tangent come back as the subject later on} and the students seem nice.\footnote{not that my description really means anything, since that just means they didn't threaten or attempt physical harm on me, or tell me to be quiet without reason (and yes, me talking is reason)}
Unfortunately, felt a lot like I did when I would visit a class back in the days of the college search.\footnote{wow what an adventure that was}

For those of you who aren't in the college search,  who finished that ordeal long ago, or who simply don't understand what I'm talking about, a frequent part of many campus visits is a chance to watch a class take place.
You get to see students interact with each other and a professor in a somewhat live environment.
But, since you\footnote{or at least I} tend to visit these classes near the end of the term, there's a lot of context behind many statements that don't make sense.

That's more or less how I felt here.
The major is apparently fully tracked here, and only about 30 members strong.
So, each of them takes every class together, and takes the same class.
In effect, they have more continuity and similar educations to each other over the entire year of class they've had than Grinnell has in its one year Organic Chemistry sequence.\footnote{where in Organic 2, the professor might have to say \say{oh, Prof. So-and-so forgot to cover this. Ok here's a quick explanation}}

The professor would say things like \say{So-and-so mentioned this last spring, so can anyone remember (related topic)?}\footnote{which is also super cool and I love that the professor knows that much about what his colleagues do.}
Also, I don't really know much\footnote{or really anything} about Material Science.\footnote{and I've forgotten terms like \say{Van Der Waals}}

But, this isn't to bemoan my fate.
As I mentioned above, I'm still incredibly excited to learn about polymers!
Sure I may not have the same prior experience as the other students in the class, but that's half the fun!

\section{Draft 1}
As those of you keeping up with my life may know, today was my first day of class at the British University I'm studying\footnote{partially} at this semester.\footnote{the anti-terrorism sheet they told us to follow says not to post identifying information on the internet}
It looks to be a really fun class!
Unfortunately, I felt a lot like I did when I would visit a class back in the days of the college search.\footnote{wow what an adventure that was}

For those of you who aren't in the college search, or who finished that ordeal long ago, or who simply don't understand what I'm talking about, a frequent part of many campus visits is a chance to watch a class take place.
You get to see students interact with each other and a professor in a somewhat live environment.
But, since you\footnote{or at least I} tend to visit these classes near the end of the term, there's a lot of context behind many statements that don't make sense.

That's more or less how I felt here.
The major is apparently fully tracked here, and only about 30 members strong.
So, each of them takes every class together, and takes the same class.
In effect, they have more continuity and similar educations to each other over the entire year of class they've had than Grinnell has in its one year Organic Chemistry sequence.

The professor would say things like \say{So-and-so mentioned this last spring, so can anyone remember (related topic)?}
Also, I don't really know much about material science.
Overall, this class should be a really fun way for me to learn a lot, and prepare me for the real world!
I'll have to learn the information, and also the expected prior knowledge.
It'll be a great time!
\end{document}