\hypertarget{first-56-hours}{%
\section{\href{first-56-hours.html}{First 56 Hours}}\label{first-56-hours}}

My first 56 hours of life in London have passed me by, so it felt like a
good time to get some reflections out of the way. Since I've never lived
anywhere but Grinnell, I thought I'd be a little more culture shocked
than I was. To be honest, London feels a lot like Grinnell so far. Or at
least, London feels a lot like Grinnell during NSO. \footnote{New
  Student Orientation\\} I don't recognize most of the people, and
everyone is rushing somewhere. It might help that I'm in a part of
London that's fairly old, so the buildings aren't towering over me.

Some big takeaways from my first 56 hours:\\
1. Apparently when I don't have a 24/7 access to Google Maps and the
internet, I actually have pretty good navigation.\\
2. It takes around 30 minutes to walk around King's Cross Station if you
find yourself in that situation.\\
3. Apparently bagpipes aren't all that common here. In Grinnell I'm
surprised if a week goes by where I don't hear bagpipes, but so far I've
heard and seen none.\\
4. London weather is much nicer than Grinnell's.\footnote{Apologies in
  advance for people who like the heat\\} When I walk out in the morning
it's almost, but not quite, too cold for my shirt and slacks. By 1700
\footnote{5pm}, it's heated up to what feels like the peak of the day,
and it's only slightly uncomfortable to powerwalk through the streets.\\
5. It's a lot harder to find a Catholic church in London than in
America. I've so far seen a few Church of England churches, a Baptist
church, an Ethiopian Reformed Church, and a Christian Scientist
gathering place. Looking at Google Maps, however, I think I should be
able to find one.\\
6. The underground is really simple to navigate. I'm still not sure how
the busses work though.

Thanks for reading!\\
Jonathan

~
