\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{first-day-of-class-F2022.html}{First Day of Class}}
First Published: 2022 September 7

\section{Draft 1}
Today was the first day of the new semester and academic year.
Unlike \href{first-day-of-class-S2022.html}{my last post about a new semester}, I didn't see friends.
I also didn't have any class today.\footnote{pun intended}

Instead, I started my day by TA'ing, which looks like it'll be fun.
I'm helping with the graduate instrumental course, which I'm very excited for.
Tomorrow I have my first actual class period, which I'm also pumped for.

In other exciting news, I got free breakfast\footnote{coffee and a granola bar and a bagel with cream cheese} and lunch\footnote{cheesy bread} from different organizations giving things to students today.
I also gave blood, and got a t-shirt for that, along with other various knick-knacks from a fair.

Of course, there were some not bright parts of the day.
On my walk to work I saw some horrible anti-semitic hate chalked brightly and in large letters in a central campus location.
That didn't really set me up for a happy day.
While giving blood they missed my vein and wandered around for a while, jabbing the muscle more than once.\footnote{my arm still hurts and I'm not sure if it's supposed to.}

But, I'll move on from the less than happy and back to the joyful.
I found out my band is planning to play a song I wrote next Monday!\footnote{now I need a title}
I got a free donut from someone whose birthday it was, and I got to go to a meet-and-chat with the person who discovered pulsars.
I also finally placed requests for the different books which explain early thoughts on the harmony of the spheres.

All in all, this semester is shaping up to be a fun one!
\end{document}