\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{flash-fiction-229.html}{Flash Fiction Friday}}
First Published: 2023 December 1

\section{Draft 1}
It's another Friday, which means that it's time for another edition of \say{I try to do Flash Fiction Friday}!
This week, the friend I did NaNo with is joining, which should be fun.
The theme is nebulous roads.
 
My initial thought, as always happens when there's a word immediately preceding roads, is to do a parody of John Denver's seminal work.
I'll keep the fun part of that energy in mind as I work on the actual project, for all that I don't know quite what I'm going to do.
I know that I need to do a sonnet today, so there's a voice in my head that says I should work on a sonnet, and I might as well let that voice win for at least a little while.
Unlike normal, where I hand write sonnets, today I'm going to try typing it out.\footnote{because the writing app I use is incredibly motivating to me, and honestly basically no other reason.}
 
What are nebulous roads?
The prompt suggests they could be real roads that are obscured by fog as easily as they could be roads that do not, strictly speaking, exist.
 
I find that I am drawn to the idea of a desire path right now.
They aren't roads in the strictest sense, instead being passages worn by the repeated choice of people to take a shortcut.
Most of the time, they are not a function of a single person.
The single exception is probably on fresh snow.
The way that a clear night on fresh snow looks is something completely unique and almost ethereal, and that feels like a good place to start.
 
One draft of a sonnet through, I already remember why I don't always write in sonnet form.
For all that it's nice to have something so rigid, I do really like the option to have triple meter.
There's absolutely a part of me begging to delve into the fact that even time is now considered the standard, while in early music, triple meter was considered the perfect version.
That's too far from the prompt, though, so that lecture will be reserved for another day.
 
The rest of the day passed far too quickly, and so I will not be revising the sonnet again. 
 
I think something that could be helpful for me\footnote{I'm writing this after \say{lecture will be reserved} even though it's going to come at the end of the post}, given how long the daily reflection is, is to go through the list often throughout the day, so I have more reminders.
 
\begin{itemize}
\item Hobbies:
\begin{itemize}
\item Did I embroider today? I did! I did a few rows which was nice. 
\item Did I play guitar today? I did! I played a few scales and did some warmups. Not very much, though, because I did it first thing in the morning and was tired. 
\item Did I practice touch typing today? I did! Didn't do a great job, but I tried, and that's the only really important part. 
\end{itemize}
\item Reading
\begin{itemize}
\item Have I made progress on my Currently Reading Shelf? Yes! I read about a chapter. 
\item Did I read the book on craft? I've chosen to read \say{Writing Well Ninth Edition} by Donald Hall and Sven Birkerts. It's a fantastic book, and I'm in love with it from the first pages. 
\item Have I read the library books? Not yet, but probably will when I post this. 
\end{itemize}
\item Writing
\begin{itemize}
\item Did I write a sonnet? I did! As you might guess from the fact that I blogged about it, I wrote on the theme of ethereal roads. 
\item Did I revise a sonnet? I revised as I wrote, but I still don't know if I really know how to revise one generally. Probably worth asking my poetry friend. 
\item Did I blog? Look at this fun little blog! 
\item Did I write ahead on Jeb? I finished the chapter this morning, which was nice. 
\item Letter to friends? Nope! 
\item Paper? Looked at some fun data! 
\end{itemize}
\item Wellness
\begin{itemize}
\item How well did I pray? I remembered to start the day with prayer, even if last night's rosary wasn't great. I then went to adoration for an hour which was nice. 
\item Did I clean my space? I did! I went for the lowest hanging fruit. 
\item Did I spend my time well? So far I have, but the day is mostly begun, so doesn't really count yet. 
\item Did I stretch? I did! This morning, which is nice. 
\item Did I exercise? I did a pushup and a body weight squat which is good. 
\item Water? Not enough. 
\end{itemize} 
\end{itemize}\end{document}