\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{font.html}{Font!}}
First Published: 2018 November 2
\section{Draft 2}
Today I began mapping the keystrokes on my keyboard to Celtic knots.
I've mapped around a quarter of the letters,\footnote{A,C,D,E,F,G,Q,R,T,W,X,Z,a,b,c,d,e,f,g,q,r,s,t,w,z,z, (space),1,2,3,4,!,@,#,\$.} and have been able to begin drawing with what I've made.
It may not have been one of my most productive four hours in terms of benefit to the world or self, but it was productive in the sense of losing myself to the project, if only for a bit.
\section{Draft 1}
Today, I made a font!

Technically.

Maybe.

Let me check the definition.

Maybe?
I'm unsure what I made.
I guess: I made a series of images that correspond to the letters on the computer keyboard.

Technically, even if I were to call it a font, I'm missing most of the characters.
The characters I've mapped are: A,C,D,E,F,G,Q,R,T,W,X,Z,a,b,c,d,e,f,g,q,r,s,t,w,z,z, (space),1,2,3,4,!,@,#,\$.
What I made was a Celtic knot generation font.
So, each letter had a different symbol attached to it, so that I could make the knots I've been drawing more easily and quickly.
It was a semi-productive way to kill four hours, and I'm not quite done yet,\footnote{I don't have every case covered for things I may want to draw} but I had a good time.
\end{document}