\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{game-night.html}{Game Night}}
First Published: 2023 November 3
\section{Draft 1}
Interestingly enough, \href{writers-block-5.html}{one day ago today} I sat in front of my computer without any idea what I would blog about.
Today I have a slightly different issue.
I am going to play games with friends tonight,\footnote{specific games not listed for a variety of reasons} and had\footnote{have?} every intention of musing about that experience.
However, as I may have mentioned before,\footnote{though I'm not sure when, given that I more or less stopped blogging} I've started writing on a website which I find very helpful for getting me to write often and well.
One feature of the site is that it sets semi-arbitrary goals for me to hit with regards to word count and pace.

Unfortunately, though the overlap is close, it does not always align perfectly with the number of words that I have left to write in a chapter of my web novel.
In this case, I finished a longer than standard chapter with 200 or so words in my arbitrary goal.

\say{But wait,} I hear you\footnote{I don't know why I assume my readers (who don't exist) are going to loudly comment on my writing} ask, \say{why not simply let those remaining words go to waste?
Or, even better, why not simply start another chapter?}

To that, I reply,\footnote{I guess that since I did, in fact, take a break from writing in the middle of the last footnote, I am the reader} \say{I hate losing progress for work that I've begun, and I need a blog post more than I need another chapter of my book at this exact moment.}

Now that I've addressed the concerns, I can start writing about the game night I went to tonight.
It was a good time!
I got to spend time with friends, and I got to play a fun game of chance and skill!\footnote{or many iterations of a fun game of chance and skill, I suppose, depending on the framework you take.}

Daily Reflection:
\begin{itemize}
\item Did I write 1700 words for NaNoWriMo? Once again, I managed a 2000 word hour with a friend, and did my writing for the day.
\item Did I write a chapter of Jeb? I did! I finished it and sent it to my beta reader hours before this post. Once again, it felt even easier today than yesterday.
\item Did I blog? As you can see, we are now on day four of the streak.
\item Did I stretch? I did! This morning no less.
\item Am I doing better at prayer than a rushed and thoughtless rosary? Once again, I did the Angelus.
Last night's rosary was pretty rushed.
\item Am I doing a good job writing letters to friends?
I got a friend's address, which is technically progress in writing letters.
Tomorrow I should actually write a letter, though.
\end{itemize}
\end{document}