\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{getting-lost.html}{Getting Lost}}
First Posted: Day beginning 2018 October 13
\section{Draft 1}
Today, I was planning on posting about my trip to a museum.
But, I'm also in Scotland.

Since I was in Scotland, I decided that I should try to take the opportunity ot listen to some Scottish Folk music.
Last night, my friends convinced me not to go.
So, tonight, I decided to go.

Of course, it turns out every pub operates on the \say{Folk Music Friday} \say{Standard Pop Saturday}\footnote{i don't know if either of those are real, but I liked the alliteration in the first, so forced the second} realm for music, so finding folk music was hard.
I did end up being able to find a single pub with it, around a mile away.

By 2300\footnote{11pm} I was feeling tired, and so routed myself home.
After a short walk, I found that the hotel I had routed myself was a different version of the hotel that I was staying at.
So, I routed myself to the correct one.
Then, at 2326, the unthinkable happened: my phone died.
I became slightly worried.

But, I found out that people were very willing to respond to \say{hello, do you know how to get to the train station?}\footnote{I knew my hotel was near the train station, so assumed I could find it from there}
Of course, I soon learned that there were two train stations.
Thankfully, my gut did tell me the right one, so I began heading.
Somehow I ended up on a gradually curving set of streets which led me in a circle.

Talk about disappointing.
I was so excited to see familiar sites, only to realize that it was where I had just been.
Eventually, I found my way to the train station, although it was much larger than I remembered.
I found a hotel, which had a map and a very helpful man who was willing to draw directions to my hotel.
I found a familiar site finally, and made my way home.

Highlights: two drunk men, who \say{aren't from around here} asking everyone near me for directions to the train station.
But, I did hear some music, even though it was a little disappointing.
I also managed to take more than 30000 steps, which is a lot for me.\footnote{it helps that I also climbed Arthur's Seat} 
Time for some sleep.
\end{document}