\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{goal-updates.html}{Goal Updates and Scheduling}}
First Published: 2024 December 10

\section{Draft One:}
I know that I literally made the goals less than a week ago, but I have already forgotten them.  
With that in mind, I think that it might be good to start going through the goals I've accomplished, and organizing the ones I have left so I have a reminder.

\begin{itemize}  
\item One offs:  
\begin{itemize}  
\item Talk to boss about Ph.D. timeline  
\item Pick a topic for a science communication article  
\item Find an occasion I could write a song for  
\item Make a list of the stretches I'll do each day  
\item Find a place to volunteer  
\item Paper hit list  
\item Read the comments on the serial  
\item Compile a list of people I want to write letters to  
\item Muse about macros and micros  
\item Compile a list of 20 meals that I can make, with their ingredients (inc. shelf stable or lifetime), time, effort level, and nutrition info  
\item Come up with an ordered list for what I'll read  
\item Figure out my motivation for each book and have it as the bookmark  
\item List of things that need to be cleaned and the frequency  
\item List of things in my life  
\item Decide on what I want to draw right now  
\item Make a list of musings to do  
\item Block out time on Sundays for gospel reflection  
\end{itemize}  
\item Weekly:  
\begin{itemize}  
\item Read a pop sci article a week, making notes about how they work  
\item Spend 30 minutes 2x a week working on writing the song  
\item On Sundays, write a hymn harmonization for one of the hymns we sang  
\item Muse on Sundays about the Gospel  
\item Read readings on Saturday  
\item Ten minutes 4x a week on drawing  
\end{itemize}  
\item Daily:  
\begin{itemize}  
\item Define how I'm feeling each day at start and end   
\item Practice guitar daily (at least one scale and a chord progression)  
\item Muse daily  
\item Stretch Twice a day  
\item Walk to the gym every day  
\item Do daily affirmations  
\end{itemize}  
\end{itemize}

Having forgotten about most of these, stretching is really the only one I've been particularly good about doing. I did write a hymn harmonization on Sunday, though, which I suppose is a good thing!  
I think that now is a great time to begin putting explicit time markers on my life.  
I know that my schedule will change when I begin to teach again next semester, but the first of those is at 11 AM, so in theory I can schedule anything I like before then.  
It might be worth considering locales as well.

For those events which happen multiple times a week, that means setting aside multiple blocks of time.  
For writing the song, I think that one time on Sunday makes sense, since I'll already be doing music, and the other maybe on Wednesday.  
Great, they're in at 8AM those two days, and I'll for now plan on doing them at home.

For pop science, I think that Friday mornings could be a good day, and it would be nice to do them in a coffee shop.  
That means I need to pick one out on Thursday and print it out, since I'd like to avoid having to use my computer.\footnote{though I suppose the ipad might also be a good choice.}  
I've booked it an hour a week, starting at 8am this Friday.

When do I want to work on drawing?  
Realistically, whenever.  
I know that I want to do it at home, though, if only because it's embarrassing to have others see my work.  
MTWR makes sense to me?  
I get a long weekend off of it, which would be cool.  
In at 7 50 am so that on Wednesdays it will not conflict with music time.  


I have scheduled 3 to 5 pm on Sundays for reflecting on the Gospel and writing the hymn harmonization, and 4PM Saturday for prereading it.

That takes care of all the weekly events, so now it's time to start scheduling the daily events!  
I recently got an app that asks me about my day at start and end, and I'm going to treat that as good enough for now.  
715 to 725 will daily be guitar time.  
I haven't quite figured out where musing is going to fit into my schedule, but I think that it might help to figure out what my days actually contain on a weekly basis first.

725 to 740 is booked each day for the first stretch, and the second will happen before bed.  
I don't think that I want to do daily affirmations, and I'll plan to walk to the pool daily at 1050 am, except for Wednesdays, when I'll move it to 10 AM.\footnote{and other days maybe, whenever I have an 11am meeting}

Wow, it feels kind of nice to have the whole day scheduled out like that. I know that tomorrow we will not be able to follow the schedule exactly, because it takes me more than 20 minutes to get ready and to work, and I have to be at work at 850.  
Guess everything gets shifted back 15 minutes!  
I hope that I'll find a way to make this routine both helpful to me and also maintainable.  
\end{document}