\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{grad-recruiting.html}{Grad Recruiting Weekend}}
First Published: 2022 March 11


\section{Draft 1}
I was tempted to write today's post about how, when I'm underslept\footnote{as now}, I lack the ability to do the work I want and need to do.
But, I gripe enough without the explicit permission.
So, instead I will be writing about the first day in my department's Graduate Recruiting Weekend this year.

Our group is currently fairly full, so we are not interested in having too many new students.
That being said, it did not seem like too many students would want to join us, based on the applications at least.
But, the draw of space and chemistry seems to have pulled analytical students this year like my year, and we've got new interested students.
I wonder if they will remain interested through group joining.
Certainly they all seem brilliant and qualified.

Anyways, on to recruiting.
I got to hang out at the check-in station for a few hours and chatted with a good number of recruits.
Then I showed my recruit our office and we did a lab tour.
I went to the poster session, where I finally met one of my committee members.
And I ended the night at a dinner where the department did not get enough food for everyone on accident, which is sad.
That being said, I still had a great time.

I miss seeing my chemistry friends when I don't see them, and I love that we're all in a loose web so I keep making new ones.
\end{document}