\hypertarget{how-im-keeping-track-of-my-time-abroad}{%
\section{\href{how-im-keeping-track-of-my-time-abroad.html}{How I'm Keeping Track of My
Time~Abroad}}\label{how-im-keeping-track-of-my-timeabroad}}

I don't tend to keep track of my daily movements for a variety of
reasons. The biggest of these is that one day in Grinnell is rarely much
different from a handful or more other days, and those that are I don't
always want to remember.

The second reason I don't track myself is the time required. Writing
takes time, and I'm usually doing or recovering from doing.

Finally, as far as I can tell, most of the time I'm the only one who
really cares what zany adventures I've gotten up to. Obviously my
professors care if I show up to class \footnote{or at least I hope that
  they do\\}, my coaches care that I show up to practice, and my friends
and family care that I show up at prearranged times. Other than that,
though, I really doubt that anyone cares whether I studied for three
hours in Noyce or in Bucksbaum.

None of these apply to my time abroad. With no frame of reference, every
day in London feels very different. So far I have far more free time
than I know what to do with \footnote{assuming (accurately) that I don't
  have the attention span to work on required and recommended readings\\}.
Finally, I've had at least a few people mention that they want to know
what I'm doing while abroad.

So, for those of you keeping track at home, that was 224 words to
explain why I'm writing, but not addressing the title of how \footnote{255
  as of the end of this footnote\\}. I'm keeping track of my life in a
plethora of ways. Like in Grinnell, I send the minutiae of my life to
friends via various instant messaging platforms. Unlike in Grinnell, I
update different social media far more frequently, I hope not to the
annoyance of my friends there. I'm writing this daily journal \footnote{obviously}.
Finally, I'm maintaining a hybrid journal. That is, I'm writing a
journal that is partially digital and partially analog. I'll talk about
the nitty gritty of that later, but it's been probably the source I use
most to record my days.
