\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{juggling.html}{On Juggling}}
First Published: 2022 September 13
\section{Draft 1}
Today I started juggling again after a long hiatus.
I started practicing on my walk to work, and it's much harder to relearn juggling while walking\footnote{relearn juggling and while walking are distinct here. I was learning to juggle and walk for the first time} than I really thought it would be.

I also learned my first trick!
It's called Sky High.
Literally all you do is throw one of the three balls higher each time it comes around.
I'm currently learning the trick tennis, where one ball gets thrown differently, but that's much harder than I expected.

When one of my friends watched me juggle, they commented that it seems that I am constantly showing new skills that they never knew I knew.
It remains strange to me that people don't have more hobbies and skills than they have time to practice in a day.
I realized and remarked to a different friend that my life would be easier if I had fewer things I was interested in learning, so I could actually devote the time that any of them deserve.
Instead, I think I'll continue juggling until I misplace the balls, then not for a few years again.

Still, I think it's worth remarking on what got me into juggling.
In high school I went to a theatre camp.
One of the breakout sessions was learning how to juggle.
While I didn't learn it perfectly there, I learned enough that I could teach myself when I had time.

That summer I was working at the city pool.
The pool had\footnote{has, to the best of my knowledge} a tube slide, and a lifeguard needed to stay at the exit to make sure the tubes get out safely.
That summer there were many days that were cold enough that not many people wanted to go down the slides, and fewer lifeguards wanted to wait in the water.
So, I had hours on end to sit and practice juggling with the rocks in the pool.
I still feel kind of like I'm cheating when I juggle with bags or balls that are the same size and not jagged rocks.

Anyways, juggling is in many respects like most any other skill that I've learned.
The second you start demonstrating even the most basic competence in it\footnote{here being able to do three balls with two hands for a dozen throws or so}, people are amazed at the skill you learned.
It's always weird to me, because I'm pretty sure it took me like an hour of dedicated time to get to that stage the first time I learned how to juggle.
But, equally as exciting, a few other people will comment on how they juggle\footnote{or whatever the hobby is}, and it's really fun to bond with others over shared hobbies.
Also, the basic skills are fun and the advanced skills often look easier for all that they're significantly harder.
\end{document}