\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{mind-drains.html}{Mind Drains}}
First Published: 2022 February 23

\section{Draft 1}
When I'm not in mentally draining situations I often forget how easily mentally drained I am, and what situations can drain me effectively.
Today I had a reminder of what can cause it very easily.
As I mentioned in yesterday's post, I was very engrossed in a book yesterday.
I almost finished it before I went to bed last night, which was a little more than an hour past my bed time, itself an hour past when I like to be off of my devices.

So there is one effective way to set myself up for mental exhaustion: going to bed late.

A second thing is that I procrastinated an assignment with a hard deadline of today until today.
The homework was very mentally taxing, made more-so by the looming deadline I had while working.
When I felt my mental strain start to build, I realized that I would not have time to finish the assignment before its due date.

Point two and three: Do mentally exhausting work and do not give yourself a break during it.

I also realized that I was missing some files that I really need, and I am still not totally sure where they went.

Point four: existential dread.

Finally, after I turned in my homework, I remembered that I have another, similar assignment due tomorrow.

Point five: knowing you will repeat it again.
Anyways, I really hope that I will be better about keeping my schedule in mind in the future, because everything suffers in my life when I don't take care of any part of it.
\end{document}