\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{missing-time.html}{Missing Time}}
First Published: 2018 November 3
\section{Draft 2}
People who know me might know that I'm somewhat flighty.
Despite this, I really try to build my days around touchstones, or events that are required at a certain place and time.
This works nicely in a majority of my life, as academics and extracurriculars provide this.
Somehow, having anything to do in a day makes me keep track of the entire day so much better.

But, some days don't have any events.
Even Sundays, where I attend Mass, don't feel like an event, because there are multiple options for time.
These past two days in particular, I feel as though time has simply passed me by.
I don't really know where the last 48 hours went, though I know they must have gone somewhere.
Such is life I suppose.

\section{Draft 1}
Normally I keep my days very structured.
While it isn't the structure that most people think of,\footnote{i.e. plans of minutae} I have the entirety of my days flow around focal points, as a way to orient myself.
So, when I have days with no imposed structure, they tend to disappear.

Today is a great example of this.
I woke up at nearly 11 am, because I had no reason not to.
Over the next hour and a half, I apparently wrote.\footnote{based on my journal}
After that, I think I watched a tv show until 5, when I helped people make dinner, and then did activities with friends.
But, the day still feels as though it's barely started.
I don't like this feeling.
\end{document}