\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{mission-trip.html}{Mission Trip Recap}}
First Published: 2023 July 27
\section{Draft 1}
At the beginning of the month, I volunteered for a local mission trip.
For those not in the know, mission trips are often experiences for middle and high school aged youth to travel somewhere, do nominal service, and pray about it.
I\footnote{like many people} tend to take issue with the fact that they often require very expensive travel and that they do minimal actual good.
Likely to help combat that trend, my local diocese has a program which does most of those same elements but locally in the diocese.

It was a really incredible event, for all that it was a bit of an accident.\footnote{I meant to sign up for a high school trip, misread H and M, and then volunteered to do the middle school trip because it was the days that actually lined up with my schedule.}
Over the three days that we were there, we helped maintain the diocesan offices,\footnote{which I think is important, for all that I absolutely see why that could feel less than ideal to many} helped a family with a newborn to maintain their home,\footnote{the project that I (being brutally honest) felt least good about (though still very good. Service is service, after all)} and then finished the lawn work that other groups had done for a woman with advanced MS.\footnote{which is probably the project I feel best about.}

I, along with another leader who had not done this before, were responsible for shepherding some middle schoolers, directing them in their work and making sure that they were safe and engaged.
It was a shockingly easy job, especially compared to the horror stories I had been told.\footnote{I was told many students would just sit and refuse to work. All of mine were beyond thrilled to be able to help people.}
On all three days, we finished every task well ahead of schedule, which was a really nice feeling.

As mentioned in one of the footnotes,\footnote{which feels wrong to reference} the third day was the one that I felt best about.
When we were packing up, the woman made her way to the front of her home for the first time in weeks.
She teared up upon seeing all of her hedges neatly trimmed and the detritus in her lawn cleaned up.
Knowing that trimming a hedge, something that is not difficult for me, means so much to someone who cannot really made me reflect on the many blessings I've been given.

Of course, being a Catholic camp, there was a lot of time for prayer.
We had Mass every day, and I was even asked to do the readings for the first day's Mass, which was really nice, if incredibly stressful.
It is also a camp, and so there were bonding activities, and time for the kids to play.

All in all, it was a fantastic experience, and I really hope that I'm able to do it again next year.
I'm sure that there is more to say about the experience,\footnote{like the fact that I was told to join the priesthood, seeing my old parish priest, doing morning prayer while looking at the sunrise, etc} but I think that this is enough detail for me to recall the event later on, which is one of the primary goals of this blog.

\begin{itemize}
\item I cleaned the smallest possible amount. I did move a friend out of their home, though, which counts to me.
\item I did blog today\footnote{obviously} and also did the day before. I think I'm getting back into it.
\item It was\footnote{is} far too hot for me to feel comfortable exercising outside. I did spend two or three hours this morning moving a friend, though\footnote{as mentioned above}, so I think that counts in many respects.
\item As \href{conference-2.html}{with a week ago}, I set my alarm for half seven and woke at six. I'll still be rising earlier tomorrow.
\item I made it to the chapel for a quick prayer this morning, and I did night prayer tonight after the theology discussion I went to.
\item About halfway through a chapter, which I think is as much as I can do tonight. I'm beat from the day\footnote{and more than doubling my exercise and move rings (for those who don't know what that means, sorry)}
\item I did not do poetry today, but I did think about the nature of language and poetry, which is close enough to me
\item I again managed to write a letter. That's really nice, for all that the explicit goal for the month was empty my pile. The fact that it's nearly doubled feels a little unfair to me.\footnote{Curse you past me}
\end{itemize}

611/168
\end{document}