\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{musescore-4.html}{Musescore 4 Initial Review (Rave)}}
First Published: 2022 December 17

\section{Draft 1}
So I may have completely lost myself and ability to blog these past few weeks, but now seems as good of a time as any to get back into the swing.
Musescore 4 recently came out, and it's an absolutely wild experience.

Musescore\footnote{for those who don't already know} is one of the two music engraving software\footnote{still bothers me that it's not softwares} I use.\footnote{along with Lilypond}
It is Free\footnote{capital F because it's open source etc}, and the latest version completely overhauled most of the UI, which is nice.\footnote{The scores also default to being much better laid out}
The part that really gets me excited, though, is the difference in how music playback works.

The lead of the project made a long video discussing it, but the summary is basically that there are now sampled sound packs available, and they really bring the quality of the sound so many levels up.
I honestly somewhat forgot that not all of the notes were computer generated when I was listening back.
It makes it so much more fun to write music when the sounds coming out are nicer.

I said above that I didn't really get excited about the UI, which is somewhat true.
It in many regards is the ideal UI, in that you hardly notice it.
I was entering notes generally without issue, and that's really what software is for.

On a tangent, I told one of my old professors about the new release, and he pointed me to another app which has AI sing vocal words.
Now I can finally know what my choral pieces sound like sung!
\end{document}