\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\begin{document}
\doublespacing

\section{\href{my-wonderful-brothers.html}{My Wonderful Brothers}}

Those of you who know me likely also know my brothers\footnote{despite the fact that many people are unable to tell them apart, they still claim to be distinct entities}. This post seems like a great way to talk about how amazing they are, since I sometimes forget to do that enough.

My older brother is everything an older brother should be. He's smarter, kinder, and more generous than me. He follows the rules, and is just all around the perfect older brother to have. Because of him, teachers assumed I was trustable, groups accepted me, and just generally his presence made my life better growing up.

Now that we're older, he's still amazing to have around. He's incredibly knowledgable about a variety of topics that I'm beginning to find interesting. He, along with a mutual friend of ours\footnote{ who, despite the beliefs of some prospective students' families, is not my brother}, share books that we enjoy reading, as well as share interesting short writings as we find them. When I need help with Excel, or really any software that a business person is likely to use, he's there and willing to drop most things to help.

But, as I mentioned above, I have two brothers. The younger is really everything I could hope for in a younger brother. He is also smarter, more musical, and far more technically adept than me. For all of the softwares that aren't common business ones, he either already knows them, or is willing and able to quickly learn them to hold my hand as I try to learn them\footnote{the ambiguity in the sentence above is because many times I'm not sure whether he knows how to do what I want when I ask, but he always gets there quickly enough}. He's a brilliant musician, and I love listening to him perform\footnote{even though I have still procrastinated listening to his improvisations}. He's much wittier than me, but also much more sly about it.

Just as my older brother is incredibly knowledgable about topics I know nothing about and am interested in, my little brother is too\footnote{they're both also incredibly knowledgable about topics I know nothing about and care little about, topics I also know much about and care about, and topics I know much about and care little about}. He's well versed in music theory, and helps me a lot when I need a sounding board. He also has shares my impulsiveness, but in a much more constructive way. For instance, right before I left, he decided that with the extra fabric he had\footnote{how he ended up with extra fabric is a different story}, he would make a shirt. He'd never made clothes before, didn't have a pattern, and still did a passable job.

In the interest of full disclosure, my little\footnote{in my mind, even if reality says otherwise} brother is the reason for this post. I prefer writing my documents in LaTeX \footnote{because I'm pretentious like that}, and WordPress doesn't really support that. So, I asked him to build me a website, since we own a domain for some unknown reason. He did, and assuming that I'm able to follow the (incredibly simple) instructions he gave me, my blog will be moving to \href{j.rebelsky.com}{j.rebelsky.com}. Depending on how my ability to not break software goes, I may stop updating this site.

In summary, I have the best brothers anyone could ask for, and I'm grateful every day that they're in my life.


\end{document}
