\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{nanowrimo-3.html}{NaNoWriMo Update}}
First Published: 2022 November 7
\section{Draft 1}
It's officially one week into NaNoWriMo\footnote{which I and an old FAQ pronounce /raj/, despite my friends assuring me it's /ri/}, and I'm currently doing well.
I've managed to write at least my word goal every day, and I'm almost a full day ahead now.
Since the last time I attempted it\footnote{in 2011}, the website has changed a lot.
It's much more user friendly now, and it's far more gamified as well.

There's even an achievement for hitting par\footnote{word goal for the day} every day in the month, which has been my primary motivating factor.
One thing I have noticed, though, is that the daily goal appears to update based on how many words you have left to 50000.
I wonder if that means it'll set itself to 0 when I surpass the goal.\footnote{currently scheduled for the 27th, but I'm also writing faster as the days go on, which is interesting.
I can't tell how much of that is due to increases in typing speeds, increases in knowing what I want to write, decreases in forced revision and pauses for words, or decreases in average word length. I'm sure there's some way for me to track it, but I don't really feel like testing any of it right now. All I know is my last 10 minute writing session was over 700 words, which is about as fast as I've scored on some typing tests.}

Huh, also apparently there's more text in this document in the footnotes than in the actual text.
I guess my asides are more content than I expected them to be.
I\end{document}