\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{novel-update-2.html}{Novel Update}}
First Published: 2022 February 18

\section{Draft 1}
As I promised, I will be using my novel updates as a way of generating content when I'm mentally exhausted from writing a novel.
Today I wrote almost 3000 words, not including the code I wrote so I knew what words to write.

If that sounds a little strange, I guess I should explain.
I don't remember if I have mentioned that the book I'm writing is a LitRPG, which stands for Literary RPG\footnote{RPG stands for nothing here because its not a game}
More or less, imagine a roleplaying game but instead of playing, you're reading.
That is to say, characters have statistics and can train and specifically watch numbers go up when they do.
As a result, readers of this genre tend to be far more accepting of weird contrivances that are due to math.

I decided that I wanted there to be some way that hard spells are more difficult than easy ones.
What I decided on is layers of connections between the points which make up the spell.
The first level is fairly simple, energy flows from each point to its neighboring point.
The second level has energy flowing from each point to the square of it mod the number of points.
So, the first point flows to itself, the second to the fourth, etc.

Since the spell I had him learn has\footnote{completely arbitrarily} 25 nodes, the sixth piece connects to the 25th slot and the 11th slot, since those add to 36.
The eighth connects to the twenty fifth one twice, since 64>25+25.
Somehow I wrote almost 3000 words of a character learning this himself, and I really hope that my alpha reader doesn't find it too boring.

That's about all the writing I have space for now, since it's already past my bedtime and I completely lost track of time writing.

\end{document}