\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{novel-update-6.html}{Novel Update}}
First Published: 2022 April 28


\section{Draft 1}
I'm less than 2000 words away from my monthly goal and I've been writing nearly 2000 words a day recently, so I really believe I can make it.
I've realized that the plot is steadily progressing less and less with each chapter, and I'm not sure how I feel about that.
On the one hand, I'm writing because it's interesting to me and the scenes I write are interesting now and I feel set me up for other interesting future events.
On the other, I think I've so far spent 5000 words talking about growing magical cotton and probably have another 5000 coming.

I've finally formalized some of my thoughts about themes I want to include in the book, which is nice.
I don't quite know how to subtly weave them in so it's not just a \say{By the way the world was actually terrible this whole time} without also doing the reverse of \say{do you get it yet? the message that I'm beating you over the head with?}
I don't think that it should be a fine line to walk, but I feel like it is one.
I've taken the advice to have time pass less explicitly, though I'm back to being explicit again, which is a little sad.
On the other hand, I have him working constantly over the span of two days, which in the grand scheme of things isn't that much.
I think I said the next big plot point would occur in two in-universe months, but I also never gave actual lengths for those, so I guess that's also optional.
Anyways, all this to say I greatly enjoy writing the book, and I'm optimistic that I may be able to come to a satisfying book ending in the next 40000 words or so.
\end{document}