\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{open-mic-3.html}{Open Mic}}
First Published: 2022 October 31

\section{Draft 2: 1 November 2022}
Last night went well!
I ended up doing my two original songs and Stan Roger's \say{Maid on the Shore,} because it's a little bit spooky, which is good Halloween vibes.
I had another person comment that the song seemed incredibly sad, and that I seemed sad while performing it, which is fun.
It's especially fun because they then commented on how not sad I seem otherwise.

I ended up staying later than normal, and played another set.
That one was significantly less prepared, so I did two more Stan Rogers songs that I kind of know.
It could have gone better but, that's the way the cookie crumbles.
I realize I never actually figured out how to end them in playing, so it was awkward.

\section{Draft 1}
Tonight I'm playing at the open mic alone for the first time.\footnote{I technically did it once or twice in undergrad, but I don't really know if that counts.}
I'm a little nervous, especially since I'm only like 60\% sure what I want to play.
But, hopefully I get home early enough tonight to relay my time.
\end{document}