\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{open-mic-7.html}{Open Mic}}
First Published: 2023 August 2

\section{Draft 1}
Assuming \href{open-mic-6.html}{my last post about open mics} was the last time I went to one,\footnote{which I think it was} I haven't been in about two months.
I'm glad that it's been long enough that the staple songs I mentioned no longer feel stale.
In particular, Maid on the Shore was everyone I polled's favorite song.

I had planned on it being like most open mics I've gone to at the bar, where I have ten minutes, though finishing early is encouraged.
Instead, I had fifteen and a generous fifteen at that.
It was fun!

I played two original songs.\footnote{one new and one old}
I then played Three Fishers, because I love the picking pattern.
After that, I made a joke about having time and played The Rose.

By that point I really thought I should be done.
I wasn't which meant I had to start thinking of songs I just know on a deep level.
Maid on the Shore is one of those, so I played it.\footnote{and wow it went so well.
I don't think it's ever sounded that good to me before from on stage.}

Even still I had time!
So I finished with 45 Years, which was a little low for me where I set my capo.
C'est la vie, live and learn.

I'm very excited to go back next week.
I had initially planned to play accordion, but my accordion is out of tune sadly.
So, assuming I don't figure out how to fix it yesterday, it looks like another week of guitar.
I suppose I should start thinking of a setlist.

Maid on the Shore deserves an encore, I think at least.
I've only ever done Treaty\footnote{by Leonard Cohen} on accordion, but I think it could work on guitar.
If not, You Want it Darker maybe?
What did the Deep Sea Say is a song my band did, so that could be fun.
I Will Follow You Into the Dark is another option, though I'd need to be better at the chords for it.
Til Forever Falls Apart also maybe belongs.

My two originals should probably get some more love/playtime too.

\begin{itemize}
\item I did minimal work on presentations, though I did finish one that's due Friday.
\item I made progress against entropy! It is nice being able to see more of my floor.
\item I blogged yesterday and today! wow a streak
\item I finished the chapter of Jeb! I'm also starting another. Total this week: 1.4/4+?
\item I wrote a poem yesterday and am going to write another after this post.
\item I wrote and posted a letter!
\item I did not work on my song, though I meant to.
\item I stretched this morning!
\item I am out too late again, though it was a friend's birthday, so I feel less than bad about it.
\item I did a rosary in the chapel this morning! It was hard to stay focused, but easier than historically, which is nice.
\end{itemize}
457/33

\end{document}