\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{open-mic-planning.html}{Open Mic Planning}}
First Published: 2023 August 4

\section{Draft 1}
Apologies in advance, this is me using the need to blog as an excuse to plan my next open mic.

As I mentioned, I need to come up with a setlist for \href{open-mic-7}{an open mic}.
I want to start learning more music as well, so hopefully I can.

Right now, I'm thinking the following songs:

\begin{itemize}
\item Jonathan Original One\footnote{which I need to name at some point? Probably starfall since that's what I used to call it.}
\item Jonathan Original Three\footnote{idk cats chase bears?}
\item Ring of Fire\footnote{because I've really liked it for a while and it's so easy to play}
\item St. Olav's Gate\footnote{because I fell in love with it this summer and memorized it (also fairly easy) (also has the benefit of being unique}
\item Fisherman's Wharf\footnote{which I've been working on for like a year, so I just need to get over myself on}
\item I will follow you into the dark\footnote{which I've only ever performed on accordion, so that will be interesting.}
\item Maid on the Shore
\end{itemize}

Now, that may be far more or less music than I need.
I think that starting with Maid on the Shore makes the most sense, if only because I know that song like the back of my own hand.\footnote{obligatory: \say{huh I never noticed that spot}}
From there, St. Olav's Gate has a similar love lost, though far more consensually.
The love segues into Ring of Fire nicely.
From there, doing my first original could be fun, since it's about heartbreak.
My third original could follow that, because that's the opposite order as last week.
Assuming I still have time, I will follow you into the dark is better right now than Fisherman's Wharf, so I'll save Fishers for last.

If I still have too much time, Three Fishers is great\footnote{for all that I don't really want to do three Stan Rogers songs in one night (though the internet only seems to believe in the Garnet Rogers version of Three Fishers}
If that still isn't enough music, I guess 45 Years is always a staple, or I could try Til Forever Falls Apart, depending if the friends I hope to show up do show up.\footnote{one of my bandmates who normally takes lead vocals on the song}

\begin{itemize}
\item I made a lot of figures!\footnote{my group doesn't like them but meh}
\item I made far less progress on entropy. I'm run down after this week. I still cleaned a little, just only slightly more than the mess I made.
\item Blogging streak continued.
\item I did not write today\footnote{see \say{I'm run down...}} 2/4+
\item I wrote a sonnet last night. I'm beat, so I'll skip it tonight\footnote{I just did a crossword, which I am counting}
\item I wrote my first journal entry in the morning. It was weird.
\item Shoot! I really need to transcribe the song that I sang to myself.
\item I stretched less than before, though it was still nice.
\item I am now I think five for five not being in bed early enough this week.
Hopefully that trend starts to break.
\item I did not do a rosary this morning because I knew that I would be doing one during an adoration hour tonight. That was a mistake, the morning rosary really helps me center my day.
\end{itemize}

386/158	

\end{document}