\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{pathfinder-0.html}{Pathfinder Session 0}}
First Published: 2022 March 15

\section{Draft 1}
Tonight I got to do session 0 for a Pathfinder 2e campaign.
I'm going to play a Gnomish Wizard, and more than that we're still settling.
I had my normal issue while building the character, which is that I saw the option to know a lot of languages and had to resist the build where I would have 13 languages at first level.\footnote{Gnome (3 languages) 20 intelligence (4 languages) multilingual from translator (2 languages), Gnome Polyglot (3, +1 for multilingual)}
Instead, I only know nine, which feels really sad.
I did, however, take the ability to speak with any burrowing creature, which is kind of fun.

Honestly, building a character in Pathfinder 2e is a much different experience than in DnD 5e.
There are way more options which is great, because I can build exactly what I want, but horrible because I don't know what I want.
I get I think an average of more than a feat per level, which is pretty cool because it means that every Wizard can look different\footnote{even if they won't.}.
I need to come up with a backstory for my Gnome\footnote{and a name I guess}, which might be the topic of a future post.
\end{document}