\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{pathfinder-0-1.html}{Pathfinder Character Backstory}}
First Published: 2022 March 16

\section{Draft 1}
I wrote a basic background history for my character, which is below.

Salvia Gnomeson is a gnome.
Gnomes don't believe in last names, so whenever you need one they just all go by Gnomeson because they're children of gnomes.
She grew up in an expatriated community in a poorer part of the capital.
Spent most of her childhood translating the traditional woven stories of Gnomish into Common and Draconic and legal documents from Draconic into Gnomish.

She was always touched by the wild, but never was able to fully turn it into a true sorcerous or druidic talent.
Instead, was always studious, so went to Wizard school.

While in school, refused to specialize, since her goal was moreso converting spells into woven expressions in Gnomish than actually learning magic.
Managed to learn how to save a spell as something you can cast once (scrolls), and a temporary version which lasts a day or so (vancian preparations).
Instead of remembering how to do that in particular, realized you can write directions for weaving the spells as a knot, though that takes some valuable threads to prevent fraying/because magic fiat. (costs 1 cp per level of spell).
Since 10 cantrips and 6 spells, 91 cp of fine thread left.

While researching, had a thesis idea: permanently woven spells that can be activated at will.
She was reminded of staves, so worked to make staff using Gnomish language rather than the traditional one.
Currently doesn't work great, but has a permanent cantrip and a semi-permanent lvl1 spell that can be refreshed.

\end{document}