\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{pathfinder-1.html}{Pathfinder Character Update}}
First Published: 2022 April 26

\section{Draft 1}
Well, it's been a little over a month since I last talked about my Pathfinder Character, so now seems like a great time.
Salvia has thus far gotten roped into investigating the attempted theft of wine from a party.
So far, this has involved overthrowing a minor crime lord and now venturing off into another city.

This session we leveled up, and Salvia learned two new feats.
Since she's still very passionate about the permanency of staves, she now has the Specialty Crafting: Woodworking Feat, and hopes to use that to improve her staff and make others for friends.
Additionally, though non-lethal spellcraft was of interest, the idea of learning from all sorts of scrolls was far too tempting, so she took the Scroll Trickster Dedication.
More or less, Salvia will be able to work with any sort of scroll going forward, which is very exciting.

Excitingly, today the party encountered a Cobbleswarm, and Salvia finally got to put her Burrow Elocutionist Feat to good use.
After defeating the swarm, Salvia spoke with the remaining cobblemites and convinced one of them to join her on an adventure.
Unfortunately, this meant letting Burrus\footnote{Burrus 1 technically} go, and Salvia's new familiar is Burrus\footnote{the second?} the cobblemite.

Currently Burrus is riding the Dull Gray aeon stone that Salvia looted from the crime boss they fought.
Someone cast perpetual flame on it, and it has been orbiting Salvia's head for days now.
\end{document}