\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}   
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{pilates.html}{On Pilates}}  
First Published: 2025 November 22 (forgot to post)

\section{Draft 1: 13 November 2025}

I mentioned in a few recent posts that I've been starting to do Pilates.  
It's definitely my favorite form of exercise to talk about.  
My brothers and I have on multiple occasions enjoyed joking about it.\footnote{partially the fact that the inventor was named Joseph Pilates, so Pilates is really just named after this guy Joe. Also he was German and the main instrument used in the practice is called a reformer, so I always say it's making me more Lutheran.}

I've absolutely enjoyed the few classes I've gone to, and wow have I learned that there are parts of me that do not want to move at all.  
Mostly, that's my hips and legs.  
I've always known that I was tight, but I never realized quite how tight I am.

And, of course, my shoulders continue to ache when I hold them up for long periods of time.  
That being said, each of those is absolutely improving as I continue to go to the classes.

However, there's a very fair question that could be asked: what do I like about Pilates?

I kind of joked to a friend that I like it because so much of the workout is done lying down.  
That's not entirely untrue; I do appreciate the fact that I can be horizontal and supported, because it means that I can close my eyes and make the workout more mindful.  
Also, I'm officially reaching the age in my life that it's probably best to start being concerned about my joints.  
Much as I do adore box jumps, my knees probably don't as much.  
Doing slower and more controlled motions, even though they aren't as fun, is probably better.

It is somewhat strange to see what parts of the workout is difficult for others versus myself.  
I very rarely have issues with moving smoothly or slowly, but lack the endurance to continue through entire sets.  
This is, so far as I can tell, the exact opposite of the normal experience in the classroom.

So, all this to say, I do really think that going to Pilates will be a good thing for me to continue doing.

\section{Misc}

This feels like a great place for some journaling!

I've recently started using a calligraphy pen, and wow it feathers so much, and also wow when I hold it right, everything I write looks absolutely gorgeous.  
It's a hard practice to make sure that I am holding it correctly, though.  
For whatever reason, a part of me is unconsciously shifting my grip to keep the stroke width identical through the entire character or word.

Also, the pen is definitely designed for cursive.

1 mm is incredibly broad for what I tend to write, but that might help with the whole \say{I am gradually getting too much ink} thing that I complain about below.  
Also, doing a page a day of writing will probably serve me best there.\footnote{I know that I calculated much more than that, but it's about starting the trend, not getting all the way there at once!}

Current Pen List\footnote{for my own posterity, mostly}

\begin{itemize}  
\item Hongdian Black with Fude Nib: Empty  
\item Jinhao Shark: Diplomat Sepia Black. 10/6  
\item Pilot Preppy: Diamine Bilberry. 10/6  
\item Shaeffer (blue): Empty  
\item Diplomat: Diplomat Caramel. 10/6  
\item Kaweko: Stipela Sepia. 10/6  
\item Monteverde: Diplomat Burgundy. 10/6  
\item Shaeffer Calligraphy: Whatever ink they sent: 11/10ish

So far really liking the pen, even though it practically gushes ink.  
Should refill the other pens that are starting to get empty sooner than later. I forget what all is empty, honestly, but I want to get through them all sooner than later.  
Given that I'm getting 25 mL in a month, I would like to start shooting for more than that amount out.  
\href{https://www.reddit.com/r/fountainpens/comments/y7nthz/any\_guesses\_how\_much\_ink\_it\_took\_to\_write\_out/}{A quick Reddit search} implies between 12 pages per mL and 3 pages per mL.  
That means between 75 and 300 pages a month, which is between 3 and 10 pages a day...

That's not not doable.

\end{itemize}

\end{document}