\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{pinball.html}{Pinball Part One}}
First Published: 2023 August 22


\section{Draft 1}
Last Wednesday I competed in my first ever pinball tournament.
I had no clue what it would be like going into it, which may not have been my best choice ever.
Nonetheless, I knew a few important facts.
?
\begin{itemize}
\item Signups were at six pm
\item Play started at half six\footnote{I'm never giving up this construction, even though it makes me sound so much like the person who studied abroad in London (which, to be fair, I am}
\item It was sponsored by a local craft brewery
\item There was a group play and a finals portion of the night?
\end{itemize}
As I told my friends going into it, my only real goal in the competition was making it past group play.
As it turns out, that was a needlessly pessimistic goal.
Everyone makes it into the finals, though not in the same bracket.
?
I suppose I should explain the format of the competition.
After signups, everyone is\footnote{allegedly, though I think they intentionally try to get a diversity of levels} randomly assigned to a group of four.\footnote{or three, I think there were a couple of those because there weren't enough people competing that night.}
Each group plays seven of the eight machines at the bar\footnote{going left to right, so you don't play the machine to your left when you begin}, and they record their scores at the end of each three ball set.\footnote{the number of people I know who didn't know that pinball is played with three balls astounds me}
They had a few extra rules, like that you weren't allowed to play extra balls, which makes complete sense to me in retrospect.
While it would not have made a huge difference for me, there were people whose every ball lasted at least five minutes.
?
In my group of four, there was me,\footnote{obviously} the person who ended up winning the entire competition that night, the girlfriend of the brewery's rep\footnote{one of the people who didn't know about the number of balls you get}, and a fourth person about as good as I was.
Once group play ended, we all turned our slips of paper in to someone, who then ranked us best to worst.
One rankings were done, I found out how finals work.
When I had signed up, the organizer told me that they make sure it's not just the absolute best players who get a prize, because that would discourage less good players from attending.
?
So, we are all ranked from best to worst.
The best four players go to a machine and play single elimination games until there is one person left.\footnote{so at the end of everyone's three balls, last place is eliminated}
Now, you may be wondering how they pick which machine they go on.
The top seed in each set gets to choose their machine.\footnote{though the top seeds aren't allowed on the Godzilla machine, because it takes far longer than the other machines, especially at high level of play (for instance, the person in my group had two different multiballs active at once.}
I was the top seed of the fourth bracket\footnote{thirteenth place}, which was where they started putting us in groups of three.\footnote{because we did not have a modulo four number of players, I assume}
I chose Godzilla, because it was the most fun machine.
At that point, I was incredibly nervous.
One of the other people on my machine was the fourth player in my qualifier, who was notably better than me at the Godzilla machine.
?But, I managed to squeak out a win twice, and that meant that I got a prize.?I ended up taking home a four pack of craft beer.\footnote{I think I chose a sour initially, but then traded away a few individuals to other people who took a four pack so we could try multiple flavors or something.}?I also took home a tshirt and some stickers, which was nice.
I also learned while there that the brewery buys your first\footnote{read: my only, since it was a Wednesday} beer of the night.
?It was really fun, for all that it lasted much longer than I expected it to.
I had really thought that the entire event would be over in two or three hours.?Instead, it took four, and that was apparently a quick tournament as far as their timings go.?I'll probably do it again, though I'll make sure to eat dinner first and know that I'll be late rising the next day.
?
\begin{itemize}
\item I need to start working on the eclipse talk again. I have some notes from friends who have made them in the past, which should be helpful in making the presentation, as soon as I start to look at them. Truthfully, I'm not entirely sure what the layout of my talk is going to be. Right now, I'm leaning towards building the solar system up from the sun, then the sun and earth, then adding the moon, then adding locks, etc.
I don't know if that's the best idea, but it's resonated with me for a week, which is generally a good sign. I should really blog about it sometime.
\item I think I made a slight bit of progress against entropy last night, though that was as minimal as it could get. Hopefully I have a little more energy tonight.
\item Blogged yesterday! And today! Wow look at me the best
\item I'm writing this post first thing in the morning, so no new book content. 1/4+
\item I wrote some iambic pentameter last night\footnote{eight non rhyming lines, I think} and a little more today\footnote{four rhyming lines}. Maybe that's a better thing for me to do right now than a whole sonnet.
I know that's an excuse, but any poetry is probably better than no poetry, and I'm mentally exhausted lately.
\item I did not journal today, though I meant to. I got a letter from a friend yesterday and a package from a different friend a few days ago. Both of those probably deserve and need responses.
\item I stretched last night and this morning, focusing on my hips and shoulders.\footnote{hips because I noticed they've been strangely tight recently and shoulders because I swam.} I also ran on a treadmill yesterday and then swam.\footnote{long course, no less}
\item I went to bed incredibly early last night, which meant I fell asleep somewhat early.
\item I should really pray rosaries more. That's something I need to get back into.
\end{itemize}
Once again, sorry for the rambling nature of the posting. That's what the site encourages.?
?
\end{document}