\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}   
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{planning-for-freetime.html}{On Planning for Freetime}}  
First Published: 
\section{Draft 1: 17 September 2025}
I've realized multiple times over the past few weeks that I want to once again be a real boy.
That is, I want to once again have hobbies, do them, and find that I am growing as a person.
What hobbies do I want to pick up, though?
That's what this space is for me to ideate over.

This site, obviously.
I have thought so much more deeply these past few days by sheer virtue of writing.
Back when the site was more daily occurrences, I did find that I was paying more attention to what happened in my day to day life.
After all, if one must figure out something to blog about, then the small can become large.
I don't know if I will be able to keep up these deep and many drafted follies forever, and likely will not.

So, then, what does an idealized version of this site look like?

I think that one image I have is some incredibly long follies, which have drafts over days and months as I slowly explore my thoughts on an issue.
Despite the fact that I have always claimed the right to go back and modify posts, I don't find that I do that.
Mostly, I think that I don't because if I am going to iterate over some thoughts, I want that to happen on a new document.
Rarely do I have an old folly in mind and go \say{huh, my views have developed in a cogent way}.

That being said, I do also think that I would have more to say to myself if i read through my old posts more.
A fun idea could be reading the posts for a given day every day.
I might actually try that starting today.
I can add it into the daily reflection as just a cute little \say{anything stand out?}.\footnote{does the period belong there?}
And, I can hopefully see trends in my own life.
Do I, for instance, lose hope every year on the same day?
Maybe!

Second, I want to be able to deal with boredom.
I think that I have good ideas somewhere inside of me, but I do also think that the noise I surround myself in keeps them tamped down.
Also, I think that it's good for people generally to be bored, and there is research to support that.
Maybe I can start spending five minutes a day staring at a wall?
Is that boring?
Is trying to become bored a contradiction?

Third\footnote{I'm doing this so that when I redraft I can find ideas}, I want to be flexible.
I feel like much of why should and could go without saying, but I want to be able to move my body, and I feel better when I stretch.
At a minimum, twice daily stretching is probably a habit that would do wonders for my mind and self.

Fourth, strength.
I feel like I'm not as strong as I was once, and I would like that to change.
Also, there's something really nice about picking up a heavy thing and setting it back down.

Fifth, cardio.
I'm not in great shape right now and that's a true thing.
It would be nice to be able to keep up with friends who decide to go for a run, or at the very least to not be winded after going up flights of stairs.

I talk about the web novel a lot.
Is that sixth?
I think so.
It will be really cool to be able to say that I have written an entire web novel.
Given the length of the first two books, it is even likely that it will break 3 million words, which is wild to think about.
I enjoy much of the premise, even if upon a reread of the early chapters, I see that I've dropped a lot really quickly.\footnote{there was a whole false religion plot line that I kind of forgot about}
Sure, then, let's say the web novel gets to come back.

Writing other things?
I love poetry, and I feel like I am a better writer and speaker when I write it.
I want to do more hand written journaling, if only so that I can practice penmanship.
I want to get back into letter writing, ideally with people who will write me back.

Seventh, reading to challenge myself.
At a minimum, poetry and philosophy are two areas that feel important to me right now.
Music is absolutely one as well.

Eighth, meditation or prayer of some sort.
I don't know where my spiritual journey will take me, but I do want to continue to spend time with the Divine.
Reading theology is always a good time for me, and feels somehow different than philosophy, for reasons I can explore later.

Ninth, music.
I know this is coming at the end, but it is really incredibly important to me.
Music has slowly fallen out of my life to the point that I don't even really listen to music any more.
I remember listening to music in Seattle, but that may well be the last time that I did.\footnote{ope, no I listened to a tiny bit while driving with my younger}

So, nine things I want to do.

I think that I also want to get into concert going.
I love music, and would like to consume more of it live as well.

I want to get into some fiber art.
Whether that's knitting, crochet, embroidery, cross stitch, etc. I feel like each has a place in my life, even if not all at once.

Also in music, I want to get back into guitar and accordion.
Also back into performing.

Oof that is many things.
Let's write them all up in a list and see if we cannot defend them with a paragraph.
Since it's to my future self, I think that it could be good to have task, expected gain, expected loss, reason.
Will that work? Maybe.
Also past relationship maybe?

\subsection{Writing Low-key Follies}
\begin{itemize}
    \item Expected gain: better understanding of myself and deeper contemplation of the world around me.
    \item Expected loss: time. Oof writing can take as much time as I let it.
    \item Reason: I like the person I become when I write these follies, I like the social aspect of chatting with my friends about my posts.
    \item Past relationship: see this site.
    \item Ideal frequency: Daily?
\end{itemize}

\subsection{Writing In-Depth Follies}
\begin{itemize}
    \item Expected gain: deeper understanding of topics.
    \item Expected loss: so much time.
    \item Reason: I like having these longer form things, and this site hosting long-form essays feels fun.
    \item Past relationship: sporadic
    \item Ideal frequency: As relevant, maybe at least quarterly? Monthly?
\end{itemize}

\subsection{Reading Old Follies}
\begin{itemize}
    \item Expected gain: Maybe redraft, mostly learn about who I once was.
    \item Expected loss: Some time, also some emotional weight, I'm sure.
    \item Reason: I think that it's going to be interesting to remember my own life.
    \item Past relationship: N/A really.
    \item Ideal frequency: Daily!

\end{itemize}

\subsection{Being Bored}
\begin{itemize}
    \item Expected gain: longer attention span, separation from phone, betterment of personality.
    \item Expected loss: relationship to memes, some time.
    \item Reason: being bored is not a part of myself. I Have to believe that spending more time without stimulus will make me better able to do creation.
    \item Past relationship: eh, intermittent at best.
    \item Ideal frequency: Daily? At least at first it feels smart to spend time being bored. Five minutes to start? Is this different than meditation? Maybe. 

    Does day dreaming fit in here? Honestly kind of.
\end{itemize}

\subsection{Stretching}
\begin{itemize}
    \item Expected gain: flexibility, joint motion, feel better about myself.
    \item Expected loss: time, pride when I do it in front of others.
    \item Reason: I am not flexible. I don't like that it's a struggle to touch my toes and I don't like how much it hurts to stretch my shoulders.
    \item Past relationship: Eh, varied through the ages.
    \item Ideal frequency: More than bi-daily.

\end{itemize}

\subsection{Lifting}
\begin{itemize}
    \item Expected gain: Strong, look better in mirror\footnote{it's a real goal, even if it shouldn't be}, friendship?
    \item Expected loss: Time, feeling sore, money for gym membership.
    \item Reason: The periods of my life I lift feel like they correlate well to the periods of my life I'm happy.
    I like being happy.
    Also, being strong is really nice, and it feels great to pick up something incredibly heavy.
    \item Past relationship: prior to graduate studies, entirely assigned. In graduate school, I tried some different routines.
    I think that ideally I would get a lifting plan from someone.
    \item Ideal frequency: Few times a week? I think so?
\end{itemize}

\subsection{Cardio}
\begin{itemize}
    \item Expected gain: Better physical and mental health, weight loss\footnote{again, goals don't have to be healthy}
    \item Expected loss: Time, happiness while doing.
    \item Reason: It's embarrasing that I can't swim a 500 or run a mile. Also there's all the research showing better outcomes for better cardio.
    \item Past relationship: Swimming and running. I like swimming, but it's such a pain. Running is easy but terrible. I've also started doing some cardio with the Meta Quest I have, and that's also an option, even if it's objectively less effective.
    \item Ideal frequency: Daily? At least as often as lifting.

\end{itemize}

\subsection{Writing the Web Novel}
\begin{itemize}
    \item Expected gain: kind comments from fans, pride in writing, maybe money someday.
    \item Expected loss: time, emotion connected with my mother, mean comments, mental effort.
    \item Reason: I started it, so want to finish. Also like I want to write other things but don't want to have a dropped story there.
    \item Past relationship: Between daily and weekly.
    \item Ideal frequency: I think that ideally I'd get to a three times a week schedule. Maybe two times a week.
    However, I'd like to be writing more than that so that when I have bad days or weeks or just don't feel like writing I have that option.
    Also, it'd be nice to be able to revise older unpublished chapters to set up things coming up later.
\end{itemize}

\subsection{Writing Poetry}
\begin{itemize}
    \item Expected gain: Better use of words, better songwriting, enjoyment
    \item Expected loss: time, feeling like a hack
    \item Reason: I generally think that it's nice to be able to write poetry.
    It was fun being able to write a sonnet at the speed of handwriting, even if the metaphor and imagery was stilted at best.
    \item Past relationship: I used to do a daily sonnet.
    \item Ideal frequency: Daily sonnet, weekly villannelle?
\end{itemize}
\subsection{Hand Written Journal}
\begin{itemize}
    \item Expected gain: bette  r penmanship, enjoyment of seeing ink on page, centering.
    \item Expected loss: time, cost of ink.
    \item Reason: I feel like I think differently when writing by hand and machine.
    Writing by hand also means that I have time away from screens.
    \item Past relationship: Nominally daily lately.
    \item Ideal frequency: Daily, in the morning, probably
\end{itemize}
\subsection{Letter Writing}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency

\end{itemize}
\subsection{Reading to Learn}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency

\end{itemize}

\subsection{Meditation/Prayer}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency
\end{itemize}

\subsection{Reading Poetry}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency

\end{itemize}

\subsection{Reading Theology}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency

\end{itemize}

\subsection{Practicing Guitar}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency

\end{itemize}

\subsection{Practicing Accordion}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency

\end{itemize}

\subsection{Writing Music}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency

\end{itemize}

\subsection{Recording Music}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency

\end{itemize}
\subsection{Performing Music}
\begin{itemize}
    \item Expected gain
    \item Expected loss
    \item Reason
    \item Past relationship
    \item Ideal frequency

\end{itemize}
\section{Daily Reflection: 16 September 2025}

\begin{itemize}

\item Did you journal by hand today?

\item Did you do a folly?

\item Did you in some way, shape, or form advance the web novel?

\item Did you work on music, whether education or creation?

\item Did you work on book binding?

\item Did you work on another hobby?

\item Did you stretch? Really?

\item Prayer?

\item Meditation?

\item Reading?

\item Minimizing screen time?

\end{itemize}

Current Pen List\footnote{for my own posterity, mostly}

\begin{itemize}  
\item Hongdian Black with Fude Nib: Diplomat Caribbean (8/30ish)  
\item Jinhao Shark: Diplomat Caribbean (8/30ish)  
\item Pilot Preppy: Private Reserve Electric DC Blue I think (I think since late june. I think)  
\item Sheaffer: Private Reserve Spearmint (since 7/15) (I Think)
\end{itemize}

\end{document}