\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}   
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{planning.html}{IDK planning life again?}}  
First Published: 
\section{Draft 1: 17 September 2025}
I've realized multiple times over the past few weeks that I want to once again be a real boy.
That is, I want to once again have hobbies, do them, and find that I am growing as a person.
What hobbies do I want to pick up, though?
That's what this space is for me to ideate over.

This site, obviously.
I have thought so much more deeply these past few days by sheer virtue of writing.
Back when the site was more daily occurrences, I did find that I was paying more attention to what happened in my day to day life.
After all, if one must figure out something to blog about, then the small can become large.
I don't know if I will be able to keep up these deep and many drafted follies forever, and likely will not.

So, then, what does an idealized version of this site look like?

I think that one image I have is some incredibly long follies, which have drafts over days and months as I slowly explore my thoughts on an issue.
Despite the fact that I have always claimed the right to go back and modify posts, I don't find that I do that.
Mostly, I think that I don't because if I am going to iterate over some thoughts, I want that to happen on a new document.
Rarely do I have an old folly in mind and go \say{huh, my views have developed in a cogent way}.

That being said, I do also think that I would have more to say to myself if i read through my old posts more.
A fun idea could be reading the posts for a given day every day.
I might actually try that starting today.
I can add it into the daily reflection as just a cute little \say{anything stand out?}.\footnote{does the period belong there?}
And, I can hopefully see trends in my own life.
Do I, for instance, lose hope every year on the same day?
Maybe!



\section{Daily Reflection: 16 September 2025}

\begin{itemize}

\item Did you journal by hand today?

\item Did you do a folly?

\item Did you in some way, shape, or form advance the web novel?

\item Did you work on music, whether education or creation?

\item Did you work on book binding?

\item Did you work on another hobby?

\item Did you stretch? Really?

\item Prayer?

\item Meditation?

\item Reading?

\item Minimizing screen time?

\end{itemize}

Current Pen List\footnote{for my own posterity, mostly}

\begin{itemize}  
\item Hongdian Black with Fude Nib: Diplomat Caribbean (8/30ish)  
\item Jinhao Shark: Diplomat Caribbean (8/30ish)  
\item Pilot Preppy: Private Reserve Electric DC Blue I think (I think since late june. I think)  
\item Sheaffer: Private Reserve Spearmint (since 7/15) (I Think)
\end{itemize}

\end{document}