\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{planning-to-fail.html}{Planning to Fail}}
First Published: 2022 February 2

\section{Draft 1}
I woke up this morning and thought to myself \say{Hey, Wednesday nights are always really late for you, and also in general you want to use nights to wind down, rather than write an essay.
Maybe, just maybe, you should blog earlier in the day}\footnote{for those not in the know, I generally write my posts near the end of my waking hours}.
So, I planned to at some point before tonight write my post.

But, when I got to work in the morning I had two two-sigma problems all morning.\footnote{two-sigma here meaning rare but not horribly so, something that screws up the routine but doesn't upend it}
Lunch, as it always does, took longer than expected, and then my early evening activities all had one to two sigma issues themselves.\footnote{one sigma issues are completely foreseeable, just things I did not think about. Example: I lose track of time when working with electronics, so I should have known that I would be working there until later than planned}
And so I had to rush to my final appointment of the night, which unfortunately lasts from 1845 until\footnote{tonight at least, which is not horribly strange} 2230 or so.
Adding in the next 15 minutes to walk home, and I suddenly went from planning to write a post early to writing a post nearly an hour past when I've set as my \say{no more notifications because you should be asleep right now} time.

As I look back at my day, I definitely see times that I could have written my post.
This morning I was tired when I woke up, so doing it before work wasn't really an option.
But, I could have taken some time after lunch instead of whittling time away to write this post.
Or, I could have made a few minutes while monitoring the pumps, rather than just idling away my time.
Regardless, hopefully my future failures to plan don't become plans for failures themselves.
I'm not at the word goal, but this is as far as my brain will let me write.

271
82
\end{document}