\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{playing-with-garageband.html}{Playing with GarageBand}}
First Posted: 2018 October 12
\section{Draft 2}
Today, I was on a five hour train ride.
While on the ride, I was doing some homework on the iPad that Grinnell College lent me for the semester.
Then, having finished the homework, I decided to play around on the iPad.
I saw that the iPad came with GarageBand, so I thought I'd play with it.
It was fun!

I forgot how much fun it can be to make musical sounds with synthesizers.
Of course, it took around three hours to make a just under three minute long piece,\footnote{not a song, which I talk about somewhere earlier} but that's still less time than composing, recording, and then post processing.
It wasn't great, but people who've listened to it have responded more positively than neutrally.
If you'd like to hear it, feel free to email me at \href{mailto:flyingrebelpipes@gmail.com}{flyingrebelpipes@gmail.com}.
\section{Draft 1}
Today, I was on a fiveish hour train ride.\footnote{as I've mentioned multiple other times, I'm apparently not supposed to say where in case terrorists are targeting me (because apparently the many devices I carry with automatic location setting don't exist) so I won't share my location.}
While on the ride, I was doing some homework on the iPad that Grinnell College lent me for the semester.\footnote{I love my class}
Then, having finished the homework, I decided to play around with an app on the iPad.
I saw that the iPad came with GarageBand, so I thought I'd play around with it.
It was fun!

I forgot how much fun it can be to play around with synthesizers.
Of course, it took around three hours to make a just under three minute long piece,\footnote{not a song, which I talk about somewhere earlier} but that's still less time than composing, recording, and then post processing.
It wasn't great, but people who've listened to it have responded more positively than neutrally.
If you'd like to hear it, feel free to email me at \href{mailto:flyingrebelpipes@gmail.com}{flyingrebelpipes@gmail.com}.
\end{document}