\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{poetry-forms-5.html}{Writing through Poetry Forms}}
First Published: 2022 May 4


\section{Draft 1}
I think I may have written a few poems in the intervening days, but more importantly, I was able to compose a double acrostic in my head on the walk to work today.
I'll call that good enough to move on to the next form.
According to \href{poetry-forms-1.html}{my list} of poems, the final acrostic to work through is the compound acrostic.

I've been struggling with this one primarily because I want there to be a nice symmetry between the two words, and so few words that bookend well share the same letters.
Come and go, for instance, works not at all.
Fight and flight, here and there, see and hear, and so on.
I guess I came up with one just now, though, so we'll see how it goes.

Wave and Moon\\
What starry skies in nighttime skies ne'er claiM\\
And daytime's star can never dO.\\
Vast though the ocean in its turning to and frO\\
Each day is pulled to her when she comes agaiN\\

Well, not the strongest poem ever.
I think one thing I really struggle with in the ending portion of each line is that I really like rhyme, so the ending letters mess me up.
I already have corrections actually, I'm going to make them.

Wave and Moon\\
What starry skies in nighttime never claiM\\
A force which calls, rememb'ring long agO.\\
Vast though the distance 'tween the two\\
Each day they pull to join agaiN\\

I don't know if this one is any better, but the flow is at least slightly better between lines.
\end{document}