\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{questionable-bread.html}{Questionable Bread}}
First Published: 2019 January 13
\section{Draft 1}
We're getting ready to return to Grinnell.
As a result, we decided to clear out our food.
We had around two pounds of bread, a pound of brown sugar, salt,\footnote{stolen from another room} and a packet of yeast.
So, I decided to make bread.

With the one packet of yeast added to most of the flour, I dumped in the very precise measurements of \say{some} salt and brown sugar.
That being accomplished,\footnote{sometimes Latin class pops up in the worst ways} I added water to the flour.
As I realized that there was still far too much flour, I found out we also had extra milk.
So, I added more flour, and I\footnote{I've been told I comma splice, so rather than change the problem, I just make sure to have more independent clauses} added milk to the flour, and continued to work.

I then got bored while kneading, so picked up the dough and kneaded as I walked and visited other rooms.
After letting it rise for 2.5 hours,\footnote{I was so forgetful} I rekneaded, and let rest for the entirely unreasonable length of 3 minutes.\footnote{I'm impatient}
I put it in the oven and walked away for ten minutes.

When I returned, the bread looked more like a cake.
It had risen quite nicely.
Of course, it wasn't browning, even after 30 minutes, so I bumped the temp from 350 to 400.\footnote{F because I love small changes and hate water-based systems}
It still didn't brown, but did turn a nice light brown colour.\footnote{wow that's a bad sentence. Also, a break was taken before writing this sentence because I realized I'd forgotten the bread in the oven}

Reviews from housemates were positive.
As for myself, I'd give it a solid neutral.
As my father would say, \say{c'est la vie.}\footnote{la vee}
\end{document}