\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\usepackage{nested}
\begin{document}
\doublespacing
\section{\href{reading-writing-24-01-04.html}{What I Read and Wrote}}
First Published: 2024 January 5 (because I forgot to post, not bc forgot to write.

\section{Draft 1}
It's been another week, which means that I get this week's version of what I've been reading and writing.
I've read basically nothing over the past week, which is a little sad.
It is also Christmastide still, so I guess that it doesn't surprise me that much, and it isn't really that bad of a thing.

However, I did just start reading the extended Percy Jackson Universe book about Nico and Will, so we'll see how fun that ends up being.
Once I've finished that, it will probably be more or less time for me to go back to the actual reading goals that I have.

In terms of writing, I mused about the album that I'd like to write, and I've started thinking about the album's content.
I've also managed to continue with daily musings, filled a few pages in my lab notebook with notes, and I've written two chapters of my web novel.\footnote{that is, I was well ahead by writing a chapter two days in a row, and then I haven't really written since. I was worried about boom and bust, and it seems like that was a reasonable concern.}
I think that's everything!

Oh wait! I've also been working on some of my Saturday musings.
That really is everything, which is a little bit disheartening, but I suppose doing this every week should hopefully keep me at least somewhat accountable for how much I'm reading and writing.
Time to do another draft of one of the musings, I suppose.

\begin{itemize}
\item Blog? There's this, and also the next draft on the Saturday musings that I'm going to try.
\item BiaY and CCCiaY? Nope, sadly. Maybe tomorrow, though.
\item Jeb? SHOOT. Tomorrow, I hope.
\item Album? I want to do some work on the song writing after this post, but I'm not sure whether that's going to happen after I get the musing draft.
\item Exercise? I did the bare minimum, which is what I've set as my daily goals
\item Stretch? I have stretched a little bit, which is great. I'd like to do more, but even the minute or so that I did today is enough to help at the point that I'm at.
\item Book on Craft? Ugh, I really don't want to have not read it for so long. Maybe if I'm smart and lucky I'll find time ot write it soon.
\item Library Books? I looked at them, which is more than I've done in a few days.
\item Guitar? Nope, sadly enough. I looked at it and moved it out of the way, though, which feels worse than nothing.
\item Prayed? A little better. I fond that I do a better job praying when I am failing to sleep.
\item Water? A little bit, which is nice. I should try to drink more, which I don't feel great about, because there's far more water that I should drink.
\end{itemize}

\end{document}