\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-2022.html}{Yearly Reflection}}
First Published: 2023 January 2

\section{Draft 1}
\subsection{Year Breakdown}
As with \href{restarting.html}{my} last \href{ending-18.html}{two} yearly reflections, I'm going to start with five positive things that happened to me in 2022, and five things I'm excited for in 2023.

\begin{itemize}
\item Passing my second year exam
\item Getting an accordion!
\item Restarting this blog!
\item Writing two books
\item Learning that I can run 5 miles when I need to.
\end{itemize}

Looking at the five things I was excited for in 2022, there's a lot of overlap.
As always, though, more wonderful things happened than I could have ever expected.

As I look to the coming year, I'm excited to/for:
\begin{itemize}
\item Passing my third year exam
\item Self-publishing a book
\item Taking an improv class
\item Watching my littlest brother graduate
\item Growing in my relationships
\end{itemize}
\subsection{Reflection on December}
My goals last month were:
\begin{enumerate}
\item Blog every day.
\item Stretch every day.
\item Write another 50000 word book.
\item Catch up on BiaY.
\end{enumerate}
I accomplished the final one of those only.
That's kind of sad, but I suppose natural.

Looking into 2023, I've \href{new-year-plans-23.html}{already planned out most of it.}

This month in particular, I would like to:
\begin{itemize}
\item Blog daily. I have faith in myself.
\item Listen to the BiaY and CCCiaY on average once a day each
\item Stretch daily
\item Write a poem a day
\item Write a piece of music a day
\item Write through Chapter 35 of the book I'm self publishing
\item Practice music daily
\item Say a rosary a day
\end{itemize}

\subsection{Theme}
I think my theme is going to be Schedule.
I find that my life works better the less I leave what I do to chance, and so I want to regiment out my day more.
I've tried using auto-generated lists these past few days for the things I want to do daily, and that's been really helpful.

Happy 2023! 
\end{document}