\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-september-23.html}{Monthly Reflection}}
First Written: 2023 October 1
First Published: 2023 October 31\footnote{Whoops}

\section{Draft 1}
Well, another month as flown by, carried away on the wings of time.\footnote{Someday I'll learn how to write poetry.
Until then, we all get to deal with this}
As you\footnote{hmm who is the you in this situation? Is it potentially future me?} can tell from the lack of posts lately,\footnote{this phrasing implies that I expect to have active readers, which I don't think I do} there are many updates since the last time I talked.

In short, I:
\begin{itemize}
\item Bound a book with friends!\footnote{which should go in \href{twenty-five}{my yearly goal post}}
\item Made cookies in lab\footnote{well, office, but close enough}
\item Did not win a pinball tournament
\item Learned blender\footnote{for a very, very generous definition of learn}
\item Did a graduate recruiting event/weekend
\item Went to a workshop on how to effectively give and receive feedback\footnote{I think? The point of the session was a little muddy to me}
\item Had a poker night with friends.
\item Saw the relic of St. Jude.
\end{itemize}

Let's see once again how that compares to the list that I tried to make about things I was excited for this month.\footnote{I wrote everything before this on the first, and nothing has really happened since then, so that still works, I guess.}
\begin{itemize}
\item Running more than five miles again!\footnote{I did it on the first! I think I pr'd}
\item Swimming with friends!\footnote{did that this morning/early afternoon. (it was a long swim time}
\item Giving my final talk in the parks for the season\footnote{I am ninety percent sure I've used the program name in this blog before, but if I haven't, this will not be the first time. I did it, in fact, last night! It went really well. Without (many) spoilers, there were like seventy people again!}
Coincidentally, this is also the final of the talk series for any speaker.
\item Recording a song!
\item Being ready for my upcoming talks
\item Maybe\footnote{depending on Bureaucracy} give or at least hash out details for me to give my first invited talk at a college I do not attend.
\end{itemize}

Oof ok.
So, I did do the first three of those, but I had already done them by the last reflection.
I did not record a song, which is a bit of a shame.
As you might guess from the lack of postings lately, last month was not a good month for me in many regards.\footnote{it's much better now, though}

I'm mostly ready for my upcoming talks, though that's a brand new development.
Yesterday I gave a practice version of the talks to my groupmates, who resoundingly hated the talk.
In their defense, I agree with absolutely all of their comments.
They mostly boiled down to the fact that a public presentation should be a story that's somewhat educational.
Instead, all that I had was a list of facts.

As a result, I more or less restarted, this time much more focused on collecting pretty images than anything like having a coherent set of facts.
After all, it's far easier to make a coherent set of facts when you have a story than it is to make a story from a set of facts.
I don't think that I have quite enough content yet, though, so I'll need to think about other ways that I can pad the content.
One option is obviously just to add in some more specific facts about what the different kinds of months are?\footnote{idk, I'm really lost and not feeling particularly inspired by anything right now}

I started hashing out the planning for the talk I'm giving at a real school.
It's for sure happening, which is really nice.
I even have a date\footnote{i think} nailed down, which is great.
Other than that, I vaguely know what I'm going to talk about.

So, what am I excited for this month?
\begin{itemize}
\item I have a friend staying with me! That's always exciting
\item I'm giving two real talks this week!\footnote{real in the sense of a talk that was explicitly asked for and that I have legitimate plans for}
\item There's a cool dinner tomorrow I get to go to
\item I'm going to a school to talk to the kids about careers in STEM!\footnote{I should probably prepare something for that}
\item I'm going to a science fair next week!\footnote{kind of? it's a like \say{this is what science research is like for graduate students} event at a local high school}
\end{itemize}

All in all, it's looking like it'll be a pretty calm month, which will be nice, especially with how hectic my summer was.\footnote{it says something that giving two talks and two school visits is a boring month to me}
I'm sure that I did a bad job with my goals last month, but let's see just how bad.

\begin{itemize}
\item Finish/make my talk on the eclipses. Hey nice! I did it.
\item Make my home clean again. Also did this.
Well, at least I made half of my home really clean.
It's the half that anyone has a reason to see, which is good enough.
\item Blog more!
Objectively, I failed at this goal.
\item Stretch and exercise more.
Technically I did this! I made it to the gym a couple of times with a friend.
\item As before, sleep enough, and try to prioritize sleeping earlier.
I think I did this.
It was hard, especially since I felt like I needed tons more sleep than I should.
\item As always, be more intentional about prayer.
That was a mixed goal.
I started to pray a rosary every night, which is nice.
I'm not always praying it well, but that's progress at least.
\item Actually get ahead on my book.
Oof.
Ok so I did plot out to the end of this arc, but I'm writing so far off of that plan.
I've been basically writing each chapter as I need it.
\item Write more poetry.
I did not write any poetry.
\item Write or record a song.
I don't think that I did this.
\item Write five things I like about myself every day\footnote{starting now}, three things I'm excited for, and ten things I'm grateful for.
Well, I gave up on this quickly, but was then told it's ok that i did.
\end{itemize}

Goals for this month:
\begin{itemize}
\item Blog more.
I feel like this is self explanatory
\item Get ahead on Jeb.
As above.
\item Keep my home clean.
I like how it looks right now and I like that I can do things in it.
\item Pray better.
I'll need to spend some time figuring out exactly what this means.
\item Stretch more.
I need to start taking care of myself.
\item Get back into writing letters to friends.
I have fallen so hard off of this, and a lot of my friends deserve responses to their letters.
\end{itemize}\end{document}