\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflections-on-readings-33-ordinary-b.html}{Reflections on Today's Gospel}}
First Published: 2018 November 18

Mark 13:31 \say{Heaven and earth will pass away, but my words will not pass away.}
\section{Draft 2}
Today's readings are fun for me because they're more mystical than normal.
But, despite the allegories and metaphors, there are some facts we can pull out.
First, eventually mankind will reach its end.
Second, we don't know when it will be.
Third, the Lord will protect his people when the world does end.
Fourth, the Lord will endure, as will his works.

Personally, I appreciate the reminder that time is limited.
Regardless of when the deadline is, it still exists.
And, as often happens when I realize the existence of deadlines, it makes me more aware of the people in my life.
So, today is a great day to remind those you love that you do, those you trust that you have faith in them, and those you hated that you forgive them.
The Year of Grace is almost over, and so we should think about where we've come in the past year.

\section{Draft 1}
Today's readings tell us two important things.
First, eventually mankind will reach its end.
Second, we don't know when it will be.
I guess also third, the Lord will take care of us, and fourth, he'll still be here.

It's a nice reminder that, try as we may to prevent it, we can't control the future.
Every single one of us has free will, and the ability to make each day the best or worst that it could be.
But, everyone else also gets to make that choice.
\end{document}