\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflections-on-readings-christ-king-b.html}{Reflections on Today's Gospel}}
First Published: 2018 November 25

Revelations 1:8 \say{\nsay{I am the Alpha and the Omega,} says the Lord God, \nsay{the one who is and who was and who is to come, the almighty.}}
\section{Draft 2}
Today is the last Sunday in the\footnote{liturgical} year, the Feast of Christ the King.\footnote{of the Universe?}
It's a great way to end the year, especially because we get a line from my\footnote{tied for} favorite book, Revelations.

We also get to use today as a way to reflect on the year we've had, and whether we've lived this Year of Grace\footnote{wow it would be embarrassing if I got the wrong year here} as if Christ was \say{King of the Universe.}\footnote{that's also the title that always feels the most awkward for me to say, because it feels anachronistic (it took me way too long to remember that word) to me}

Since I'm preparing for the end of my semester and time abroad, the ending of the year is the first of a lot of endings I'm going to have to be ready for.
But, that's neither here nor there.
\section{Draft 1}
Today is the last Sunday in the\footnote{liturgical} year.
It's the feast of Christ the King.\footnote{of the universe?}
So, today is the day we celebrate the idea of Christ as the \say{one who is and who was and who is to come} as a part of the Trinity.

And, we get a reading out of the book of Revelations, which is always nice in a reading.
But, today, as the last day of the year, so it's time that I think about endings.
My liturgical year has almost ended, and so the Year of Grace has too.
I wonder what Pope Francis will decide next year will be.
\end{document}