\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-october-23.html}{Monthly Reflection}}
First Written: 2023 October 3

\section{Draft 1}
Shoot, somehow it's the end of October.
I really feel like I blinked and suddenly the month has completely vanished.\footnote{Of course, there are reasons for this (which I will not be discussing on this blog but it seems important for future me to remember) (also present me)}
Despite the fact that this month is gone without any blog postings, I still managed to keep up my five a days.\footnote{I'm sure I've blogged about this before, but, in short, (hmm is that too many commas in a row? probably, at least in that the essay as a whole will suffer)}\footnote{with a few exceptions that I fixed}
As a result, I can still give some highlights for the month.

This past month I:
\begin{itemize}
\item Went to a fancy PChem banquet in the department
\item Gave my last planned talks for a while!
\item Talked to children!\footnote{I keep being told there's a better way to frame this, but wow I cannot find it}
\item Met with a high school friend
\item Visited home
\item Made ravioli
\item Went to Rocky Horror Picture Show!\footnote{a live cast version, which was fun}
\item Went diving for the first time in ages!
\end{itemize}

Let's see how that lines up with my things I was excited for from last month's reflection.
\begin{itemize}
\item I have a friend staying with me! That's always exciting.\footnote{Saw this in my notes but wasn't sure if I'd already mentioned it}
\item I'm giving two real talks this week!\footnote{They were fun!}
\item There's a cool dinner tomorrow I get to go to\footnote{mentioned}
\item I'm going to a school to talk to the kids about careers in STEM!\footnote{I did not end up talking to kids much about careers, though I did enjoy talking to them}
\item I'm going to a science fair next week!\footnote{I did not do that. Oops}
\end{itemize}
Hey, that's pretty close to overlap.
As always, there are new and exciting things that I did not know I was going to do at the start of the month.
I also set my standards incredibly low, which made it easy for the lists to overlap.
Let's see how we did against last month's goals, though.
\begin{itemize}
\item Blog more.
I somehow blogged less.
\item Get ahead on Jeb.
I am planning to write another chapter of Jeb right after I write this post, which will technically be slightly ahead.
\item Keep my home clean.
My home is about as clean now as it was at the start of the month, which is nice. It fell apart in the middle, but I got it back.
\item Pray better.
I've started doing a daily rosary before bed, which is, at the very least, more prayer.
\item Stretch more.
I stretched a total of five times, compared to 6 in September. Whoops.
\item Get back into writing letters to friends.
I wrote not a single letter.
I didn't even address a letter wow.
\end{itemize}

So, as expected, I did not do a great job on my goals.
But, there's always the future to improve, and that's what my goal is now.
Next month, I'm excited for the following:
\begin{itemize}
\item Going home for Thanksgiving
\item Doing NaNoWriMo with a friend
\item I'm guest teaching a class, which is fun.\footnote{though I should really reach out to the prof and figure out what, exactly, that will entail}
\item I'm going to a cool discussion about Pascal.\footnote{I'm not entirely sure what about him, because I didn't write that down, but the bishop will be there, which is cool}
\end{itemize}

Once again, a fairly small list, though one that's spaced a little more over the month, which is probably good for me.
Goals for the upcoming month:
\begin{itemize}
\item Write 1700 words a day for my NaNo project.
I averaged more than this last year, and I think that I can do it fairly quickly, especially since I even plotted this novel.\footnote{unheard of, I know}
\item Write a chapter of Jeb every day.
So, this is such an outlandish goal, except that I don't do as many social activities anymore, and I will already be in the swing of writing for NaNoWriMo.
If I cut myself off from writing too much more than 1700 words a day for that, the extra creative juice will have to flow somewhere, and it may as well be into Jeb.
\item Blog every day.
Now, lots of people say that the correct way to build a habit is by picking a single incremental change to your life and implementing it.
They're probably right.
Nonetheless, I want to do my best here, rather than simply doing something.
I very often have monthly goals of writing more blog posts, and this month I will already have the daily momentum of Jeb and NaNo to keep me blogging.
\item Stretch every day.
There is really nothing about my life that is not improved when I stretch more.
Given that I will be hunched over a computer more this upcoming month\footnote{or, as I am right now, reclined with my arms cocked weirdly}, it is almost certainly going to be necessary for me to at least stretch my neck, shoulders, and hands.
Also, there's now a club diving team at my school, so I can go diving again.
My body was not flexible enough for it last time, but that's only more reason for me to improve.
\item Improve the cleanliness of my home.
Last month I raised my standards for what my home should be like.
I would like to do that again.
\item Pray better.
I have gotten to the point that a daily rosary is what I do, but it's not always\footnote{read: often} particularly mindful.
At a minimum, it would be good for me to be better about that.
\item Write letters to friends.
At a minimum, there are three people I owe a letter to and at least one other person I would like to send a letter to.
We're almost at the time of year that holiday cards become appropriate, and I could consider doing those this year.
\end{itemize}

This means that I'll have a daily reflection that looks like:
\begin{itemize}
\item Did I write 1700 words for NaNoWriMo? /1700
\item Did I write a chapter of Jeb?
\item Did I blog?
\item Did I stretch?
\item Am I doing better at prayer than a rushed and thoughtless rosary?
\item Am I doing a good job writing letters to friends?
\end{itemize}
\end{document}