\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-june-22.html}{Monthly Reflection}}
First Published: 2022 June 30

\section{Draft 1}
So... I took a while off from blogging.
I could make a lot of excuses, like that it was the end of the semester.
If I look at my daily reflections, it somewhat supports that.

Anyways, life updates.

\begin{itemize}
\item I finished the semester
\item I presented at a conference
\item I\footnote{literally today} passed my second year exam
\item I played at an open mic with a friend
\item i think that's it
\end{itemize}

So, looking at my goals for May, and thinking about that into June:

In May:
\begin{enumerate}
\item Blog daily. I still like how it forces me to think about something every day.
\item Write a poem a day. I need to do this more and I will try.\footnote{starting tomorrow}
\item Stretch daily. I like how stretching makes me feel, and maybe I'll be able to touch my toes at the end of the month.
\item Listen to BiaY 7 times a week. This feels more aware of my tendency to listen to three or four in a row.
\item Finish a draft of the book I'm writing.\footnote{likely 100K words, 50 chapters} This may be optimistic, but in theory these past two weeks suggest I can do it.
\item Practice guitar every day. I've been getting better and I really like it.
\item In professional news: finish a reasonable draft of my exam. I need to write this, and soon
\end{enumerate}

Um
\begin{enumerate}
\item Did not do, gave up one week in.
\item ...I completely even forgot that was a goal
\item I stretched most days, though I've recently gotten back out of the habit
\item I think I listened 7 times since then
\item I apparently kept writing off and on until the 23 of May, getting up to 74382 words, which is still progress
\item I practiced most days
\item I just presented my exam, so I guess that counts as reasonable 
\end{enumerate}

Now that I don't have that existential dread over my head,\footnote{I'm ignoring the next exam that I need to start soon} I think I'd like to get back into writing.
July is apparently Camp NaNoWriMo, so I would really like to try writing here and a short story every day.
I've already written a few\footnote{if you'd like to get the link, just ask} of them and I really enjoy the fact that it's done when I finish writing.
I'd like to get back to the LitRPG I was writing, but it's beginning to feel like an albatross.
That transitions nicely into my goals for July:

\begin{enumerate}
\item Blog daily. I kind of completely have no idea what happened in May or June because I have minimal records from them. I don't like that
\item Stretch daily. I liked how I was starting to get more flexible
\item Be able to run a 5k. I tried one at reunion, and did not do well
\item Listen to BiaY more. I would like to finish at some point, but it's hard to motivate
\item Practice guitar every day. I still like the incremental improvements, and I think I'd like to start shifting more up the fretboard
\item Practice accordion at least 2x a week. I just got this and I don't want it to feel neglected\footnote{I still find it weird that most people gender and name their instruments}
\item Write a short story every day. I want to force myself to do more creative writing, especially in short contexts
\item Maybe finish the book?
\item Finish either of the two songs I'm writing. I started working on a choral setting of Stabat Mater Dolorosa, and I finally put some words and a melody to a chord loop I really like. It would be nice to finish a project
\end{enumerate}

Ok so having looked at what I thought my updates were, I think there are more.
To check, I'm looking at my daily notes for the past two months in far more detail than I did to see why I stopped blogging.
Since I stopped blogging I have:\footnote{not counting the things mentioned above}\footnote{mostly chronologically}

\begin{itemize}
\item Seen a lunar eclipse.\footnote{it was cool}
\item Started jamming with a fellow chem grad student
\item I think started working out with a fellow groupmate\footnote{tbh no clue when I started}
\item Tried recording mental state of the day with my daily reflection.
\item Bought a guitar
\item Played at an open mic
\item Saw my sibling at their institution of higher learning to celebrate a major life milestone
\item Joined a new bible study
\item Made lemon wine
\item Bought new clothes
\item Went on group retreat
\item Went to a reunion and reconnected with a lot of lovely people
\begin{itemize}
\item Ran a 5k
\item Saw my family
\item Got positive reviews of the lemon wine
\end{itemize}
\item Went to a conference
\begin{itemize}
\item Met many of my collaborators
\item Made new friends
\item Tried new food
\item Gave a presentation
\end{itemize}
\end{itemize}

Wow that really looks like a lot when I write it all out.
Anyways, sorry for rambling, but also not really.
I'm excited for the next month of 31 days of writing.
\end{document}