\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-2024a.html}{Semi-Yearly Reflection}}
First Published: 2024 July 1

\section{Draft 1}
Well, it's been half of a year!
Despite the fact that I haven't really blogged at all\footnote{including after my post claiming that I would restart, whoops}, I do still want to keep making progress on all of my goals.
Since it's the first of a month, and the first of the quarter and half of the year, it seems like a good idea to potentially look through all of my goals and see where they're at.
My monthly goals\footnote{admittedly in January} were:

\begin{itemize}
\item Keep up with BiaY and CCCiaY. I gave up on BiaY, and in general have actually been pretty decent on CCCiaY.
\item Keep blogging daily. Welllll that certainly didn't happen, but I'm hopeful that I can start getting better at that.
\item Get ahead on Jeb. I just got another review requesting the ability to give me money, so this priority should really get shifted higher than it has. As of right now, I am not ahead at all, though I have some plotting done.\footnote{and I kind of want to plot out every chapter until the end of the arc}
\item Write and record at least a song. I've in total recorded about half of three songs, which does create more than a single song. I don't know that I did that in January though.
\item Exercise and stretch more. At least recently, I've been doing pretty well at stretching regularly. Obviously something that I'd like to be better at as well.
\item Finish the book on craft. Hmm I think that i have? I've at least read one book on craft since then, even if it wasn't the one referenced.
\item Read and/or return at least three of the library books I have checked out. I um don't know that I've read any. I also checked out a bunch more last week, so I should really get on this.
\item Play guitar more. I was doing pretty well on that, but then put my nicer guitar outside of my reach. I should replace the strings on the less good one, and then I can probably do that more.
\item Pray better. At least for the past month and a half, I have been doing absolutely horribly at this.
\item Drink more water. I got a larger water bottle recently, and that has absolutely helped a lot with drinking water.
\end{itemize}

Moving to the yearly goals, I am somewhat curious about whether they still feel resonant and whether I've made adequate progress on them.\footnote{Given that we're halfway through the year, being halfway to the goal seems like something reasonable}

\begin{itemize}
\item Blog Daily. As mentioned, that did not happen, though it is still somewhat resonant with me.
I aspire to doing so again starting now.
\item Finish dissertation research. I've at least made some good strides on the research, though heaven knows whether it's even close to done.
\item Make significant progress on writing my thesis. I haven't really started at all. I've brain dumped a few times, but that's not anything really.
\item Figure out what I want to do after graduate school. I think that I want to end up in the world of science outreach, though that's about as far as I've gotten.
I am meeting with two people in that space this upcoming week, though, so maybe that will help me get some better ideas.
\item Apply to whatever I want to do next.
As mentioned, I'm talking to people about what the next steps could be, so that's at least in\footnote{on? like it's in works} the books.
\item I would like to finish the book on craft that I've started and then read the ones that I was gifted this past Christmas. 
I definitely have not finished it, I realize, though I have finished one of the other books of craft.\footnote{and I think that I lost another of them, though I have no clue where it could have gone (which I suppose is evidence for its being lost)}
\item I want to read through all the books that I've checked out.
I think that I've read two or three of them, though I have nothing like returned any of them, and I've read far too few of them.
\item I would like to be better at putting myself out there. I had a very specific way of doing this in mind, and I think that I've made some progress on that front, though of course it's always an in progress thing. Still, I think that I am happy with the efforts I've done so far.
\item Write and record an album. OOOF I really need to get on this faster and more really, because we're at under 40 days to finish it.
\item Do BiaY and CCCiaY. I gave up on BiaY and I'm a few days behind on CCCiaY, but that's fair enough.
\item Be better at exercise. I don't remember where I was in January, but I feel as though I've been better this year so far at least.
\item Learn to weave. I think that this goes in the aspiration, rather than practical, goalset. It would be nice to have done, but I don't feel a drive to do this.
\item Learn to spin yarn. As above.
\item Learn a polka on the accordion. My accordion remained in the shop\footnote{technically still remains, because I do really need to drive up there sometime soon}, but I bought a new one\footnote{well a new to me one.}.
That being said, have not worked on a polka.
\item Swim a mile. I was making good progress and then kind of completely gave up on that. Will get back in the water tonight, and I'll stay until I've finished a very very broken mile.
\item Be better about exercise. This was a double goal, which is kind of funny.
\item Improve at prayer. I think that my prayer life was doing better for a while, but it's unfortunately suffered more than a little bit since then.
\end{itemize}

Well then, with all this in mind, what are my goals for the month?
\begin{itemize}
\item Finish the album. Birthday is rapidly approaching, which means the deadline is as well.
\item Swim at least 4 times weekly. If I want to get to a mile, it's going to take a lot of swimming.
\item Read/ choose not to read\footnote{meaning like decide that there's nothing in the content that I need} at least a dozen of books that I've checked out. Even if there's stuff in the books that I cannot process rapidly, I still can get at least the notes I want done.
\item Stretch twice daily. I want to get flexible, and stretching is such a low investment exercise.
\item Improve my prayer life. I think that to start that's going to mean a daily rosary, and then at the end of the month, we can see where we're at.
\item Get 5 chapters ahead on Jeb. That's about the minimum I feel comfortable charging people for, and if I don't do it now, then when?
\item Blog daily. There's no way that I'll be able to keep myself accountable on all of these points if I don't reflect at least once a day.
\end{itemize}

With this in mind, the daily reflections will be:
\begin{itemize}
\item What progress did I make on the album?
\item How many times a week have I swum? Is it greater than or equal to four?
\item How am I doing on reading through my backlog? ?/12 for the month
\item Have I stretched twice today?
\item Rosary? Other prayer?
\item How many chapters ahead on Jeb? /5
\item Blogged daily?
\end{itemize}

Given that the day isn't quite halfway done right now, I'm debating between publishing this now and then adding a new draft later, and just waiting to post it until closer to bedtime.
I'm leaning towards the latter, as it will give me more time to get items on the list finished.

Having now gotten to the end of the day:

\begin{itemize}
\item What progress did I make on the album? None, sadly enough.
\item How many times a week have I swum? Is it greater than or equal to four? I swam today, which may be the first day, but it's also first of the week.
\item How am I doing on reading through my backlog? ?/12 for the month. No progress, but I am very tired, and so am ok with that fact.
\item Have I stretched twice today? I'm about to go stretch!
\item Rosary? Other prayer? Will do rosary before bed.
\item How many chapters ahead on Jeb? /5 Ugh I feel bad that i have done nothing.
\item Blogged daily? Look at this
\end{itemize}

\end{document}