\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-september-2022.html}{Monthly Reflection}}
First Published: 2022 October 1

\section{Draft 1}
Hooray! We made it another month.

My goals were:
\begin{enumerate}
\item Blog daily
\item Stretch daily
\item Manage to run the entire doctoral dash
\item Continue keeping up with my BiaY buddy
\item Write a poem every day
\item Journal every day
\end{enumerate}

Lets see how we did:
\begin{enumerate}
\item Nope! I wrote 12 blog posts. Oof.
\item Again, I stretched maybe once.
\item \href{running-1.html}{I did it!} Woo! It was kind of fun in retrospect.
\item I'm now something like 60 days behind oof.
\item I wrote 10 sonnets, and started another song. Let's call that an even dozen.
\item I didn't journal even once. Whoops.
\end{enumerate}

Moving forward into next month:
\begin{enumerate}
\item Blog daily. Eventually this goal will happen.
\item Stretch daily. I'm going to stretch right after this, just so I make sure to do it.
\item Figure out how to repair/improve my accordion case. I made some notes today, and I think I should be able to get some of it done by the end of the month.
\item Write a poem every day. I did feel like the poems I wrote helped me ease into sleep, and they certainly help me write songs better.
\item Finish the newest song I'm working on. 
\item Make progress on catching up for BiaY.
\item Fill in at least 3 more items on my 24 for 24.
\end{enumerate}
That seems like a nice set of goals.
Let's see how it goes!
\end{document}