\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-april-22.html}{Monthly Reflection}}
First Published: 2022 April 11

\section{Draft 1}
I may be about ten days late for this, but better late than never.

As with my March reflection, I will start by reflecting on last month's goals.
My goals for the month of March were:
\begin{enumerate}
\item Blog daily. I think this is still a helpful thing for me to do
\item Write music or poetry daily. I would like to do this, even if it is hard
\item Do the pushup/squat thing and stretch daily. I liked how I felt when I did this
\item Listen to BiaY Daily. I like making progress on it.
\item Reach 50000 words in my book. I'm currently at more than 20K, so this should be very doable.
\end{enumerate}
I accomplished none of these.

I blogged for about half of March, before I gave it up.
I don't think I wrote poetry more than a few times in March.
I stopped the pushups almost immediately.
I did not listen to BiaY.
I got to approximately 40000 words, which is fun, because it means that a sustainable pace is apparently 20K words a month, though I guess it's always possible to draw a line with two data points.

My goals for April are:
\begin{enumerate}
\item Blog daily (starting now). I think that the reflection it makes me do is really useful. I do think that I need to find a better way to ensure that I have time for it, though.
\item Write a poem a day. I just bought a book of poetic forms, so it would be good to start working through them.\footnote{Look forward to postings about that.}
\item Stretch daily. I tried to stretch this morning and was shocked at how inflexible I am.
\item Listen to BiaY daily. I really don't like how far behind I am, and I'd like to catch up sooner than later.
\item Reach 60K words in the book. If past months are indicative, that's a goal I can accomplish. I think I may need to do some more planning, rather than writing by the seat of my pants, because I'm starting to get into a bit of a rut in terms of writing. Maybe it's just that I have continued this section of the book for far too long.\footnote{If I keep thinking about it here it'll become worth its own blog post, and I refuse to do that.}
\item A secondary goal for the book is to write every day, even if only a few words. I think it's good to develop good habits, though I guess I should think about balancing doing something because I enjoy it with getting work done. That's another thing to think about I suppose.
\item Practice guitar every day. I like the sound of guitar, and I would love to be able to play longer without my fingers hurting.
\end{enumerate}
I hope these are plausible goals, though only time can say for certain.
I know that I \emph{am} about to write the poem, so that's at least four things off the list today.\footnote{I listened to two BiaY this morning, and the aforementioned stretching}
Hopefully I can make it through all six tasks each day, especially since most of them are so short.
\end{document}