\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-july-2022.html}{Monthly Reflection}}
First Published: 2022 August 1

\section{Draft 1}
Welp, another month has slipped through my life.
It feels like it's only been two or so weeks, but that's all kinds of untrue.
Major life updates are really just that I've given my first public talk.

My goals were:

\begin{enumerate}
\item Blog daily
\item Stretch daily
\item Be able to run a 5k
\item Listen to BiaY more
\item Practice guitar every day
\item Practice accordion at least 2x a week
\item Write a short story every day
\item Maybe finish the book?
\item Finish either of the two songs I'm writing. I started working on a choral setting of Stabat Mater Dolorosa, and I finally put some words and a melody to a chord loop I really like. It would be nice to finish a project
\end{enumerate}

Welp, lets go through them in order:

\begin{enumerate}
\item I blogged 10 times. Welp, I could do better there.
\item I stretched less than ten times I think
\item I \href{running.html}{did it!}
\item I set up a reading plan with a friend and got through three books!
\item I think I practiced guitar most days at least, and I'm certainly getting better
\item I practiced at least 10 times which is certainly an average of 2x a week.
\item I wrote 10. Wild that I got as many of each, because I really had no idea which I did more.
\item I cut the remaining plot points that I had been planning on writing, so as a result I am now done!
\item Well... I started writing a new song, more or less restarted Stabat, and dropped the other song after working on it a bit. I did also add chords to a song that a friend was working on.
\end{enumerate}

In August I will try to:
\begin{enumerate}
\item Blog daily! As with last month, I prefer having a record of my times. I also have an idea for a chemistry book/curriculum I'd like to work on, so may post notes there.
\item Stretch daily. I really do feel better when I stretch more
\item Be able to run 5.49 miles. As I mentioned, I need to be able to, so might as well try.
\item Keep up with my reading buddy for BiaY. That feels self-explanatory to me
\item Practice guitar daily. I'm doing open mics with a friend\footnote{maybe friends!} and I'd like to not hold them back.
\item Practice accordion at least 3x a week. The above friends mentioned wanting some accordion on a song, so I'd better get better.
\item Revise the book I wrote? I don't know if this is a good goal, but I would sure like it to be. I have certainly become a better writer since I started the book and I'd sure like to demonstrate that to myself.
\item Write 20000 words of a new story? I have an idea for an urban fantasy novel. Well. I have a few things I'd like to explore at least. At worst I can probably just write the sequel to the above book.
\item Decide what I want to write my Research Proposal on. That's the next exam in my life, so I should work on that.
\end{enumerate}
\end{document}