\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-november-2022.html}{Monthly Reflection}}
First Published: 2022 December 1

\section{Draft 1}
It's the final month of 2022, which means that it's my final monthly reflection for the year.
I didn't really set any goals in my \href{restarting.html}{first post of the year}, but I did mention five things I was excited for then.
I'll reflect on those at the end of the year

My goals last month were:
\begin{enumerate}
\item Blog every day
\item Stretch every day.
\item Write a poem every day.
\item Finish NaNoWriMo successfully
\item Make progress towards catching up on BiaY
\item At least two entries in 24$^2$.
\end{enumerate}

\begin{enumerate}
\item I blogged 13 times last month, which isn't my best job ever. Hopefully this month goes better.
\item I stretched three times that I recorded, which is still progress technically.
\item I wrote a poem a day until the 22 or 23, when I abruptly stopped.
\item I \href{nanowrimo-4.html}{did it!}
\item I'm much closer now, though still not there
\item I only added one new entry.
\end{enumerate}

That's honestly slightly better than I normally do.
I realized that I was using time I would often use for blogging for NaNoWriMo, which meant I didn't want to blog as much.
This month I'd like to write at least as much, but I guess I'll have to see if I can do better about still blogging.
Stretching remains a goal of mine that feels so unapproachable for some reason.
Writing a poem a day did a lot to force me to write, though in addition to the prose I was doing, I don't know if I still need it right now.
NaNoWriMo was fun, and now my brother has pointed out how easily I could output a large sum of writing.
I'm behind on 24$^2$, which is sad, but I guess encouragement for me to start doing things faster.

My goals for this month are:
\begin{enumerate}
\item Blog every day. This month is the month, I can feel it.
\item Stretch every day. ibid.
\item Write another 50000 word book. I saw that it was very possible last month, so I'd like to show myself that it is again.
\item Catch up on BiaY. If I want to finish this year, I need to be caught up by the end of the month.
\end{enumerate}
Time to see how I do!
\end{document}