\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-august-2022.html}{Monthly Reflection}}
First Published: 2022 September 1

\section{Draft 1}
Wow, once again, I have watched as a month slipped by my life.
I finally finished the journal I started in November of 2019 which is really exciting.\footnote{Though the comments I got on my new, identical-but-for-wear journal have already started.}

My goals were:
\begin{enumerate}
\item Blog daily! As with last month, I prefer having a record of my times. I also have an idea for a chemistry book/curriculum I'd like to work on, so may post notes there.
\item Stretch daily. I really do feel better when I stretch more
\item Be able to run 5.49 miles. As I mentioned, I need to be able to, so might as well try.
\item Keep up with my reading buddy for BiaY. That feels self-explanatory to me
\item Practice guitar daily. I'm doing open mics with a friend\footnote{maybe friends!} and I'd like to not hold them back.
\item Practice accordion at least 3x a week. The above friends mentioned wanting some accordion on a song, so I'd better get better.
\item Revise the book I wrote? I don't know if this is a good goal, but I would sure like it to be. I have certainly become a better writer since I started the book and I'd sure like to demonstrate that to myself.
\item Write 20000 words of a new story? I have an idea for an urban fantasy novel. Well. I have a few things I'd like to explore at least. At worst I can probably just write the sequel to the above book.
\item Decide what I want to write my Research Proposal on. That's the next exam in my life, so I should work on that.
\end{enumerate}

Well once again, let's see how we did:
\begin{enumerate}
\item I wrote a total of 13 blog posts over I think 10 or so days. I did work on the curriculum a bit, but not as much as I would have liked to.
\item I did not do this, and I can really feel it.
\item I don't even think I ran that much total this past month.
\item I did it! We made it up to day 151 in August.\footnote{so still horribly behind but}
\item I think I practiced every other day, but managed to keep up.
\item I don't think I did, but everyone seemed ok with my performance this past Monday, so maybe I did well enough.
\item I did not revise it at all.
\item I wrote about 1700 words
\item I have not done this
\end{enumerate}

Overall, I met almost none of my goals, but I'm ok with that.
I was having a rough month in a lot of respects, so I'm mostly proud of myself for doing as well as I could.
That being said, I'm going to strive to do better this month.
So, monthly goals are:

\begin{enumerate}
\item Blog daily! The more I blog, the better I do at blogging, and I think it also helps me with writing more generally.
\item Stretch daily. My body is starting to ache fairly often, and I'd like it to not do that.
\item Manage to run the entire race tomorrow. That's not really a monthly goal so much as a goal I'd like to accomplish, but it goes here anyways.
\item Continue keeping up with my BiaY buddy.
\item Write a poem every day. I find that my ability to write songs has started to suffer, plus I really like filling my notebook more quickly.
\item Journal every day. As much as I love this blog, its inherent semi-public nature means that there are a lot of topics I won't\footnote{and shouldn't} write about in it. I still think it's good for me to discuss them, plus I need to fill this new notebook.
\end{enumerate}

I've taken the musical goals off the list because I don't really know if that's a goal I have anymore.
I certainly want to practice enough to not hold my band back, but that's not necessarily a quantity thing for me anymore.
Now it's more about learning specific songs.
\end{document}