\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-2023.html}{Yearly Reflection}}
First Published: 2024 January 1

\section{Draft 2}
Happy New Year!
It has been basically a year to the day since \href{reflection-2022.html}{my last yearly reflection.}
Last year I did five things that I was excited for and five things that I was excited to have done in the previous year.
So, five things that I am excited for in the upcoming year:

\begin{itemize}
\item Publishing my first first author paper
\item Giving an invited lecture at a university
\item I'm excited to grow in my relationships\footnote{this was something from last year, but it remains true}
\item I'm once again also excited to watch my little brother graduate
\item I'm excited to record an album
\end{itemize}
Five things not on last year's list that I'm glad I did,
\begin{itemize}
\item I got to explore my new home state and visit a lot of the state parks in it as outreach!
\item I got to give a lecture to a classroom which is only slightly different than the last item but felt significantly different.
\item I did open mics!
\item I kind of became a computational chemist
\item I got much better at writing! Both in terms of content and in terms of quality.\footnote{well, at least I think that I improved in terms of quality}
\end{itemize}

Last year I also had five items that I was excited for!
\begin{itemize}
\item Passing my third year exam. I did it!
\item Self publishing a book. I have more than a thousand followers, which is really exciting!
\item Taking an improv class. I sadly didn't get around to it.
\item Watching my littlest brother graduate. It was fantastic.
\item Growing in my relationships. I did! It was very rewarding, and I am very glad that I did it.
\end{itemize}
I had a number of goals for last year, and I generally did not do a great job with them.\footnote{feel free to read the last draft if you'd like more details}

This upcoming year, as with every year, I have any number of goals, however (un)reasonable they may be.
\begin{itemize}
\item Blog Daily\footnote{with the disclaimer that I may not post the ones I don't like}
\item Finish the research for my dissertation\footnote{I would ideally like that to happen, for all that I don't really expect it to work}
\item Make significant progress on writing my thesis
\item Figure out what I want to do after graduate school
\item Apply to whatever I want to do next
\item I would like to finish the book on craft that I've started and then read the ones that I was gifted this past Christmas
\item I want to read through the books that I've checked out
\item I would like to be better at putting myself out there
\item Write and record an album
\item Do BiaY and CCCiaY. It should be easier because I can talk to a family member about them
\item Be better at exercise
\item Learn to weave
\item Learn to spin yarn
\item Learn a polka on the accordion
\item Swim a mile
\item Be better about exercise
\item Improve at prayer.
\end{itemize}
That's far more than I think might be reasonable, and so I will hope that I can make it through everything, increasing in productivity constantly.

Let's move on to the other portion of the reflection, which is the monthly reflection.
I think that monthly goals remain useful for constructing my month in the way that I would like to live it.

Goals for the upcoming month:
\begin{itemize}
\item Finish at least three of the books that have been sitting maligned on my \say{Currently Reading} shelf. I did it! I think that I even cleared through more than three of them.
\item On a related note, read two of the books that I've checked out from the library. I don't think that I did a good job with that, but I did read like a third of one book. I then found like another five or ten that I want to read, which isn't great.
\item Following that line of thought, I want to spend my time more intentionally. I did a better job with it, even though it wasn't super intentional.
\item I want to write a sonnet every day. I wrote a lot of sonnets, and I even revised a fair few of them
\item I want to read a book on the craft of writing start to finish. I had accepted that I might not finish this book at the end of the month, which is good, because I didn't do it. Hopefully next month.
\item Get better at prayer. I really did not.
\item Clean my home. I think that I did improve the home at least a little bit.
\item Stretch and do some other form of exercise every day. Oof, I fell off this wagon.
\item Get better at touch typing. I did! My words per minute has grown much higher, and I hope that I wil continue to improve.
\item Write letters to friends. I wrote a few of them, which is nice!
\item Get ahead on Jeb. OOf, I did not get ahead of the book, which is ok.
\item Get better at embroidery. I did get better! I think that I could have done better, but it's ok.
\item Play guitar every day. I did play guitar more often! Even though I didn't get there all the way, I tried my hardest, and that counts for something.
\item I want to keep up the daily blogging. I kept up with it! Yay!
\item I want to finish a full draft of the paper I'm working on. I did not, which is sad enough.
\item I want to drink more water. I don't think that I drank very much water, sadly enough.
\end{itemize}


Anyways, goals for the upcoming month, which should hopefully reflect my goals for the upcoming year.

\begin{itemize}
\item Keep up on BiaY and CCCiaY. If I want to egt there at the end of the year, I need to start there.
\item Keep blogging daily
\item Get ahead on Jeb
\item Write and record at least a song
\item Exercise and stretch more
\item Finish the book on craft
\item Read and/or return at least three of the library books that I have checked out. Three might be far too many, but hopefully at least one of them, maybe two?
\item Play guitar more
\item Pray better
\item Drink more water
\end{itemize}
\section{Draft 1}
So, it's been a year.\footnote{since the last year, I guess. It's been more than a year since a lot of things have occurred and far less than a year since others have happened}
I'm planning to work on this in a few drafts, so let's take a page from last year's yearly reflection and do five things I was grateful for last year and five things I'm excited for this year.

Last year I thought that I would be excited for:
\begin{itemize}
\item Passing my third year exam. I did it! I'm very proud of myself, and it's wild that I'm now a dissertator
\item Self publishing a book. As of the time that I'm drafting this right now, I'm sitting at just under three hundred and fifty thousand words, I have 1351 followers, and my chapters have been read an average of over four thousand times each.\footnote{total chapter views divided by chapters} It's been a great experience, and I have definitely been forced\footnote{given the opportunity to? Kind of both} to reflect on myself based on how the writing I put out is received.
\item Taking an improv class. Sadly, this never happened. I do think that I went to an improv show last year, which was fun. Hopefully I'll find a time with my friend to go to improv class this year.
\item Watching my littlest brother graduate. He did! It was fantastic to get to watch him, and it was really great getting to spend time with family and see him in his element.
\item Growing in my relationships. Oh boy did I! I started being deliberate about writing letters to friends, and I made an effort to stay in touch with a lot of people. I think that they have by and large been successful goals, though I've also finally come to the realization that I don't have to be friends with everyone. Some people will dislike me for who I am, and that's ok.\footnote{arguably good for me, especially if they dislike the parts of me that I personally like}
\end{itemize}

All of those tasks that I did accomplish were things that I am glad I did.
Other highlights from the year,\footnote{because it feels kind of wrong to double count}

\begin{itemize}
\item I got to explore my new home state and visit a lot of the state parks in it as outreach!
\item I got to give a lecture to a classroom\footnote{slightly different, but it felt so different, because it was a completely wild experience where I just got peppered with questions about literally anything (in retrospect, introducing the idea of quantum uncertainty may have been a mistake)}
\item I did open mics!
\item I kind of became a computational chemist
\item I got much better at writing! Both in terms of content and in terms of quality.\footnote{well, at least I think that I improved in terms of quality}
\end{itemize}

That is all very exciting!
What am I looking forward to in 2024?

\begin{itemize}
\item Publishing a first author paper!\footnote{ideally, at least. I think that I'm close, and it should be very doable}
\item Growing in my relationships.\footnote{This is something I said last year, but it remains true this year}
\item Giving an invited talk at a university\footnote{I think that they call themselves a university, at least. Wow I need to start working on that talk}
\item I'm excited to watch my littlest brother graduate again!\footnote{he really is the brains of the family}
\item I'm excited to write and put out an album.\footnote{I remembered recently (read: my family reminded me) that many people expect an album to tell a story over the course of its songs. I should probably try to have mine do that, but of course, that is a goal that I am willing to give up on if it becomes untenable}
\end{itemize}

Ok cool, that also includes some of my goals for 2024.
Turns out I did set goals for 2023, I just put them in a separate document.
My goals last year were to:
\begin{itemize}
\item Blog Daily. I did better at that towards the end of the year, but I think that I averaged somewhere like one day in three overall.\footnote{not going to confirm that right now}
\item Do BiaY and CCCiaY. I completely dropped the ball on both of these. I do think that they're important, and a family member is doing them, so that should help be a motivator.
\item I wanted to be better about exercise. I think that I ebbed and flowed in that goal over the course of the year. I'm generally pretty ok with that fact, though. I have higher priorities, and I'm comfortable with that fact.
\item I wanted to write more and varied forms of poetry and prose. I think that I generally did a pretty good job of writing more, for all that I kind of dropped the ball on the poetry. I think that I did do a pretty good job with varied forms of prose.\footnote{also, 2023 lasted just forever, and I can't recall what things I did then and what things I didn't do since 2022}
\item I wanted to practice music more. Again, this is a goal that ebbed and flowed, but I would like it to flow more than ebb this coming year.
\item I wanted to try monthly, quarterly, and yearly goals.
I generally did alright\footnote{not to be confused with all right} with the monthly goals, but I gave up on quarterly goals almost instantly and never really referenced the yearly goals.
\end{itemize}

Last year I wanted to make an effort to learn species counterpoint better.
I don't think that this is a goal that I am going to take with me to 2024.
I've briefly talked about it before, but to recap: I do want to compose, but mostly for my own solo performance, rather than traditional choral composition.
I don't think that there are enough hours in the day, days in the week, or weeks in the year for me to explore everything that I want, so I need to prioritize.

What else are things that I want to work on or do this year?

I said in my 25 for 25 post that I want to learn how to weave, swim a mile, take an improv class, learn a polka on the accordion, and spin yarn.
Those all remain things that I think that I want to do.
Let's see what I think that I would need to accomplish each of the tasks:
\begin{itemize}
\item Learn to weave: sign up for a class with my friend who also wants to learn how to weave
\item Swim a mile: Start swimming regularly, focusing on just swimming
\item Take an improv class: force my schedule to overlap with the friend I want to take the course with and the course itself
\item Learn a polka on the accordion: get my accordion back and look up an easy polka for it
\item Spin Yarn: either use the kit that I have or sign up to take a class with a friend
\end{itemize}

What else do I want to accomplish?
\begin{itemize}
\item I would like to figure out what I want to do after graduate school
\item I would like to finish at least most of my thesis research
\item I would like to make significant progress on writing my thesis
\item I don't think that I want to do NaNoWriMo again. It was fun the past few years, but I know myself now well enough to know that the way I should grow as a writer is by writing better, not necessarily writing more.
\item On that note, I would like to finish the book on craft and read at least the other books that my friends have given me for Christmas.\footnote{or will have given me, as the case may be (don't ask)}
\item I would like to read through a lot of the books that I've checked out, and I would like to be able to return them with the knowledge in my mind
\item I would like to be better at putting myself out there, at least in terms of presenting a genuine version of myself more readily.
\item I would like to apply for a job in whatever field I end up deciding feels right for my next steps
\end{itemize}

Wow that's a lot of things that I want to do.
I guess that I should either reduce the goals or increase my productivity.
Those both sound like a lot of work, so we'll see what ends up happening.
For now, time to look away from this and do work for the day, rather than looking months into the future.
\end{document}