\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-june-23.html}{Monthly Reflection}}
First Published: 2023 July 1

\section{Draft 1}
I missed a day of writing, but such is the nature of life.
I had fun with friends and volunteered, which is probably better.
My goals last month with their status:

\begin{enumerate}
\item Accomplishments/Finite Tasks
\begin{itemize}
\item I played and sang at a friends wedding!
\item My talk was written and performed
\item My instrument did not run, but it was not my fault finally.
\end{itemize}
\item Growth
\begin{itemize}
\item I'm once more ashamed of my living conditions, but it's a faster fix this time I'm sure
\item I blogged a fair amount! I also wrote a total of a little under thirty five thousand words. That's fewer than May, which is a little surprising. Then again, I suppose that I did lose a few weeks of writing altogether.
\item Exercise was intermittent
\item Sleep was intermittent
\item I didn't make enough time for sleep
\item I'm a little under three chapters ahead
\item I wrote a song!
\item I wrote three letters to friends, though only mailed two.
\end{itemize}
\end{enumerate}

Looking forward, I would like to:
\begin{itemize}
\item Make my home clean again and invite a friend over. I have actual time in it this month, so that should be easier.
\item Continue blogging/find a way to do it during my conference. I know I won't have time for it next Thursday, because I'm volunteering.
\item I'd like to exercise more. Ideally daily, but
\item Once again, I'd like to develop a sleep schedule that gives me enough and gets me up early (6am)
\item I'd like to make more time for prayer, or at least be more intentional about my prayer
\item I absolutely need to get five chapters ahead, if only because I want to start monetizing.
\item Doing some sort of poetry each day seems like a doable goal, if not a low bar.
\item I would like to get through my stack of letters\footnote{including the two new ones I need to add}
\end{itemize}

That seems like a doable set of goals.
Today I get to give a talk in a state park again, which I'm beyond excited about.
\end{document}