\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-april-23.html}{Monthly Reflection}}
First Published: 2022 May 1

\section{Draft 1}
So, you know, I kind of fell off writing this again.
In my defense, I did write just under 80,000 words last month, so most of my mental energy was occupied elsewhere.
In \href{reflection-april-2022.html}{last year's} version of this post, I set the goals of blogging, poetry, and stretching daily.
I also, humorously enough, set the goal of finishing the first draft of the book that I'm now putting out as a web novel.

My goals for the month come in a few shapes.
\begin{enumerate}
\item Professional:
\begin{itemize}
\item Start running my first instrument. I have a conference in about a month and a half, and I really need to start collecting data.
\item Finish building the second instrument. More or less as above.
\item Finish TA'ing for the semester. There isn't too much to this goal, since I just need to grade a few items.
\item Prepare for a talk at a state park. I can recycle most of my content from last year.
\end{itemize}
\item Personal:
\begin{itemize}
\item Deep clean my home. It's messier than I'd like.
\item Keep up with the book that I'm writing/finish the other one. One book brings me joy, the other doesn't.
\item Relearn bagpipes. I'm playing at another wedding this summer, and I need to be able to do so.
\item Practice instruments more. I miss being musical.
\item Write a song. I have an idea that's been floating around for a few days that I think I just need to make time for
\end{itemize}
\item Growth:\footnote{I see this as different than the two above in that this is aspirational and focused explicitly on future benefit}
\begin{itemize}
\item Make more time for prayer and meditation. I felt better for the few weeks that I made the time to do this.
\item Write at least three letters to friends and mail them. I've talked to a number of friends who mentioned wanting a hand written letter. It's fun to write them.
\item Blog more. I'd like to say daily, but, as I pointed out a year ago, that's a strange level of both too high for realistic and too low for aspirations.
\item Run more. I like the way I feel when I can run, for all that I hate running. I suppose I could start swimming instead, but.\footnote{but nothing honestly, pools just have more restricted hours/require more planning.}
\item An actual aspiration: It would be fantastic to hit 1000 pounds in my 1RM for the big three lifts.\footnote{Squat, Deadlift, Bench Press.}
In theory I'm at about\footnote{305+355+205 =} 865 pounds, which is much closer than I thought. If I manage to actually keep up lifting 3x a week this month, it should be very doable.
\item Get to bed early enough that I can get up at 6 am every morning. I find that if I start my day early\footnote{Yes I know that I used to be actively swimming laps at 6am, but I never really enjoyed it} by writing or doing something else productive\footnote{i.e. baking bread} I become much happier and more productive for the rest of the day.
Unfortunately, that means that I need to be smart and go to bed earlier.
\end{itemize}
\end{enumerate}
Welp, that's certainly a lot.
Hopefully I manage to do at least most of these most of the time!

Generally, it looks like my professional goals are all deadline based, which makes some amount of sense.
My personal goals are generally musical, which is interesting.
My growth goals seem to focus on fitness and putting out writing.
No real commentary there.

Anyways, hopefully see you\footnote{the hypothetical reader reading this before my next post} tomorrow!
\end{document}