\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflections-on-readings-3-advent-c-24.html}{Reflections on Today's Gospel}}
First Published: 2024 December 15

\section{Draft 1}

It may have taken 6 years, but I'm finally reflecting on the same Sunday Gospel more than once.  
While reading today, the two things that most struck me were the fact that the first paragraph of the gospel was almost entirely secular advice, and the second half was almost entirely spiritual.  
I know that the distinction is not necessarily true, but an atheist should take no issue with anything in the first paragraph.

My other major takeaway was the wheat and the chaff. Since fire was used in reference both to baptism and the burning of the chaff, I read it as saying that we are the wheat whose chaff is being burned off.  
Chaff, as we all know, is not something independent of wheat. It is the outer covering, which we remove because we don't want it.  
Likewise, the sin in us is the chaff that we need to not just separate from, but burn away entirely through the healing power of Christ.

I'm really fatigued today, so that's all I have, other than a quick look to see what has changed in the past six years.

Ooh! I focused on the fact that it was Advent, and mentioned that we should focus more on the joy aspect of the faith.  
That's still true, but it's interesting how my takeaways have changed through the years.  


Goals:  
\begin{itemize}  
\item One offs:  
\begin{itemize}  
\item Talk to boss about Ph.D. timeline  
\item Pick a topic for a science communication article  
\item Make a list of the stretches I'll do each day  
\item Find a place to volunteer  
\item Paper hit list  
\item Compile a list of people I want to write letters to  
\item Muse about macros and micros  
\item Compile a list of 20 meals that I can make, with their ingredients (inc. shelf stable or lifetime), time, effort level, and nutrition info  
\item Figure out my motivation for each book and have it as the bookmark  
\item List of things that need to be cleaned and the frequency  
\item List of things in my life  
\item Make a list of musings to do  
\end{itemize}  
\item Weekly:  
\begin{itemize}  
\item Spend 30 minutes 2x a week working on writing the song. Started working on the choral piece today. Realized I got two prayers\footnote{Ave Maria and Salve Regina} mixed up in my head, so now deciding whether to keep the mishmash of the two prayers or pick a single one to stick to.  
\item Ten minutes 4x a week on drawing. Did it last week, ready to go this week.  
\end{itemize}  
\item Daily:  
\begin{itemize}  
\item Define how I'm feeling each day at start and end. eh, doing ok  
\item Practice guitar daily (at least one scale and a chord progression). Yup  
\item Muse daily. almost a week!  
\item Stretch Twice a day. yes!  
\end{itemize}  
\end{itemize}


\end{document}