
\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}  
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{reflection-june-25.html}{Monthly Reflection}}  
First Published: 2025 July 14 (because I forgot to hit post)

\section{Draft 1: 8 July 2025}

Welp, here I come a full week late with a reflection on the last month.  
It was, as every month seems to be, just absolutely full of events.  
In particular, the travel I did towards the end of the month meant that I was away from my computer more\footnote{good}, and therefore writing far less on it.\footnote{un-good}  
I really want to get back into the habit of doing this, in part because I also really want to get back into the habit of the daily reflections.  
With that in mind, though, let's get into the meat of the reflection.

Last month I thought I would be excited for:

\begin{itemize}

\item Seeing a close family friend's wedding. Went, it was super fun! It was a little sad because they had a memorial to my mother up, but that's also really sweet in retrospect. The week before it we visited other family friends, and that was also really nice.

\item Visiting a friend. Also super fun! Ended up happening after the conference, because I don't know how time works, I guess. We went to a zoo and a science museum. Great times, and it was really lovely to meet his fiancee.\footnote{English lacks diacritics, and so critics can be satisfied knowing this is an active choice of mine}

\item Presenting my research at a conference. Went really well! Unfortunately, the calculations were still ongoing at the time of presentation, and so I didn't end up having as nice of one as it happened.

\item Singing in a few more concert-like events. They were really fun! Turns out one of them was the governor's party, and they had us acting as guests when not singing.  
The other one was pretty bog standard.\footnote{where does that term come from? I wonder}

\item It happened today, but going to a friend's\footnote{since I'm friends with both parents, not entirely sure how to possessive that word} baby shower! It was so nice to celebrate with them.  
I assume this was true!

\end{itemize}

Last month's must dos!

\begin{itemize}

\item Finish the presentation that I'm giving on Friday and then again at the end of the month

Woo! Gave the presentation that Friday, and gave it again at the conference. It was significantly improved by the second go round, and I do think that the Friday version helped with that.

\item Continue applying to next steps

Not really doing, which I'll likely discuss more below.

\item Make progress on my thesis

Lots! Boss is happy with the work rate.

\end{itemize}

Last Month's hopefully dos!

\begin{itemize}

\item Make an actual list of everything that needs to happen before I can submit the paper. I don't think that I officially had that happen, but it remains a good task.

\item Do all of those things. Nope! Paper is not submitted, which means that at least something isn't working. I keep being 99\% done with the project only to find a problem in the code that means I need to redo a lot of the work.

\item Finish the presentation and make it good. I got a lot of compliments on the presentation, even though many people were also disappointed by some of the findings.

\item Finish the chapter of my thesis on the program.  
I completely spaced this one, so it goes on my new\footnote{ugh someday I'll get into some sort of ordering that works for me, I hope} list.

\item Rewrite the chapter of my thesis on the apparatus I used. Done, but I did a bad job of it.

\item Keep up on my web novel. Lol, nope! I feel really bad about it, though, which is like doing it?

\item Keep up on this site. See above.

\item Do music. I jammed with a friend one of the days, and then left my guitar in its case for a few weeks. I did buy two harmonicas\footnote{one necklace worn that's a single octave and one in I think key of D}, and they were fun to play.  
I also sang a fair amount, I think?

\item Take care of myself.

Eh, by the end I was certainly disregulated.  
I think that's mostly because I love routine.

\end{itemize}

What did I dream of doing last month?

\begin{itemize}

\item Finish the Paper -> as above.

\item Write a full outline of the rest of my thesis. I actually think that I did this! Wild

\item Writing a folly a day. you can see that this is not happening.

\item Getting a backlog of chapters ready for the web novel. Nope!

\item Finish the presentations that I'm going to be giving in July. I give my first one on Thursday, and I have the loosest sketches of a beginning, which I started making yesterday.

\item Get the video series done. I did absolutely nothing on it.

\item Record the new song I wrote. I sang it for the friend, and she enjoyed it.

\item Write a few more songs. Nope!

\item Record a few more songs. Nope!

\item Jam with other people. Once or twice.

\item Find my next steps. Yeah!

\item Once again become comfortable with silence. I think so, honestly. It's really nice having my headphones on even and especially when I'm not listening to things.  
My brain is once again in a space where I can't listen to things while using my mind, which is good to know.

\item Spend the time I need to confront the faith issue that's been boiling in the background for a few months now.

I forget if I wrote about it, but did actually figure out some of it, een\footnote{I meant to say even, but I hae been using hae in texts lately, and may also get into een} if I didn't, I did end up resolving a lot of it.

\item Learn shorthand and start writing it with my left hand.

Lol, I was so optimistic.

\end{itemize}

Before getting into the priorities, let's look forward to this month\footnote{and what's already happened in it}.

Five things I was excited about last month that I didn't know would happen:

\begin{itemize}

\item Getting to go to a family-hosted board game night again.  
\item Went on a brewery tour  
\item Saw the cryptozoology museum  
\item Went to a number of breweries!  
\item Started brewing again.  
\end{itemize}

Five things that excite me about this July:

\begin{itemize}

\item Visiting a friend! Did it  
\item Giving a talk this Thursday to some high schoolers. I'm still really excited for i, even if I am growing incredibly nervous about how I'll do.  
\item Getting into a routine again! I haven't really had one, but the fact that I'm gone basically all weekends means that it's a routine of sorts? I hope at least.  
\item Going on a visit to the place I got a job offer for!\footnote{woo! employable}  
\item Getting to give a talk on an island I've always wanted to visit!

\end{itemize}

Last month I did must, want to, would dream of. This month I'm just going to do should and would love.

What should I do this month?

\begin{itemize}

\item Get back into the web novel  
\item Get back into follies  
\item Write journal daily  
\item Eat well  
\item Stretch  
\item Sleep  
\item Clean  
\item Research  
\item Creation

\end{itemize}

Honestly, I think that I'm mostly just recreating the list of daily reflection, so let's go down there and try making the new one.

Last Month's daily reflection\footnote{unlike most times, I'm not doing my daily reflection before writing the new one in large part because I need to get back into writing somehow, and this seems like the best way}:

\begin{enumerate}

\item Did you journal by hand, and do you feel like the stormy questions in your mind got on the page?

\item Did you do your best to sit in still silence?

\item Are you making sure that each task is given your full attention, not just because the task deserves it, but because you deserve the luxury of doing a single thing at a time?

\item Are you focusing on your posture and breath?

\item What in your body is holding tension right now? How can you fix it? When will you fix it?

\item Comments on sleep?

\item How's eating going? In particular, how are you doing with eating plants and unprocessed food?

\item Are you neglecting any of your familial obligations? If so, how can you rectify this?

\item Cleaning: what is the biggest priority you have right now, and what is the next action item for it?

\item Thesis: current task. What's preventing you from finishing it? How will you remove that obstacle?

\item Thesis: next task. What will you need to be able to do it?

\item What's the next job you're applying to?\footnote{note that this might be a \say{things we don't post} but}

\item Are you intentionally trying to spend time with others?

\item Are you doing your absolute best to ensure that you and those you interact with view the interactions in the same light? Are you sure?

\item Are you keeping up on this daily set of reflection questions?

\item Are you keeping up on writing the follies? If not, what's in the way?

\item How are the long form follies coming? Do you feel like they're weighing you down right now?

\item Are you writing poetry? When, and what were your takeaways from the previous day's writing?

\item Are you making music? If not, what is in the way?

\end{enumerate}

How resonant is the list right now? Decently, though I think that I want to change a few things.

\begin{enumerate}

\item Did you journal a full page today?  
\item What ink/pen did you use, and what were your thoughts on it?  
\item How's prayer?  
\item How's focus?  
\item How's sleep?  
\item How many meals, and how balanced?  
\item How's the posture?  
\item How's the breath?  
\item How's the movement?  
\item How's the physical flexibility?  
\item How's keeping up with the family obligations?  
\item How's the thesis?  
\item How's the poetry?  
\item How're the interpersonal relationships?  
\item How's the music?  
\item How's the other writing?  
\item How's the cleaning?  
\item How's ordering the life?  
\item water?

\end{enumerate}

I'm sure that I'll reorder this on another day, but for now it feels good enough. So, then, let's fill out the daily reflection, I suppose!

\begin{enumerate}

\item Did you journal a full page today?

Just about!

\item What ink/pen did you use, and what were your thoughts on it?

I worked with a Kaweco Perkeo, and I was using Private reserve Vampire red. It is more brown than red, I'd say. The Kaweco is definitely not a heavy flow pen, and so the ink often went on the page almost a pale salmon. On points where the ink goes down hard, it's more like dried blood. This seems to be a standard review of the color, so I don't think I'm making a mistake there!

Other than that, I do love the way that the pen feels in the hand. It's very gentle, and that's nice.

\item How's prayer?

Oops, a good thing to remember to do in the future certainly.

\item How's focus?

Eh, it's hard to get going when I have midday meetings, but I've always known that.

\item How's sleep?

Decent. Yesterday was a really low energy day, so I ended up getting to bed relatively early.

\item How many meals, and how balanced?

Today: had a waffle and have been working on a bowl of oats since then. That's a sign I should get a more protein heavy dinner, which probably means that it's time to go grocery shopping again.

\item How's the posture?

Has been generally bad lately. My shoulders feel almost permanently curled in, and at this point I'm beginning to wonder if that's just correct.

\item How's the breath?

Haven't really thought about it that much, being totally honest.  
It's nice right now to be getting a few breaths in, though.

\item How's the movement?

Stretched once today, am about to stretch again. Other than that, I walked around a bit, but not as much as I usually like.

\item How's the physical flexibility?

I can touch my toes, my shoulders feel tight, and I find myself crossing my feet when I lie down, which I am told is a symptom of tight hips.

\item How's keeping up with the family obligations?

I failed to listen to last week's album, and will start listening to this week's.

\item How's the thesis?

Currently the main goal is making sure all my citations and figures are looking good.

\item How's the poetry?

Nonexistent, but I think that I have time today to fix that.

\item How're the interpersonal relationships?

Generally decent! On the other hand, I haven't really been seeing people, in large part because I have been out of town.

\item How's the music?

Not great, I think that I'm most of the way through the song for the wedding.

\item How's the other writing?

Non-existent. Mostly that means the novel.

\item How's the cleaning?

I can do better!

\item How's ordering the life?

Eh. I have a to do list!

\item Water?

Much better today than ever before!

\end{enumerate}

\end{document}