### monthly reflection

\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}  
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{reflection-september-25.html}{Monthly Reflection}}  
First Published: 2025 October 5

\section{Draft 1: 5 October 2025}

Wild, \href{reflection-august-25}{last month} I posted and wrote on the 4th.  
This month I do so on the 5th.  
Hopefully this is not a trend which will continue.  
I'd like to get back into daily postings, but who can say if that's doable.  
Still, today is the last day before I become a company man, which means that it's a perfect time to think about the past month and my past life.

Reflecting on last month, daily follies didn't really end up happening, nor did finding a better term for them than follies.  
Dictionary of terms started to happen, but only very briefly.  
Have yet to really start making up terms, which is a bit of a shame.

I rebound my web novel, but only read the first fifteen or so of three hundred some chapters.  
This month, I think that it might be more productive to instead plot out the rest of the series.  
I just today watched a video on plotting, which suggested that the story should be seen as a series of arcs, each of which feeds into the next, which is slightly more intense, until the very end, at which point obviously the plot peaks.  
There's probably an element of that which would be good to do.  
At the very least, I think that it could be good to remind myself where the series is supposed to end, and then figure out how to get there.  
Since it's been long enough since I wrote anything for it, I don't think that pantsing it\footnote{NaNoWriMo term for writing without plotting} is going to work for me.  
Next month is NaNo though, so there's something to be said about waiting to start writing until that starts.

Eh. We'll see what happens as it happens.

I was on screens maybe slightly less.

I did not write the song for the wedding, and I have only gotten about halfway through Musicking.  
Binding books went generally well, and that was fun.  
I didn't bring yarn, but I did bring embroidery ingredients, and did not use them.

Didn't stretch much, and do still note that I am often tight.\footnote{let's take a quick ten to stretch right now}  
I did just recently come into a massage gun, and it is wild how it actually works to improve flexibility.\footnote{I did the very scientific stretch both legs, massage gun one, then stretch both again and noticed that the one I gunned was notably looser}  
Shoulder didn't seem to be my issue this past month, nor did it feel like the issue today.  
Then again, I'm still not doing my historic shoulder stretches, so maybe I'm just deluding myself.

I read very little of the books that I said I would get.  
I ended up buying a few along the journey, so in a way I read negative of the books I brought.  
That being said, I have finished one of the new buys, and that is certainly something to talk about in the future.

Meditation and prayer weren't going great, and still aren't.  
I've recently started reading a book about Autistic Burnout, and there's something really interesting in it.  
Or, more accurately, there's a lot that's really interesting, but one that felt immediately actionable.

When people are depressed, they don't want to do anything, and the cure is doing something.  
When autistic people are burning out, they don't want to do anything, and the cure is doing nothing.  
I'm trying to let myself not do anything, and I am taking a lot of naps these past few days, which isn't something I can really keep going for much longer.  
However, there's something mindful about letting myself stop for a little bit.

I did do some meditation/prayer on the trip, but actively doing the rote prayer from my past still hurts a lot, and I don't really know why.  
I'll make time to try that this month.

I didn't journal a ton, and that's fine.

I did buy a sketchbook, because the part of me that wants to draw when I have nothing else going on did in fact rear its head.

Old daily reflection:

\begin{itemize}

\item Did you journal by hand today?

\item Did you do a folly?

\item Did you in some way, shape, or form advance the web novel?

\item Did you work on music, whether education or creation?

\item Did you work on book binding?

\item Did you work on another hobby?

\item Did you stretch? Really?

\item Prayer?

\item Meditation?

\item Reading?

\item Minimizing screen time?

\end{itemize}

New daily reflection:

\begin{itemize}

\item Did you stretch?

\item Did you attempt to pray something rote?

\item What's going on in writing?

\item How's work?

\item Reading?

\item Sleep?

\item Water?

\item Food?

\end{itemize}

\begin{itemize}

\item Did you stretch?

Yes!

\item Did you attempt to pray something rote?

No. Last night I sat and realized that it's basically been a year since my mom died, and being sad sucks.

\item What's going on in writing?

Eh, doing this.  
Watched/listened to a few videos about writing from someone who seems like they might be right-wing, but most of the advice is still useful to me.

\item How's work?

About to start.

\item Reading?

Restarted don't die alone and kept going through autism.

\item Sleep?

Eh, I'm doing a lot of it which might be good?

\item Water?

I feel like I'm more aware than normal which is good.

\item Food?

See above.

\begin{itemize}  
\item Hongdian Black with Fude Nib: Diplomat Caribbean (8/30ish)  
\item Jinhao Shark: Diplomat Caribbean (8/30ish)

\end{itemize}

\end{itemize}

\end{document}