\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}  
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{reflection-july-25.html}{Monthly Reflection}}  
First Published: 2025 September 4 (whoops, never hit post)

\section{Draft 1: 2 August 2025}

Woo! Another month, another chance to realize that more than four weeks have passed me by.  
I am three weeks and two days away from my defense, which is horrifying.  
At the absolute minimum, I must give my committee a week to read the thesis, which means that I have just over two weeks to be fully finished with everthing.  
The travel this month has also messed me up schedule wise, and I've also not follied as much as I'd like.  
Or, I guess, the folly was not writing the follies?

Five things that excited me about this July:

\begin{itemize}

\item Visiting a friend! Did it before July reflect  
\item Giving a talk to some high schoolers. It went decently, but the host pointed out that I went a little fast.  
That's good feedback, and something for me to remember going forward for sure.  
\item Getting into a routine again!

I mean my sleep and eating was at least a little better, but I don't know if I'd call it routine.

\item Going on a visit to the place I got a job offer for!

Visited! Was great.

\item Getting to give a talk on an island I've always wanted to visit!

Was just so much fun, apparently the entire island showed up.  
I almost missed the last ferry there because it turns out I actually needed to take two ferries.

\end{itemize}

Last month's stuff:

\begin{itemize}

\item Get back into the web novel: realized that I don't have mental space for it right now. Am hoping that during September, when I'm also planning on doing a bunch of travel, I'll feel up to it.  
\item Get back into follies

Eh, did not do a great job with that.

\item Write journal daily

I journalled fairly often, but again, not as often as I would have liked.

\item Eat well

eh

\item Stretch

I did certainly get into more of a habit of this!

\item Sleep

I honestly think I did pretty decent in regards to sleep  
\item Clean

Home is cleaner, life is more ordered

\item Research

Finally did\footnote{what my advisor called a very cursory} data analysis!

\item Creation

Thesis is a form of creation, and so is the music I made with friends.

\end{itemize}

This month, the only things I can think of happening are my birthday\footnote{...I should check on 26 for 26} and my defense.  
However, I'm sure there will be more, which I can think about in the future.

\end{document}