\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-april-22.html}{Monthly Reflection}}
First Published: 2022 May 2

\section{Draft 1}
Another month, another reflection.
My goals for April were:
\begin{enumerate}
\item Blog daily (starting now). I think that the reflection it makes me do is really useful. I do think that I need to find a better way to ensure that I have time for it, though.
\item Write a poem a day. I just bought a book of poetic forms, so it would be good to start working through them.\footnote{Look forward to postings about that.}
\item Stretch daily. I tried to stretch this morning and was shocked at how inflexible I am.
\item Listen to BiaY daily. I really don't like how far behind I am, and I'd like to catch up sooner than later.
\item Reach 60K words in the book. If past months are indicative, that's a goal I can accomplish. I think I may need to do some more planning, rather than writing by the seat of my pants, because I'm starting to get into a bit of a rut in terms of writing. Maybe it's just that I have continued this section of the book for far too long.\footnote{If I keep thinking about it here it'll become worth its own blog post, and I refuse to do that.}
\item A secondary goal for the book is to write every day, even if only a few words. I think it's good to develop good habits, though I guess I should think about balancing doing something because I enjoy it with getting work done. That's another thing to think about I suppose.
\item Practice guitar every day. I like the sound of guitar, and I would love to be able to play longer without my fingers hurting.
\end{enumerate}

I blogged mostly daily.
I wrote few poems.
I stretched almost every day, which was really nice.
It's a great way for me to start the day, and I like how I feel when I stretch in the morning.
I did not listen to BiaY daily, and I think I'm further behind again.
I did reach 60K words! As of April 30 I was at 62540 words, which is pretty cool.
I wrote most days, though it's beginning to look like I need a day off, so I don't write on Sundays.\footnote{weird how the Bible and Church agree that we need a day off}

My goals for May are mostly the same.
It's here that I run into the issue of goals, though.
If they're meant to be aspirational, then many of them are set too low.
If they're meant to be realistic, then I should really accept that I don't write poetry every day.
I don't know if I can agree to either premise so I'll shoot a little higher and be ok with failure.

In May:
\begin{enumerate}
\item Blog daily. I still like how it forces me to think about something every day.
\item Write a poem a day. I need to do this more and I will try.\footnote{starting tomorrow}
\item Stretch daily. I like how stretching makes me feel, and maybe I'll be able to touch my toes at the end of the month.
\item Listen to BiaY 7 times a week. This feels more aware of my tendency to listen to three or four in a row.
\item Finish a draft of the book I'm writing.\footnote{likely 100K words, 50 chapters} This may be optimistic, but in theory these past two weeks suggest I can do it.
\item Practice guitar every day. I've been getting better and I really like it.
\item In professional news: finish a reasonable draft of my exam. I need to write this, and soon
\end{enumerate}
\end{document}