
\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}  
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{reflection-august-25.html}{Monthly Reflection}}  
First Published: 2025 September 4

\section{Draft 1: 4 September 2025}

Another month gone by!

I finished my defense, which in retrospect was probably as all-consuming as I should have expected.  
Sadly, I did not keep up on this site, nor did I really do much of anything else.  
This next month, however, I have nothing scheduled other than travel and seeing friends, which means that I can get back to the things that are important to me in general situations.  
I don't realllly feel like doing a look back at last month's stuff, but that's a part of the tradition so.

...

...

...

Oh, so the only stuff that I looked forward to was my defense and my birthday.  
Wait wait, my birthday was also last month.  
Wow that feels so very long ago, even if I can intellectually recognize that it wasn't.

Anyways, I defended, and am therefore Dr.  
Let's spend this space thinking about my monthly goals and daily goals and whatnot.

...

I want to do daily follies, and since I have nothing else scheduled, that should be doable?  
I have an idea to start making a dictionary of terms as I'm going to use them, because I don't really care what the standard meaning of words is, especially in context of wanting to distinguish similar ideas.  
The more I learn about philosophers, the more it seems like that's a thing that they do a lot, so as a Doctor of Philosophy\footnote{no, I don't think that I'm going to be tired of saying that for ages}, I too have that right.

As a child I used to be told that doctors get the right to make up new terms, which is something I plan to take advantage of as well.

I want to get back into my web novel, which will likely involve reading some emotionally charged notes from readers.\footnote{last time I logged on, someone sent me a private message expressing worry about me saying I was in a tough spot and then going radio silent}  
In order to do that, I should like\footnote{mmmm should like and would like feel different in some way} to reread the book, because I have forgotten much of it.  
Since I'm generally trying to be on screens less\footnote{which I realize is antithetical to doing these follies}, I think that I'll set it up to print and print it out today?  
That could be fun.

I want to get back into hobbies, even if I'm not sure which.

I have to write the song for a wedding, so that could be a thing that I should start on basically right away?  
I have the few books on composing that I have been wanting to read for a while, so can treat them together.  
I plan on binding the books for the different things that I want to read, which is a related, though distinct hobby.

Could be fun to bring a ball of yarn with me and just see whether I make anything fun out of it?\footnote{oh, I didn't say that here but I'm going on a train trip and I'm beyond excited}  
Might as well.

I want to improve my physical health.  
Mostly, I think that means that I want to be stretching much more than I am, because oof am I unflexible and tight\footnote{distinguished here by tight having connotations of notable pain in normal movement}.  
Eating better is also an idea, though the fact that I'm traveling more or less non stop might make that a bit of a nonstarter.  
I could spend some time thinking of a good stretching routine.  
Right now I'm too inflexible in my shoulders that my default shoulder stretches seem terrifyingly difficult.

I want to read more, and especially more high brow stuff.  
With that in mind, I did also print out a bunch of books, and I have even more I'm planning to pack with me.

I should absolutely get into meditation and prayer again.  
I think that it would be good to attempt a few minutes of meditation and a few minutes of intentional prayer a day.  
I'm finding myself more and more unsure of my faith, and hopefully some thinking and sitting will help with that.

None of the other things in the daily reflection really speak to me, even if the pen list will probably stay because I am enjoying it right now.  
I don't love the journals that I'm using for journaling right now, so will probably spend some time exploring different options.  
Might go back to my old one, might go to one of the many I've been gifted lately, might find some third option.

This means my daily reflection should look like:

\begin{itemize}

\item Did you journal by hand today?

\item Did you do a folly?

\item Did you in some way, shape, or form advance the web novel?

\item Did you work on music, whether education or creation?

\item Did you work on book binding?

\item Did you work on another hobby?

\item Did you stretch? Really?

\item Prayer?

\item Meditation?

\item Reading?

\item Minimizing screen time?

\end{itemize}

and to answer:

\begin{itemize}

\item Did you journal by hand today?

No, but I think that I might count this.

\item Did you do a folly?

Behold.

\item Did you in some way, shape, or form advance the web novel?

I'm typesetting it now to be printed, and then will print it, and maybe even do some book binding of it?

\item Did you work on music, whether education or creation?

Nope!

\item Did you work on book binding?

Will do with the web novel.

\item Did you work on another hobby?

Uhhh I cleaned!

\item Did you stretch? Really?

No. I'll do something quick now though.

\item Prayer?

Nope, will plan on soon though.

\item Meditation?

Nope.

\item Reading?

Yes!

\item Minimizing screen time?

Not in the slightest.

\begin{itemize}  
\item Hongdian Black with Fude Nib: Diplomat Caribbean (8/30ish)  
\item Jinhao Shark: Diplomat Caribbean (8/30ish)

\end{itemize}

\end{itemize}

\end{document}