\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflections-on-readings-3-advent-c.html}{Reflections on Today's Gospel}}
First Published: 2018 December 16

Zephaniah 3:17 \say{The LORD, your God, is in your midst, a mighty savior; He will rejoice over you with gladness, and renew you in his love, He will sing joyfully because of you,}

\section{Draft 1}
Today, we hear the prophet Zephaniah speak about the coming of the Lord.
Obviously, since we are in Advent, the Gospel does as well.
However, while John's call to the people is focused on the glory and fear the Lord will bring when he descends, the first reading focuses on the positive aspects.
The people are told to \say{shout for joy!} and \say{sing joyfully.}\footnote{Zephaniah 3:14a}
We hear that the coming of the Lord will bring joy and salvation.

This is really the part of the Word I feel we don't talk about enough.
Yes, there are rules we are to follow.
Yes, we are called to take up our crosses.
Yes, we are to love as Jesus loved.

But, the Lord also forgives us.
He brings us safety.
And, in these cold days while we await the coming Lord, the joy of his love should keep us warm.
\end{document}