\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-january-23.html}{Monthly Reflection}}
First Published: 2023 February 1

\section{Draft 1}
Another month has passed me by!
I said my goals last month were
\begin{itemize}
\item Blog daily. I have faith in myself.
\item Listen to the BiaY and CCCiaY on average once a day each
\item Stretch daily
\item Write a poem a day
\item Write a piece of music a day
\item Write through Chapter 35 of the book I'm self publishing
\item Practice music daily
\item Say a rosary a day
\end{itemize}

In reality I:
\begin{itemize}
\item Blogged 12 times.
\item Listen to the BiaY and CCCiaY much less than once averaged
\item Stretched at least 10 times
\item Actively gave up on the poetry goal.\footnote{which is a first}
\item Wrote Fifteenish pieces
\item Wrote through Chapter 23 of the book I'm self publishing
\item Practiced music most days
\item Said very few rosaries
\end{itemize}

On the other hand, most of the time, I was not aimlessly wasting away my time, which is one of the reasons I wanted to have more activities to do.
I found that my scheduled list of events ceased to be useful about when I started being busy again.

Other things I did this month include:
\begin{itemize}
\item Being asked to play for a musical and spent about 10 hours last weekend recording guitar
\item Finished a draft of my 1 page for my third year exam
\item Started lifting with friends!
\end{itemize}

All in all, I'm glad for the month, for all that I really wish that i had recorded more of it here.
It passed by in a blur, and that makes me sad.

\end{document}