\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-july-23.html}{Monthly Reflection}}
First Published: 2023 August 1

\section{Draft 1}
Woo! Another month passed.
It hardly feels real that it's been a month, but what a month it's been.

I gave \href{universe-2.html}{three} \href{universe-3.html}{talks} in state parks, signed up for another four(?), and very recently was reached out to for another two talks this fall about the eclipse!
I went to a \href{conference-2.html}{conference}.
I went to a \href{mission-trip.html}{mission trip}.
I rediscovered my love of pinball.

I finished the first book in my web serial.
I finished the first batch of lemon wine for the summer!\footnote{which I apparently never blogged about. Whoops! Blog incoming eventually.}
Last night, I made it back to an open mic for the first time in a while.\footnote{musing to come}

So: looking back at my goals.
\begin{itemize}
\item Make my home clean again and invite a friend over. I have actual time in it this month, so that should be easier.

I don't know why I thought I was actually at home this past month. By the 19th I had spent a total of four nights in it. It was a packed month.
Home is cleaner, though still too cluttered.
\item Continue blogging/find a way to do it during my conference. I know I won't have time for it next Thursday, because I'm volunteering.

I did not blog anywhere near as much as I would have liked to, but I did at least get seven in last month. That's more than half of June.
\item I'd like to exercise more. Ideally daily, but

I exercised nowhere near as much as I in theory want, for all that I don't feel like I was particularly sedentary. I am far stiffer now than ever before in my life, though, so morning stretching might need to return at a minimum.
\item Once again, I'd like to develop a sleep schedule that gives me enough and gets me up early (6am)

Sleep schedule was generally pretty 6am centric. I don't think all of the breaks were my fault.
\item I'd like to make more time for prayer, or at least be more intentional about my prayer

Prayer was not as intentional as I would've liked, but it's a journey.
\item I absolutely need to get five chapters ahead, if only because I want to start monetizing.

I am just under four chapters ahead right now. That's better than nothing.
\item Doing some sort of poetry each day seems like a doable goal, if not a low bar.

I wrote maybe three poems.
\item I would like to get through my stack of letters\footnote{including the two new ones I need to add}

I think I'm through every letter I meant to write at the start of July.
My list is now only five long.
\end{itemize}

This upcoming month I'm excited for:
\begin{itemize}
\item My birthday!
\item Giving five talks in state parks
\item Sharing lemon wine with friends
\item Finishing my stack of letters\footnote{and I would love to get one back, but that's not in my control so eh}
\item Starting to do open mics regularly again
\item Staying up on all of my book clubs
\item Making progress on research
\item Monetizing my story?\footnote{feels like I should put it here, idk the idea of monetizing is so stressful}
\end{itemize}

Using last month's goals and the excitement as a way to generate a list of goals:
\begin{itemize}
\item Finish my presentation on the Pleiades.\footnote{one of my double headers is over the peak of them and requested two distinct talks}
\item Make my home clean again. It was at the start of the summer, so I know it's possible.
\item Blog more. Last month I wrote 12 percent less\footnote{as measured by my word tracker, so basically book words and blog words} than in June, which I think is mostly a lack of blogs.
\item Stretch daily? I think that would be good for me and probably doable. I'll need to stretch after this, which is less than ideal since it's already past my bed time, but eh.
\item Sleep enough and have a sleep schedule based around waking up no later than 6\footnote{earlier wouldn't be the worst thing, though that does conflict with wanting to do open mics}
\item Be more intentional about prayer.
I think one thing that could help is making an actual commitment to doing a rosary at the chapel before work every day, on the road days that I'm not in Madison, before Mass on Sundays, and during a walk on Saturdays.
That's at least a little bit I can do, though today it will have to come after stretching.
\item Get further ahead on the book.
In particular, I'd like to set the goal of more than four chapters a week.\footnote{so starting/finishing a fifth at least.}
That seems both very doable\footnote{especially since I can write two chapters on a good day} and helpful to me.
\item Write poetry every day.
I need to remind myself that I like the way I am more when I do more poetry.
I do, so hopefully this works.
\item Finish stack of letters, and maybe think of more people to write to? Otherwise, start journaling during my morning time?
\item Write a song. I loved premiering my new song last night, and want to do that more.
\end{itemize}

So, my daily reflections will look like:\footnote{regrouped so that like are with like}
\begin{itemize}
\item Did I work on presentations?\footnote{after the Pleiades, I should make my eclipse talks}
\item Did I make progress against entropy in my home?
\item Did I blog today/yesterday, depending on when written?\footnote{which is a bit obvious}
\item Did I write book today? How many chapters am I at this week /4+?
\item Did I write poetry today/yesterday, depending on when written?
\item Did I write a letter/journal today?
\item Did I work on a new song?
\item Did I stretch?
\item Did I prioritize sleep?\footnote{a probably healthier question to ask}
\item Did I pray the rosary? Was it intentional? Did I prioritize other prayer today as well?
\end{itemize}

As an example:\footnote{and for today, since it is a day in August (wild)}
\begin{itemize}
\item Didn't do much work, honestly.
\item Slight progress against entropy.
\item Blogged today, forgot yesterday/got home well past bed time and fought my keg.\footnote{musing incoming.}
\item Wrote about half a chapter today .9/4+
\item Will write a poem after this
\item I did not write a letter or journal today.
\item I did not work on a song.
\item I will stretch.
\item I tried to prioritize sleep today, though I'm not by writing a poem and stretching after this.\footnote{except in the grand scheme, I kind of am}
\item I do not think I'll be awake through a rosary today.
\end{itemize}


\end{document}