\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-2024b.html}{Reflection}}
First Published: 2024 December 9

\section{Draft One Written 7 December 2024}

It's been more than a day since my last post, which is not exactly what my goal was.  
Alas, the world is what it is, and I became far too optimistic about how much mental and emotional energy I had and would need to write the posts that I had been planning.\footnote{Thinking I had far more and it would take far less, respectively}  
Still, I do know myself well enough to know that daily musing does, in fact, make me feel generally better about life, and since I want to get back to writing my web serial\footnote{I'm terrified to see what comments have been left while I've been away}, this feels like the good and gently way to slowly edge back into it.  
With that in mind, I think that I'm going to treat this like I treat the beginning of most periods of my life, and go for some goal creation.  
Unlike most of my reflection posts, however, I'm not going to be looking back at old goals.\footnote{for the triad of reasons: I don't want to, I'm worried about what I'll find, I don't know how applicable they are to my day to day these days}

Also unlike most of my reflections, I don't think that I'm going to focus on deliverables as much.\footnote{or, at least, I don't intend to.}  
I know that there's a lot of research talking about how goals are best when they're actionable and etc., but the most important of the things that I want to accomplish in the next few months aren't really the sort of thing that one can break down piece by piece.  
Anyways, with that disclaimer out of the way, time to stream of consciousness some goals, which I'll then organize into time frames, etc.

\begin{itemize}  
\item Learn how to use Vim keybindings. I'm doing not no scripting these days, and it does really seem like a great way to become a more efficient typist, if nothing else. Also, it always looks like magic watching someone who is good at Vim use it, and I love being the magic.  
\item Accept my grief. Right now I find myself either completely ignoring the fact that I am grieving, or else lean into it too hard and find myself becoming emotionally exhausted. Of course, this is a process, not necessarily something I can just do.  
\item Finish my Ph.D..\footnote{I always hate ending sentences with an abbreviation that uses a period} I feel like this one is self explanatory.  
\item Write some science communication articles. I still want to write a popular science book, but it's probably best to start with a few articles. Lots of novel advice for getting published after knowing how to write a novel\footnote{which, by words, I have done} involves writing short stories, for a variety of reasons, and that feels fairly parallel. Also, it's a great way to get my name out in the world. More than that, though, people seem more willing to read an article than a book.  
\item Finish the album. It's hard, because a lot of why I was working on it was reflecting on how precious the time with my mom was. In her absence, some of the songs ring hollow now.  
\item Write a choral song. I would really like to have one of my creations sung by the choir that I am in, and that requires writing something the director might want. I should probably pick some far\-ish off date\footnote{maybe one for the parish (pastorate?) day, or else one for the Church's patron? Will consider, and probably ask my fellow choristers}  
\item Get into daily musings again. It's so good for me to take time to sit and reflect on the world I inhabit.  
\item Stretch bidaily. I'm getting to the point in my life where my body will hurt if I do not take care of it. Also, the only way to reach my dream of touching my toes\footnote{I know that that is a relatively sad goal, but it is what it is} is to put forth the effort.  
\item Put myself out there. I've had great excuses for not attempting to expand my social circle, but I will always be able to find such excuses. The life I want to live involves others, and I need to make that happen.  
\item Publish my paper. I know that at this point a lot of what is holding me back is my executive dysfunction preventing me from pulling a trigger, but that doesn't necessarily make it easier to fix.  
\item Finish the web serial. I hate when books get dropped as a reader, and also I want to say that I've finished it. That being said, the primary motivation I had for writing it was my mother, and it will take time for me to accept my new reality, to say nothing of the fact that it will also take time for me to find a new motivating factor to write.\footnote{not that I do not still have any number of motivators, just that they aren't the primary motivator}  
\item Find a way to make exercise a routine thing for me. It's hard to do a series of activities, but routines are easy. As mentioned with the goal of stretching, it's important for me to take care of myself.  
\item Get back into letter writing. Given how many people in my life have moved away, or just generally like receiving letters, it would probably behoove me to begin writing them again. It's a little too late to do Christmas cards for the year, but that could be a fun idea for a template. Hmm that does bring up the question of whether I'd want to do a template or a series of\footnote{if only nominally} discrete letters to different people.  
\item Feel comfortable with myself. It's not that I feel uncomfortable in my own body and being who I am, but I don't feel as though I've truly actualized myself yet.  
\item Get a routine for food that serves me.\footnote{that is to say, find a way to make it so I can make food that nourishes my body, doesn't leave me craving, and is doable with the life I live} Routines, as mentioned above, are crucial to maintaining things. I don't want to have to write a menu out each week, and I don't know that meal prepping has ever worked for me in the past, but that's not to say that neither will be what ends up working best for me. If I can proactively make sure that the food I eat hits my macro and micro goals, though, that will take at least one piece of mental burden off of me. Might be worth spending at least a musing or two on the macros and micros I think that I need to hit.  
\item Finish the embroidery I'm doing. At first, I was thinking that I could use the embroidery as a coping tool to deal with the grief. More and more, though, it's just becoming the thing I do with my hands when I don't really want to think but want to be doing something.  
\item Get through the books that I have checked out. I have far too many books, and that's something that I need to resolve.  
\item Get back into Sunday musings about the readings. I want to get back into my faith, and that feels like a good starting place.  
\end{itemize}

Ok well that feels like a good enough list, if one that's probably both too vague and too specific at the same time. I know that setting really optimistic goals for myself rarely works out, so I'm going to try to avoid that if at all possible.  
With this in mind, what's a good way to break up the goals?  
There's something to be said for timelines, there's also something to be said for actionable versus overarching goals.  
Maybe I'll just go through them all and think about how I can work on them before the year ends?  
That seems reasonable enough.  
Other than that, I'll compile the list so that I have starting material for the future.  
So, without commentary, my goals for the foreseeable future right now are:\footnote{feels so weird to say that, as though there's nothing else that I'm hoping to strive for, but it is kind of true}

\begin{itemize}  
\item Learn how to use Vim bindings.  
\item Accept my grief  
\item Finish my Ph.D..  
\item Write Science Communication articles.  
\item Write a pop sci book\footnote{I think that I forgot to give this its own bullet point}  
\item Finish my album  
\item Write a choral song, and ideally have it be performed  
\item Daily Musings  
\item Twice Daily Stretching  
\item Grow interpersonally  
\item Publish the paper  
\item Finish my web serial  
\item Make exercise a routine  
\item Letter Writing as routine  
\item Comfort with myself  
\item Food routine  
\item Finish embroidery  
\item Read Library Books  
\item Sunday Musings about Gospel  
\item Clean life.\footnote{this one is new as I compiled the list, but I really hate the way that my life is a mess (physically speaking, if not metaphorically).}  
\end{itemize}

So, since working on all these things at once would be, frankly, insane, let's set come up with at least one way that I could work on each of them as a goal before the New Year, and then compile a list of what I'll actually do.

\begin{itemize}  
\item Learn how to use Vim bindings.  
\begin{itemize}  
\item Spend X minutes a day working on them  
\item Go through the Vim user guide  
\item Pay for access to the vim adventure  
\end{itemize}  
\item Accept my grief  
\begin{itemize}  
\item Write letters to mom  
\item Spend time each day focusing naming on my feelings  
\item Affirmations?  
\end{itemize}  
\item Finish my Ph.D..  
\begin{itemize}  
\item Spend X minutes a day working on writing it.  
\item Write an outline at the highest level.  
\item Talk to boss about potential timeline  
\end{itemize}  
\item Write Science Communication articles.  
\begin{itemize}  
\item Figure out a topic  
\item Decide on a place to post them  
\item Write a draft  
\item Figure out an audience  
\item Spend X minutes a day reading pop sci articles  
\end{itemize}  
\item Write a pop sci book\footnote{I think that I forgot to give this its own bullet point}  
\begin{itemize}  
\item Spend X minutes a day reading pop sci  
\item Spend x minutes a day writing the book  
\item Find a topic I'm passionate about  
\end{itemize}  
\item Finish my album  
\begin{itemize}  
\item Spend X minutes a day writing music  
\item Spend X minutes a (period) recording  
\item Spend time mastering  
\end{itemize}  
\item Write a choral song, and ideally have it be performed  
\begin{itemize}  
\item Figure out what a good commission would be\footnote{that is, figure out what occasion I could write a song for that would actually get performed}  
\item Spend X minutes a day writing  
\item Spend X minutes a day doing score study.\footnote{in general, I do want to get better at composition and music, and I think that writing the song was my way of saying that}  
\item Do X counterpoint exercises a day  
\item Spend X time reading and following either Renaissance Counterpoint or one of the other composition textbooks I've\footnote{i hate that I'm not allowed to end a sentence with abbreviated I have}  
\item Write Hymn harmonizations  
\end{itemize}  
\item Daily Musings  
\begin{itemize}  
\item Write a musing every day\footnote{lol}  
\item Compile a list of musings to do/schedule it.\footnote{That didn't work super well last time, but maybe this time}  
\end{itemize}  
\item Twice Daily Stretching  
\begin{itemize}  
\item Stretch twice a day\footnote{as two footnotes above}  
\item Come up with a stretching routine/find one  
\item Figure out a way to make it fun?  
\end{itemize}  
\item Grow interpersonally  
\begin{itemize}  
\item Find an event and attend it  
\item Spend time with people.\footnote{I'm not putting any further details here, because I um don't want to incriminate myself further/make it something problematic (not that I have any ill intentions, just writing something semi publicly makes anything seem more nefarious}  
\item Find a place to volunteer and start doing so regularly  
\end{itemize}  
\item Publish the paper  
\begin{itemize}  
\item Spend X minutes a day working on writing the paper  
\item Come up with a detailed hit list of what the paper needs and go through each item one by one  
\item Set up a meeting to discuss  
\end{itemize}  
\item Finish my web serial  
\begin{itemize}  
\item Spend time plotting it out  
\item Start writing it again  
\item Start publishing it again  
\end{itemize}  
\item Make exercise a routine  
\begin{itemize}  
\item Find a way to make myself accountable  
\item Find an exercise I enjoy and make it easier to do  
\item Find a way to reduce willpower needed to exercise  
\item Exercise daily  
\end{itemize}  
\item Letter Writing as routine  
\begin{itemize}  
\item Compile a list of people I want to write letters to and their addresses  
\item Come up with a schedule for writing letters  
\item Figure out a good template for writing letters that isn't emotionally draining but is also something someone would enjoy?  
\end{itemize}  
\item Comfort with myself  
\begin{itemize}  
\item Daily affirmations  
\item Compile list of ways that I'm dissatisfied with myself  
\item Work through that list, either coming to terms with or changing about myself  
\item Spend time each day focusing on growth  
\end{itemize}  
\item Food routine  
\begin{itemize}  
\item Musing about macro/micro  
\item Compile list of X meals I can make and their accompanying information  
\item Figure out what foods I can buy to have to eat  
\item Make a meal plan  
\end{itemize}  
\item Finish embroidery  
\begin{itemize}  
\item Spend X time working on it per X  
\item Invite friends to craft time  
\end{itemize}  
\item Read Library Books  
\begin{itemize}  
\item Spend X time a day reading books  
\item Come up with an ordered list for what I'll read  
\item Figure out my motivation for each book and have it as the bookmark  
\item Read X books a Y period.  
\end{itemize}  
\item Sunday Musings about Gospel  
\begin{itemize}  
\item Muse on Sundays about the Gospel  
\item Read readings on Saturday  
\item make a template that I can fill in  
\item Tell myself it doesn't have to be good  
\item Block out time in my schedule  
\end{itemize}  
\item Clean life.  
\begin{itemize}  
\item X time cleaning each day  
\item List of things that need to be cleaned and the frequency  
\item Schedule  
\item Throw things away/remove from my life somehow  
\item Make a list of everything I own  
\end{itemize}  
\item Learn to draw\footnote{I know this one is new even here, but it is something I've always wanted to be able to do, and it's something that I can absolutely do systematically}  
\begin{itemize}  
\item Figure out what I want to learn to draw right now (e.g. figures, nature, something abstract)  
\item Spend X time working on fundamentals  
\item Spend X hours total working on a single piece  
\item Spend X time reading/watching content on how to learn the skills  
\end{itemize}  
\end{itemize}

Huh wow, that was far easier than I expected.  


Given how many of these seem to be schedule based, scheduling my life is clearly a must.  
Since none of these are things that absolutely have to be done before the end of the year, I think that it might be best to focus on the bigger picture ones, like compiling lists.  
With that in mind, my goals for year end are:

\begin{itemize}  
\item Define how I'm feeling each day at start and end  
\item Talk to boss about Ph.D. timeline  
\item Pick a topic for a science communication article  
\item Read a pop sci article a week, making notes about how they work  
\item Spend 30 minutes 2x a week working on writing the song  
\item Practice guitar daily (at least one scale and a chord progression)  
\item Find an occasion I could write a song for  
\item On Sundays, write a hymn harmonization for one of the hymns we sang  
\item Muse daily  
\item Make a list of musings to do  
\item Stretch Twice a day  
\item Make a list of the stretches I'll do each day  
\item Find a place to volunteer  
\item Paper hit list  
\item Read the comments on the serial  
\item Walk to the gym every day  
\item Compile a list of people I want to write letters to  
\item Do daily affirmations  
\item Muse about macros and micros  
\item Compile a list of 20 meals that I can make, with their ingredients (inc. shelf stable or lifetime), time, effort level, and nutrition info  
\item Come up with an ordered list for what I'll read  
\item Figure out my motivation for each book and have it as the bookmark  
item Muse on Sundays about the Gospel  
\item Read readings on Saturday  
\item Block out time on Sundays for gospel reflection  
\item List of things that need to be cleaned and the frequency  
\item List of things in my life  
\item Decide on what I want to draw right now  
\item Ten minutes 4x a week on drawing  
\end{itemize}

Well, that's honestly not the worst list I've ever made.  
I do love how many of them are list based, if I'm being totally honest.  
For now, however, I'm going to step away, if only because I don't want to burn out too early.  


\end{document}