\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflections-on-readings-31-ordinary-b.html}{Reflections on Today's Gospel}}
First Published: 2018 November 4

Deuteronomy 6:5 \say{Therefore, you shall love the LORD, your God, with all your heart, and with all your soul, and with all your strength.}

\section{Draft 1}
The Gospel today spoke to me for the same reason that it speaks to many people.
It's an incredibly simple command that Jesus lays out.
Instead of having hundreds and hundreds of rules and laws, there are only two.\footnote{or one depending on your interpretation}

You are to love the Lord with all your heart, soul, and strength.
And you are to love your neighbor as yourself.
Wow that sounds nice and easy to understand and completely impossible to follow.

What does loving the Lord with all your heart, soul, and strength mean?
How do we love Him?

And when we start asking those questions, we realize why there are so many rules and laws in both the Jewish faith,\footnote{where the sayings came from} and also in the Catholic faith.\footnote{the one I'm familiar with}
It's the same reason that we can't just say \say{I'll write a novel,} and instead need to break it into smaller steps.
People aren't good at big picture projects.
Dedicating our lives to a cause is the biggest picture any of us can do, but without frameworks to help us, we either find ourselves paralyzed with indecision,\footnote{as many aspiring authors are} or led down dark paths, forged with the best of intentions.
Of course, there is the slight chance that we do brighten the world, and make it a better place.

But, to steal an analogy given to me, the Church provides an interstate.
It guarantees that if you don't ever get off the interstate, you'll go to heaven.

There's nothing stopping you from driving down the country roads and side streets, and you'll likely see more exciting vistas than if you stay on the interstate.
But, you always run the risk of your car breaking down before you get to where you're going.
\end{document}