\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflections-on-readings-2-advent-a-22.html}{Reflections on Today's Gospel}}
First Published: 2022 December 18

Matthew 1:24 \say{When Joseph awoke, he did as the angel of the Lord had commanded him and took his wife into his home.}

\section{Draft 1}
The Gospel today focuses on the earthly father of our savior, St. Joseph.
Lately I've been reading and hearing a lot of modern opinions on him, and many of them make me uncomfortable.

In part, this is because we know so little about him.
As is often joked, if St. Joseph is the ideal husband, then the ideal husband never speaks.
This references the fact that Joseph has no dialogue attributed to him in the Bible or Tradition.

More than that, though, we know nearly nothing about the man who raised the Lord through his childhood.
We know he was a carpenter, and not a particularly well-off one\footnote{Luke 2:24, they offer turtle doves which is (apparently) what you offer when you cannot offer more}.
We know that he did not have sexual relations with Mary.
We know that he died before Christ was crucified.
We know that he radically and totally trusted in the Lord to guide him.
And yet, people will put much more on him.

In part, I think this is because we want to be able to connect with the holy men and women who came before us.
That's a great and noble goal.

In part, I see a lot of it as coming as a response to what's seen as the emasculation of modern society.
That's not great, in my eyes at least.

And, in part I think that we don't like to have unanswered questions.
That's natural.

I don't know where I'm going with this reflection, other than to say that to model St. Joseph really means that when we hear a call from the Lord, we uproot our lives and do as He commands.
\end{document}