\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}  
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{reflection-april-25.html}{Monthly Reflection}}  
First Published: 2025 May 1

\section{Draft 1}

Oh boy what a whirlwind of a month!

Five things I was looking forward to last month:  
\begin{itemize}   
\item Leading the science experiment this coming Saturday.

Went much better than expected! I had a great time and learned a bunch and it seemed like a bunch of kids did as well.\footnote{and a shocking number of parents. Shocking only in that I didn't expect them to be as into the process as they were}

\item Going to a friend's thesis defense

Went! They did a great job and are now a Dr.  
\item Finishing and submitting my first first author paper

So, some goals may have been more optimistic than others.  
I do now have the explicit \say{stop working on optimization} order, which is fine and good I guess, but wow I just feel like there's a single thing missing from the code to make it perfect.

\item Writing more with a close friend

We wrote so much together!  
It's been really great, and I'm hopeful that we can continue it into the next month.

\item Becoming more of the person that I would like to be, both by changing and by changing my goals.

I don't really know how much I've changed as a person, but I do think that I've been setting better goals and living in better alignment to those goals, which is I guess all that it means to become the person I would like to be.  
Hmm.  
\end{itemize}

Last month I had some overarching goals.  
Let's see how we did with those:

\begin{itemize}

\item Prayer.

Praying in the way that I've always done growing up\footnote{read: generally structured and with an explicit formula} remains really difficult.  
I don't want to become someone who just says \say{yeah I feel connected to the Creator when I'm in nature}, but I do think that right now I best become prayerful as I take rest.\footnote{shocking}

\item Physical Health.

I particularly meant exercise when I started last month, and I certainly have exercised more than I did in the past.  
According to my tracking, I stretched 21 times last month for more than five minutes at a time.  
That's not nothing, but it is also far from the thrice daily I had generally hoped for.  
Still, anything is better than nothing, and I do absolutely note that I feel markedly better on days when I've had a routine of stretching.

I also realized or remembered or refocused on the fact that I need to feed myself.  
It has remained somewhat difficult, but I continue to improve at it in some marginal sense.

\item Avoiding Obsession.

I don't really know that I did a fantastic job here, but I did do my best to try to structure myself so that I don't have the chance to obsess and/or set cycles to help break obsession when it comes.

\item Intentionality.

I continue to struggle with the idea of scheduling.  
Part of me thinks that it's due to the fundamentally flexible nature of most of my day contrasting with my need for rigid timings.  
That is, arriving at the office between 720 and 740 doesn't really make a difference, but if my task is then \say{write for twenty minutes}, then the whole schedule for the day gets thrown off.  
Also, I don't really know how long things take.

Part of that is my generic time blindness, part is not knowing how productive the me of tomorrow will be\footnote{something something motivation levels}, part is not knowing what distractions will occur\footnote{read: I exist in a community and that means that there exist obligations to others that I must fulfill}, and part is just that I don't know how long a task would take independent of that.  
Revising a paper can take anywhere from a few minutes to days of concentrated\footnote{one might say obsessive, if they wished} effort, and I don't know if there's a way for me to know which it will be a priori.

However, I do think that I am generally doing better at a macro sense of spending time the way that I want to.  
Obviously I cannot and will not ever be a perfect time user, only spending time on those activities which absolutely serve the me of the future in the most optimal way.  
That's not just pessimism, it's reality and also knowledge that I do not have perfect future knowledge.  
What I do now may or may not benefit the me of tomorrow.  
A random walk down the street instead of working for ten minutes might introduce me to the love of my life.

\item Working on hobbies.

Well, that's not been great.  
Before Easter, I went on a seven churches walk with a group.  
Someone asked me what hobbies I have, and I realized that the answer had really been \say{research that is not what I'm supposed to be doing}.  
I did read 13 books last month, though\footnote{give or take the off by a few days tracking error of when I started or finished a book}

Oh right, a lot of those are books I never had clicked finished on when I did.  
Ignoring those, we're at seven, including three audiobooks I mostly listened to because I hate DNFing on something low effort.  
One of the four actual books I started in February or March.  
So, I did, in fact, read less last month.\footnote{good to know I'm not crazy for thinking so}

I kept wanting to do guitar more, and the past few days have felt some inspiration.

I did blog a lot, which is a hobby of a sort.  
That's something I did far more reliably than in most prior months.

Stretching is also arguably a hobby, and it's absolutely something that I did more of.

Ok so maybe I didn't do that bad at hobbies, after all.

I did also have a weekend spent gaming, which is a thing I chose to do!

OH!   
I've also been getting into pens a fair amount this past month.

Wow ok, so I have done a lot of hobby related activities.  
They're just not the hobbies I historically pursued.

\end{itemize}

I kept a living document of daily reflection goals, which I've now sort of stopped.  
While it was helpful for me then, it was also twenty minutes out of each day that I spent filling it out.  
Time passes regardless of how I spend it, but I have to wonder whether it's a good use of my time.\footnote{oh, actually, typing that here makes me realize that it absolutely is.  
On the days where I didn't do it, I got overwhelmed with stress.  
That's good to know. Let's move to it after this}  
I'm going to restart it, but I don't really necessarily know where my goals might be.  
That's not true, but I do suddenly have a much shorter timeline than I thought for my degree, which makes me kind of feel anxious about what all I will need to do.  
Still, I cannot write if I do not exist, and so let's structure the goals from that basis.

When I \href{what-we-dont-write}{reflected}\footnote{I should really make a new post called what we don't post and then have different notes for each folly I've written and then not made public} on my goals for this phase of my life\footnote{read: until the end of summer, which is (not coincidentally) the end of my doctoral time}, I did come up with a tiered list of priorities.  
Structuring the reflection like that might not be the worst idea.\footnote{took a break here in order to run through the rest of the ink within and then clean pens (see: I do hobbies) to set up for the next ink that I'm trying}

Before making my list of daily reflections, let's think about five things I'm excited for, five SMART\footnote{specific, measureable, achievable, relevant, time-bound} goals, and five general themes I want to shoot for.\footnote{that is, five things that are absolutely not SMART (gotta love acronymizers who make really aggressive things when taking the antonym}  
Also, five great things from last month that I didn't have as listed things last month.

April Highlights  
\begin{itemize}
\item Had a poker night with friends and managed to end at exactly where I started.\footnote{in part because I was up and then started making really risky bets so that I could go home early. Ended up like 2\% ahead (read: 20 cents), so tossed that in as an extra ante} 
\item Went to two\footnote{!} seders, and in general really felt like I connected with my heritage in a way that feels rare to me.\footnote{I feel like I've almost certainly mused before about feeling unmoored from history}  
\item Got new pen supplies and played with them!  
\item Made trifle for the first\footnote{and second} time! It was easy and very well received.  
\item Set tentative thesis defense time and then two weeks later moved that up a semester!\footnote{exciting in the literal sense of excited like an atom, full of energy, not necessarily positive}
\end{itemize}

Five things I have to look forward to in May:  
\begin{itemize}  
\item Today I TA for the last time, I think ever.\footnote{as far as I know, it's not TAing when I'm not a graduate student}  
\item I have a one week intensive writing camp for my dissertation, which will be fun.\footnote{note to self, remember to figure out difference between thesis, defense, dissertation, and everything else that people call this finishing of my academic striving}  
\item Giving the opening talk for the set of summer science outreach and communication program that I'm part of. That is, the university partners with state parks to give talks about space over the summer (I know I've talked about this before). I'm giving the first of the year (even though it isn't in a state park, technically).\footnote{it's a wildlife preserve, I think}  
\item Being able to dedicate entire days to a single project, rather than having to always split my attention.\footnote{this is similar to a rephrasing of the first thing}  
\item I'm going on a pilgrimage this weekend! That should be really fun!\footnote{and oop, I really need to pack for that}  
\end{itemize}

Five quantized\footnote{I refuse to use quantifiable. Wait is there a difference between quantized and quantified? Looks like quantized is a science only word right now but. Wow I'm going to be (more) insufferable} goals for the month:  
\begin{itemize}  
\item Finish solid\footnote{meaning well cited, contains all the information I think that it needs, and has the figures which are most pressing} drafts of at least three chapters of my thesis.  
\item Write at least one in depth exploration of some theological topic I've been wrestling with.\footnote{current front runners include: what does abortion mean, how should Catholics treat the government given its fundamentally unjust nature, punishment, the many ways that we need to ignore saints because they spoke on material reality rather than faith and morals and are therefore explicitly wrong (ok so this is also about punishment), and what it means for me to be Jewish and Catholic}  
\item Do more than 50 greater than 5 minute stretching periods. Right now I have a computer alarm set for the last five minutes of every work hour reminding me to do so, so that should help.  
\item Write and post at least 20 follies, including this one.  
\item Apply to five jobs.  
\end{itemize}

Five amorphous ideals for the month, like last month's \say{areas I want to focus}\footnote{why am I using a different term? great question}:  
\begin{itemize}  
\item Prayer and mindfulness. Figure out what difference, if any, there is between them to me and work to do both more.  
\item I've started tracking my things to do and whatnot\footnote{love that this is one word, curious what its origins are, guess it gets a note} with sticky notes\footnote{is post it a trademarked term still? probably}. Either continue with that, or figure out a better way to track my time and, importantly, track myself and keep myself accountable and productive. I guess this is kind of two, since productivity and organization are not inherently linked, but they sure feel like they are to me.  
\item Self care. Make sure that I am eating, sleeping, moving, drinking water, and the other things which I need to be the healthiest version of myself. This relates a lot to the top goal, but I guess here I'm saying physical self care rather than spiritual and mental.  
\item Reading. I want to get through more of the backlog. Yesterday I went to a bar and read the last few chapters of the science book I'd been working through. In general set aside more blocks of time to simply disconnect, sit, and read a book. This will help inspire me, give the creative part of myself a rest, and help me to be better at knowing what all is known and thought.  
\item Romance. Make efforts towards finding a life partner and generally try to be more open to more forms of love, not just the friendships I have and deeply treasure.\footnote{and, of course, work on the friendships}  
\end{itemize}

Looks great!

In making my list of general priorities, family was at the top, but it's not an ideal here.  
Why?  
I generally feel like the way I am with my family is relatively good, and so it does not need to be an area of specific focus like these other five, where I feel that I am very lacking.

So: let's revise our daily reflection template with my ordered tiers of goals in mind.  
Within each numbered entry, bulleted points are nominally of about the same importance, or at least feel flexible enough that I cannot always put one above another.

\section{Daily Reflection}

\begin{enumerate}

\item Top Priorities:

\begin{itemize}

\item Sleep:

\begin{itemize}

\item Keeping sleep time sacred?

Not at all last night, was on my computer until nearly 2300.  
Still, after that I did avoid using phone until this morning.

\item Good sleep hygiene?

Nope! As mentioned, on computer from 1900 until 2300, all in bed.  
That's really bad.

\item Sleeping enough?

Eh, 8 hours is nominally enough.  
I tend to like having the option for up to 10, but that's maybe not needed.  
I've been waking up with my alarm every morning lately, which is a sign that I maybe should be getting a little more.

\item How well rested do I feel?

Hard question to answer, because often sleep inertia, once overcome, really forgettable.  
I also have a lot of coffee\footnote{back to the 10 oz of espresso a day life}  
Then again, very little sleep inertia today, and I have generally been doing well at keeping energy through the day!

\end{itemize}

\item Feed myself:

\begin{itemize}

\item Did I eat breakfast?

Woo!

\item Did I eat a second meal?\footnote{I don't know why the term lunch bothers me, but I think part of it is that I often have started eating something over the course of an hour or five, and it feels wrong to call a six hour meal lunch}

Nor entirely sure, but had a pastry which I'll call breakfast and am actively working through a bowl of oats.  
Also packed a lunch, so we'll see how that is.

\item Did I eat dinner?

Yesterday I did!

\item Water?

Drinking it right now. Want to empty the water bottle today, which shouldn't be too hard, since I'm trapped in the bowels of the chemistry department.\footnote{it is burning hot down here. Apparently there was a heater stuck to on until the other day down here}

\end{itemize}

\item Family:

\begin{itemize}

\item Am I neglecting any familial obligations?

We're doing a weekly asynchronous album walk, which I have yet to do.  
Since I'm going on a 21 mile walk this weekend, I imagine that I will have time for listening during it.

\end{itemize}

\item Movement:

\begin{itemize}

\item Am I stretching at least 5 minutes per hour of computer time?

So far today! I have stretched for each of the three hours I've been at work.  
Why five minutes, one might ask.  
The shortest period of time that my watch counts as a full workout is 5 minutes, so that's the goal!

\item Am I generally making efforts to be limber?

Eh sort of.

\end{itemize}

\item Spirituality:

\begin{itemize}

\item Time for prayer?

None today so far.  
Will try to have some tonight.

\item Prayer?

\item Time for sacred\footnote{there we go, a distinction between absence of sound and the actual goal of silence} silence?

Nope!

\item Deep breaths?

Three just now.  
Will try to remember doing that over stretching time.

\end{itemize}

\end{itemize}

\item Secondary Priorities:

\begin{itemize}

\item Thesis/ Ph.D. work:

\begin{itemize}

\item Keeping up on the writing deadlines?

I have four chapters as a rough draft due tomorrow along with a good draft of a paper.  
Draft of paper is basically done, but the chapters are not.

\item Reading the necessary things?

N/A today.

\item Making graphs?

I think that right now better to focus time on writing words not making graphs.

\item Organizing citations?

I trawled through my downloads folder yesterday and loaded pdfs into Zotero.  
Do need to organize them, though.

\end{itemize}

\item Love:

\begin{itemize}

\item Taking risks?

Nope!

\item Making efforts?

Nope!

\item Showing affection?

No more than usual. Should message a friend.

\item Being honest?

I think so! Very little of people asking how I'm doing, so very little by way of opportunity to do so.

\item Being open?

I think so! I'm trying to vocalize what I want and need, and in general am getting what I need.\footnote{though tragically, not the mug I so desperately crave}

\item Being appropriately vulnerable?

I think so! Again, few chances for it, and so few places that I show it.

\end{itemize}

\end{itemize}

\item Adjacent to Primary and Secondary:\footnote{read: things that will help me with the above goals but not goals in and of themselves}

\begin{itemize}

\item Typing Practice?

Haven't done this for more than a few days. Will spend the next ten minutes on that, once I finish this reflection and before I get into the meat of the day.

\item Post-its being maintained?

So far! It is only really day two, though, so that's not saying much.

\item Applying to jobs?

I set up profiles yesterday, which is a whole thing.

\item Reading the things I think could be good?

I finished a book yesterday!  
I brought two more with me to work, and will hope to work on them.

\item Making manim videos?

Nope!

\end{itemize}

\item Cleaning?\footnote{yes this one gets its own tab because I think that it's more important that the below but less than the above}

\begin{itemize}

\item Office

Trying to keep it ordered.

\item Home

\item Car

\item Computer

Started cleaning my downloads folder yesterday.

\item Other as needed

\end{itemize}

\item External Obligations:

\begin{itemize}

\item Guitar for wedding?

Have a lick that I want to try basing the piece around.  
It came to me at 2 in the morning as I lay in bed, which is always fun.

\item Travel plans?

\item Talks for parks?

\item Other requested talks?

\item Talks for conferences?

\end{itemize}

\item Tertiary Goals:\footnote{mmmm off by N numbering}

\begin{itemize}

\item Blogging?

Look at this!

\item Reading?

Read some of a low mental effort book while walking from work yesterday.

\item Web Noveling?

I'm going to do this after I get through the draft of the paper I'm working through.

\item Guitar?

The piece for the wedding is so far based a lot around tenths, and I'm pretty sure the guitar book I'm nominally working through has exercises for that.  
Only one way to find out!\footnote{love that sonic song}

\item Other hobbies?

Tried a new ink yesterday and today!

Yesterday was Private Reserve Tanzanite.  
It's a bluer purple than I'm used to really seeing.  
Looks really nice, especially as a formal ink.  
I don't know how much formal hand writing I need to do, though.

It's a very low shade,\footnote{consistent color as writing, regardless of pressure/amount put on page} non-sheen\footnote{doesn't have different hues as light hits differently} ink which is probably why it feels formal.

Today is Diamine Spruce.  
It's a nice deep green.  
Really saturated which I like, and decent amount of shading, going down almost to black at high saturation areas.  
At the lighter ends, seems nearish to Hex 006B34, though I can't seem to figure out its exact coloring.  
No shimmer or sheen though.

\end{itemize}

\item Quaternary Goals:

\begin{itemize}

\item Letter writing

\item Handwriting/penmanship

Practiced loops and lines with both hands!

\item Picking a new signature

Signed a check and so had a chance to test out an idea

\end{itemize}

\end{enumerate}

\end{document}