\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-may-23.html}{Monthly Reflection}}
First Published: 2023 June 1

\section{Draft 1}
Oh wow, it's been over two weeks since my last post.
I have no clue where the days go.
I did write around 36000 words last month, so that's somewhat exciting, even if almost none of them were for this blog.

My goals \href{reflection-april-23.html}{last month} broke into a few categories.
If I had checked up on them, I'm sure that it would have been useful to have them in that order.
Instead, I just forgot that they existed until I began writing this post.

Rather than list the list again, I'll just go through how I did on them.

\begin{enumerate}
\item Professional:
\begin{itemize}
\item I did not manage to get running on my instrument this past month, which I at least now know why.\footnote{the short version is that the box I was given to output high voltage gives it negative not positive. The long version is that plus a bunch of other corrections.}
\item Probably because of the above item's issues, I did not finish building the other instrument.
\item I did finish TAing and I even got mostly positive reviews!
\item I prepared for a talk at a state wildlife area, which is apparently distinct from a state park. It went really well, and I had 53 people come! I should absolutely blog about that, so expect a post soon.
\end{itemize}
\item Personal:
\begin{itemize}
\item I deep cleaned my home to at least my own standards.
\item I finished the book I didn't enjoy and managed to at least stay on the writing schedule I needed for the one I am enjoying. I kept hoping to pull ahead but haven't managed it yet.
\item I am now I think good enough at bagpipes to where I won't embarrass myself next week. There are a shocking number of interactions I have had related to playing the pipes these past weeks, which also deserve a posting of their own.
\item I don't think that I played particularly more music, but I don't know if I dislike that too much.
\item I spent some time working on a song but not enough to break the wall of writer's block. I should really just get back into writing poetry.\footnote{well known as the gateway to songwriting}
\end{itemize}
\item Growth:
\begin{itemize}
\item I have off and on been able to make more time for prayer.
\item I wrote none letters, though I did see friends in person!
\item Oof, I did not blog daily. I blogged half as much last month as in April.
\item I ran I think zero times.
\item I mostly stopped working out. 
\item I actually did manage to go to bed generally early! My default wake time has shifted to be nearly six am now which is nice.
\end{itemize}
\end{enumerate}

Looking forward at this month, I would like to:
\begin{enumerate}
\item Accomplishments/Finite Tasks\footnote{i.e. things that I will have done by the end of the month.}
\begin{itemize}
\item Play bagpipes at a friend's wedding
\item Write and give a talk at a conference
\item Get my instrument running
\end{itemize}
\item Growth
\begin{itemize}
\item Invite friends over to my home at least once.\footnote{I'm not ashamed of it anymore which is nice}
\item Blog!\footnote{ideas from above/that I need to discuss in general are: my talk, piping interactions, book reviews of the books I've read recently, do versus have done}
\item Start exercising at least three times a week
\item Push myself to actually sleep enough and still get up at six.
\item Make time for prayer
\item Get five chapters ahead on the book I'm writing
\item Write a song
\item Write at least three letters to friends
\end{itemize}
\end{enumerate}

This might be a better way to frame my goals.
In general, there are things that I want to have accomplished, and things I want to do.\footnote{oh, shoot, that's actually something I should blog about. I had a whole idea going about the difference between things I want to do, things I do, and things I want to have done. adding to list}
Hopefully I'll be able to keep up with this more!
\end{document}