\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflections-on-readings-14-ordinary-c-22.html}{Reflections on Today's Gospel}}
First Published: 2022 July 3

Luke 10:20 \say{Nevertheless, do not rejoice because the spirits are subject to you, but rejoice because your names are written in heaven.}

\section{Draft 1}
Today is the 14th Sunday of Ordinary Time.
Since I stopped these reflections in the Easter season, it's kind of strange not having a season I can orient my reflections on.

The last line of the Gospel today is really striking to me.
Christ commands his followers to go to the neighboring towns to share the good news.\footnote{Good News?}
They return rejoicing, because they have power over demons now.
Christ reorients their joy.

Rather than focusing on the temporal benefits of faith, He reminds us that everything is good only in how it leads us to Heaven.
That's something I need to remind myself more about.
A rich prayer life is only worth celebrating in how it orients my will to the Lord's.
Struggles are only damaging in how they damage my trust in Him.

I'm sure there's a deeper level to today's readings, but this is all that I have right now.
\end{document}