\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflection-october-2022.html}{Monthly Reflection}}
First Published: 2022 November 1

\section{Draft 1}
Another month, another monthly reflection.

My goals were:\footnote{with commentary this time because I'm too lazy to fix it.}
\begin{enumerate}
\item Blog daily. Eventually this goal will happen.
\item Stretch daily. I'm going to stretch right after this, just so I make sure to do it.
\item Figure out how to repair/improve my accordion case. I made some notes today, and I think I should be able to get some of it done by the end of the month.
\item Write a poem every day. I did feel like the poems I wrote helped me ease into sleep, and they certainly help me write songs better.
\item Finish the newest song I'm working on. 
\item Make progress on catching up for BiaY.
\item Fill in at least 3 more items on my 24 for 24.
\end{enumerate}

How'd we do?
\begin{enumerate}
\item 17/31 blogs. That's more than half, so improvement.
\item I had about a week where I stretched, so that didn't go horribly.
\item Turns out repair was as simple as taping it back together, so I gave up on that project.
\item I wrote a couple of poems, rough estimate of 12, so could do better.
\item I not only finished it, I've performed it!
\item Lots of progress, I'm now at day 232.
\item I added two new points, so I'm on schedule if not my goal
\end{enumerate}

In the next month I'm going to try:
\begin{enumerate}
\item Blog every day. I believe in this month.
\item Stretch every day.
\item Write a poem every day. I'm doing a poem a day with some friends, so I'm accountable there.
\item Finish NaNoWriMo successfully
\item Make progress towards catching up on BiaY
\item At least two entries in 24$^2$.
\end{enumerate}
Let's see how we do!

Outside of my goals, I had a pretty good month.
I'm making new friends and deepening existing relationships, which is always nice.
\end{document}