\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{reflections-on-readings-7-ordinary-c-22.html}{Reflections on Today's Gospel}}
First Published: 2022 February 20

1 Samuel 26:23 \say{The LORD repays everyone's righteousness and faithfulness. Although the LORD delivered you into my hands today, I could not lay a hand on the LORD's anointed.}

\section{Draft 1}
I find today's readings beautiful, if hard to connect.
The first reading speaks to me about the need to do the right thing even when it is not the easiest option.
David could easily have slain Saul, and therefore saved himself a lot of trouble.
Instead, he did not.

In the Gospel, we are reminded that doing good in return to good or in expectation of good is not virtuous.
That feels somewhat self-evident, but is still hard for me to remember.
I am reminded of the reading from earlier in the week, where in the Letter of James we are reminded that even demons have fear of the Lord.
As easy as it is for me to intellectually know I need to forgive those who wrong me, I still struggle to do so.
That's something I can work on in the future.
\end{document}