\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{restarting.html}{Restarting}}
First Published: 2022 January 1
\section{Draft 2}
I just finished a read through\footnote{read-through?} of the blog on here.
It's really interesting to see a glimpse into my life three-ish years ago.
I noticed a couple of major things.
First, it's really fun to me that I've basically just caught back up to the point in the liturgical season we're at because readings loop every three years.
Second, seeing my public\footnote{ish} comments on different portions of my life let me remember some of the parts of my days I didn't write which is fantastic.

Since my \href{ending-18.html}{last} end of/beginning of year post had five things I was most grateful for and the same number things I was looking forward to, in 2021\footnote{wow it's weird that it's 2022} I was most grateful for\footnote{in no particular order}:
\begin{enumerate}
\item Meeting fantastic people, including a special person in my life
\item \href{/scores/Ave\%20Maris\%20Stella\%20Arti.pdf}{Composing} again (for the first time since graduating)
\item Really learning about my research\footnote{I joined my research group in November of 2020, but had minimal idea what my research would look like before January}
\item Got vaccinated!
\item Presented at my first conference as a graduate student!
\end{enumerate}
Five things that I'm looking forward to\footnote{hopefully happening} in 2022 are\footnote{again, in no particular order}:
\begin{enumerate}
\item Passing my Thesis Background Exam
\item Growing deeper in my relationships
\item Continuing this blog again\footnote{the older I get the more I feel like 'blog might be the correct spelling}
\item Taking a class on the interstellar medium\footnote{expect posts a la \href{polymer-1.html}{this}}
\item Growing more independent in my research
\end{enumerate}
Going into 2019, I never could have predicted what fantastic things would happen,\footnote{getting the opportunity to do research that fascinated me, and so much more that is flying out of my mind right now} though all five of the events I was hoping for\footnote{other than debatably the \say{learning the accordion} item} happened and were wonderful, so I can only assume the same will be true in 2022.

Anyways, since this blog more or less exists nowhere visible anymore, this may be functionally a virtual diary.
I'm excited for it nonetheless.

Posts I'm planning\footnote{for my own reference} include:
\begin{itemize}
\item Talking about writing villanelles
\item Writing about good books I have read/am reading
\item Studying for the Patent Bar\footnote{also probably an explanation of why I'd study for that}
\end{itemize}

Anyways, happy 2022!
\section{Draft 1}
It's been a little under three years since the last time I wrote on here.
It seems like it might be a good time to restart for a variety of reasons, which may be elaborated on further.
This post is very short because my goal is relearning how to update my blog
\end{document}