\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{restarting-again-again-again-again.html}{Restarting (Again (again again again))}}
First Published: 2024 June 25


\section{Draft 1}
At some point I should really stop just appending a new again to the end of the title.
Of course, at some point I should really either stop giving up on the blog or give up on it forever.\footnote{hmm actually no I do really think that there're points in my lives wherein the blog is better or worse for me. That being said, I do generally feel like the majority of points in my life are at least not worsened by the presence of a daily blog post, and it does help me to remain more reflective}
That being said, neither of those are happening now.

I've started to get the familiar summer itch\footnote{ok so scrolling through the calendar of my posts, it doesn't really seem like there's a rhythm or rhyme based on the pseudo solar calendar we all know and love} to restart the blog, and so here we are.
Very few updates since last time, though of course, if you're interested, they're mostly available on my \href{twenty-five.html}{yearly goal tracker}.
In general, I think that I've been doing fairly well, which is nice to be able to say.

Anyways, I've now basically given up on the post for the day, so I'm going to post this. Hopefully tomorrow I'll be up to the rest of the reflecting I should do.

\end{document}