\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{restarting-again.html}{Restarting (Again)}}
First Published: 2022 April 7


\section{Draft 1}
It's been about 3 weeks since my last post, when I said I was going to take a break.
I don't regret the break, because I still believe what I wrote then, that \say{for whatever reason, writing this blog isn't really making my heart sing like it used to.}\footnote{\href{taking-a-break.html}{from here}}
I claimed that I'd keep up with weekly reflections and my readings of books, and I technically did the latter, though only because I haven't been doing any of that reading.

As I look back on the past few weeks and months, I realize that I had been doing fewer and fewer \href{creative-hobbies.html}{creative} hobbies.
I wrote in January about how creating is important, and I don't think I realized quite how true that was.
I said in that posting that I felt that physical hobbies were better, and I am now moreso sure that's true for me.
Without something disconnected from my computer, I find that I grow ungrounded and disconnected from my time.
Days flow by without any real differentiation, and I don't like that.

Now, this isn't to say that I don't think my digitally creative hobbies are worth pursuing.\footnote{as demonstrated by the writing of this post}
I am planning to restart my book and this blog, but I also need to make sure that I am making music on my own, crocheting, and writing poetry.
I know that I need a reason to keep writing, and for now I'm going to hope that the reason can be keeping a record of thoughts for my future self.
\end{document}