\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}   
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{review-musicking.html}{Review of Christopher Small's Musicking}}  
First Published: 

\section{Draft 2: 17 September 2025}
Before I start this review, I just have to say that it is wild to me how much books from the late nineteen hundreds feel both like they just happened and happened centuries ago.
Small, for instance, 

\section{Draft 1: 16 September 2025}
Ok so technically I haven't finished \textit{Musicking} yet, but I'm optimistic.
I do find it interesting that Small frames the entire book through the lens of an orchestral concert.
I was assigned an article about it back when I was doing an independent study on listening to music.
It was absolutely one of the most influential writings that I've ever encountered, if only for how it makes me think of music.

Small's key argument is that music is not a thing but an action.
When we music, we are listeners or performers or dancers or stage hands.

I love this take because it helps me to deal with that most fundamental urge of the scientist in me: labeling what is and isn't music and who is and isn't a musician.
Music is what we make of it, and musicians are those that make it.

I enjoyed greatly the aside on Cartesian dualism and especially the way that Small makes a point that so much of the industrialization we live and think under is like the water a fish has no name for.
I hadn't considered the mind matter dualism really at all, especially in the context of music.



\section{Daily Reflection: 16 September 2025}

\begin{itemize}

\item Did you journal by hand today?

\item Did you do a folly?

\item Did you in some way, shape, or form advance the web novel?

\item Did you work on music, whether education or creation?

\item Did you work on book binding?

\item Did you work on another hobby?

\item Did you stretch? Really?

\item Prayer?

\item Meditation?

\item Reading?

\item Minimizing screen time?

\end{itemize}

Current Pen List\footnote{for my own posterity, mostly}

\begin{itemize}  
\item Hongdian Black with Fude Nib: Diplomat Caribbean (8/30ish)  
\item Jinhao Shark: Diplomat Caribbean (8/30ish)  
\item Pilot Preppy: Private Reserve Electric DC Blue I think (I think since late june. I think)  
\item Sheaffer: Private Reserve Spearmint (since 7/15) (I Think)
\end{itemize}

\end{document}