\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{hyperref}
\begin{document}
\doublespacing

\section{\href{riverwalk.html}{Riverwalk}}
\section{Draft 2}
Today, I went on a riverwalk.
Nominally, it was to fulfill an academic assignment.
Since the assignment was vague,\footnote{take a walking journey of between 45 and 90 minutes between two historic locations} I chose to journey between the London Aquatics Centre\footnote{the site of the 2012 Summer Olympics and Paralympics Swimming and Diving Events} and the River Thames.\footnote{\href{https://en.wikipedia.org/wiki/River_Thames}{allegedly }the largest river contained entirely in England}
I found that
\footnote{assuming you don't make mistakes (which I did) and are ok trespassing(only for a short distance to avoid crossing an overpass)(which I was not)} you can walk the entire distance from the Aquatic Centre to the Thames entirely along different rivers and streams.\footnote{and even one lock!}
I had a great time during the walk!
A part of me really wanted to go all the way to the English Chanel, but I knew that was a poor choice.
For one, it would have been far longer than a 90 minute walk.
Second, it's really hard to decide where a tributary ends and where the real river\footnote{apparently the correct term is actually \href{https://en.wikipedia.org/wiki/Main_stem}{\say{main stem}}} ends.
Finally, the footpath that would have let me walk along the Thames was closed.
Nonetheless, it was a great time.
If you want to see my journey at 60x speed,\footnote{20 fps and 3 seconds between shots} you can find it \href{https://vimeo.com/288755224}{here}.
If you want to see it at 15x speed,\footnote{5 fps and above} along with fun information, you can find it \href{https://www.youtube.com/watch?v=z1j-zlVfoHo}{here}.

\section{Draft 1}
Today for a homework assignment, I went on a riverwalk.\footnote{the assignment was to record a journey (by foot) of 45-90 minutes in length}
I chose to go from the London Aquatics Center\footnote{home of the Summer 2012 Olympics and Paralympics} to the River Thames.\footnote{the largest river contained entirely in England}
I found that you can go the entire distance from the Aquatic Centre to the Thames without ever leaving the river.\footnote{if you don't make mistakes and have to backtrack (which I did)}
It was a really fun walk.
It was tempting to walk to where the Thames meets the Chanel, but I was unable to for two reasons: that would have put me well over the maximum time of 90 minutes, and the footpath following the Thames was closed.

\end{document}