\documentclass[12pt]{article}[titlepage]

\newcommand{\say}[1]{``#1''}

\newcommand{\nsay}[1]{`#1'}

\usepackage{endnotes}
\newcommand{\1}{\={a}}

\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}

\newcommand{\4}{\=o}

\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}

\newcommand{\B}{\backslash{}}

\renewcommand{\,}{\textsuperscript{,}}

\usepackage{setspace}

\usepackage{tipa}

\usepackage{hyperref}

\begin{document}

\doublespacing

\section{\href{small-changes.html}{Small Changes}
}
\section{Draft 2}

By now, I'm sure you've noticed that I'm currently studying in London.\footnote{for those of you on the other side of the pond, that's why I haven't been visible}
As a result, much of the typing I'm doing here is being done on keyboards with the UK's key layout.\footnote{I assume, given that it would make sense for each country to have their own keyboard layout.\textbackslash{}sarcasm}

Some of these changes make complete sense to me, like the fact that the pound symbol\footnote{\pounds} is much easier to type.\footnote{fun fact: \LaTeX doesn't recognize typing the pound mark, and instead requires the command of \textbackslash{}pounds}
Unfortunately, it's Shift-3, not Shift-4.\footnote{the \$ in USA keyboards}

Other changes are slightly harder for me to deal with unconsciously.
Next to the single quote key ', they added in a key for pound and tilde.
Instead of shift-single giving you double, it instead returns the @ sign.
Thankfully, shift-2 therefore gives us ".\footnote{so the @ and " signs basically just traded position}
Additionally, backslash is next to the left shift key, and the vertical line\footnote{which I have never once known the purpose of} is shift backslash.\footnote{like in the US}
Where the backslash should\footnote{based on prior experience} be, there is nothing.
Those changes have messed me up more than once when typing a password.\footnote{hmmm does saying I use a shift key in multiple passwords give away some security? Especially since using capital letters is a recommendation, I doubt it.}

I'm also switching to using more Windows machines.\footnote{which is sad}
Commands, especially in the browser I use, are sometimes very different, which is an adjustment.
Overall though, those are the main changes I've really noticed.

The moral of the story is that I apparently don't notice the big differences,\footnote{noise, people, the fact that a road was torn up, pipes underneath were fixed, and the road was operational again within 3 days of them beginning, the weather, the food, everything else I'm forgetting because it's slipped my mind} but I do notice the small ones.\footnote{keyboard layout, computer commands, ending statements in yeah instead of nothing}

Am I missing the forest for the trees?
I prefer to think that I'm missing the branches for the leaves.
I still see that I'm in society,\footnote{the forest} and even the mutually intelligible\footnote{to me, a monolingual Midwestern American} part of the world,\footnote{the trees} but not the differences between here and home,\footnote{the branches} except where they're a little different,\footnote{the leaves} as many are beginning to be in this lovely start of fall.\footnote{autumn}
Also, as much as I wish I could claim this whole article was a set up for that autumn\footnote{fall} metaphor, it was completely unplanned.
\section{Draft 1}
I'm currently studying in London.
As a result, much of the typing I'm doing here is being done on keyboards with the UK's key layout.\footnote{at least I hope that I'm not just surrounded by psychopaths}
Some of these changes make complete sense to me, like the fact that instead of a dollar symbol\footnote{\$} being Shift-number, it's the pound symbol.\footnote{\pounds}\,\footnote{fun fact: \LaTeX doesn't recognize typing the pound mark, and instead requires the command of \textbackslash{}pounds}
Unfortunately, it's Shift-3, not Shift-4.

Others are slightly harder for me to deal with.
Next to the single quote key ', they added in a key for pound and tilde.
Instead of shift-single giving you double, it instead returns the @ sign.
Thankfully, shift-2 therefore gives us ".
Additionally, backslash is next to the left shift key.
That's messed me up more than once when typing a password.\footnote{hmmm does saying I use a shift key in multiple passwords give away some security? Especially since it's a recommendation, I doubt it.}

I'm also switching to using more Windows machines.\footnote{which is sad}
Commands, especially in the browser I use, are sometimes very different, which is an adjustment.
The moral of the story is that I apparently don't notice the big differences,\footnote{the noise, people, the fact that a road was torn up, pipes underneath were fixed, and the road was operational again within 3 days of them beginning, the weather, the food, everything else I'm forgetting because it's slipped my mind} but I do notice the small ones.
Am I missing the forest for the trees?
I like to think I'm missing the branches for the leaves.
I can still see that I'm in society,\footnote{the forest} and even the mutually intelligible\footnote{to me, a monolingual Midwestern American} part of the world,\footnote{the trees} but not the difference between here and home,\footnote{the branches} except where they're a little different.\footnote{the leaves}
Also, as much as I wish I could claim this whole article was a set up for that autumn\footnote{fall} metaphor, it was completely unplanned.
\end{document}