\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{spoons-2.html}{Spoons Continued}}
First Published: 2023 June 14

\section{Draft 1}
About eighteen months ago \href{spoons-and-spell-slots.html}{I wrote a post} about having\footnote{or more accurately, lacking} the energy to do the things that I want and need to do.
Since then, I have been trying to figure out what leads me to feeling better and worse and being more and less productive.
Thankfully, feeling better is generally well correlated for me with being productive.

One trend that I was positive that I had noticed was that I am far more productive when I am well rested.
Yesterday, I was all set to write a whole blog post about how the sleep that I had yet to catch up on was going to make it so I had no way to catch up on my writing.
But, I had other tasks that I needed to do.\footnote{primarily laundry, since I am about to disappear from school for a while.}

So, I set timers and started writing my book during the breaks that I had between timed activities.
I almost effortlessly wrote the entire chapter, which made my planned post obsolete.
Instead, I got to write about the reason I hadn't been posting, which was nice.
While getting a theory disproven is less than the best feeling, it was a nice thing to learn.
Looking back on the times that I am more or less productive, it seems like sleep is important, though not for the reason that I had initially believed.

I still find a correlation with sleep and productivity, though I think that there is an important intermediate step or two.
One thing that forces productivity in me is the lack of ability to do something else.
Of course, I mean that entirely in the subjective sense.
Last night, there was nothing stopping me from sitting and reading a book or watching YouTube.\footnote{which I should decide whether I'm going to treat as a proper noun or not.}
However, the fact that I knew that I needed to write a book and revise a presentation meant that I was able to write.
When I'm more tired, I think that I'm more able to remember that deadlines I set are fake and only affect me.

Another, though fairly well linked issue is that I often lose track of time.
I'll look up from an activity and hours will have passed.
Even tonight is no exception.
I sat down and it was a little after five.
Looking up again, it's now nearly eight.
Where the hours went, I'm not totally sure.
However, I do find that my ability to keep track of time is improved with sleep.

So, between those two issues, I still do see why I am more productive when well rested, for all that I don't know if they're quite as absolute as I thought.
Since this musing is a little shorter than I want, let's talk about the predecessing\footnote{which my dictionary doesn't believe is a word interestingly enough} post about mental space.
I find it interesting that I continually look at scheduling my life as a potential solution.
Intellectually, it very well could be, but I have such an aversion to scheduling myself that I don't know if it will be probable for me without changing something major about my life.

I mused about the time sink that is YouTube\footnote{which I spelled Youtube, annoyingly}.
I believed that I was actively lacking energy more, which I don't know if is true.
I did say that I need to eat more, because I was exhausted.
More and more, I find that I become exhausted feeling when I don't have enough water.
I think that was certainly true of me while writing that post.

All in all, I think it's nice that I can make myself work by lying to myself and saying that I need to.
I wish that there were better ways for me to do so, but I don't know how to find them.

\begin{itemize}
\item I'm going to friends instead
\item I blogged yesterday \textit{AND} today!
\item I walked a fair amount today, which was nice.
\item I slept in the past few days, but I'm hoping to wake up early tomorrow.
\item I'll do a rosary when I finish this post and the chapter for the day
\item I'm debatably on schedule to slightly ahead of where I need to be.\footnote{I've started writing the chapter to post on Friday. If I don't keep writing, though, I will not have a chapter on Friday.}
\item I wrote a dumb song yesterday! It has two verses and a chorus. I'm debating whether it needs more verses, but I also don't want to beat a dead horse in the song.
\item I still have yet to post the letter\footnote{which I think might be a british-slang way to phrase it. I don't know if I've heard my friends say post a letter. I think that the American might be mail a letter? I should look that up at some point}
\end{itemize}

722/101
\end{document}