\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{spoons-3.html}{Spoons Continued}}
First Published: 2023 December 4

\section{Draft 1}
It's been almost six months since I last mused about feeling wrung dry.
Then again, the absence of posts does imply something about the post that would've happened.

\begin{itemize}
\item Hobbies:
\begin{itemize}
\item Did I embroider today? Left it in my car, will try to remember to do tomorrow.
\item Did I play guitar today? I did! Not much, but I picked it up, which is good. I should probably replace the strings soon.
\item Did I practice touch typing today? I got through Y! That means my newest letter is C\footnote{I should really figure out the order that they teach new letters in. A part of me assumes that it's frequency, and that's probably correct}
\end{itemize}
\item Reading
\begin{itemize}
\item Have I made progress on my Currently Reading Shelf? A little! I also started a new book which isn't the point.
\item Did I read the book on craft? Nope! I brought it with me through the day, though.
\item Have I read the library books? I kept it by my bed in hope that I'd read it before sleep.
\end{itemize}
\item Writing
\begin{itemize}
\item Did I write a sonnet? I did! It was kind of about my research, which is nice.
\item Did I revise a sonnet? I really need to learn how to do this.
\item Did I blog? Look at this blog post! Extant
\item Did I write ahead on Jeb? I finished the chapter due today and started the chapter due wednesday, so kind of, at least.
\item Letter to friends? Nope!
\item Paper? Realized I messed up a bunch of calculations, which is kind of sad.
\end{itemize}
\item Wellness
\begin{itemize}
\item How well did I pray? Not well. I fell asleep before starting a rosary last night.
\item Did I clean my space? A little
\item Did I spend my time well? I tried. I focused too hard on research and lost track of time, which probably isn't a bad thing.
\item Did I stretch? No
\item Did I exercise? I did the bare minimum, which I'm counting as enough.
\item Water? I didn't drink enough water, but I tried to. It's hard when I don't fill my water bottles often enough. Things to think about I guess.
\end{itemize}
\end{itemize}\end{document}