\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{st-jude.html}{St. Jude's Relic}}
First Published: 2023 September 14

\section{Draft 1}
Today I had the opportunity to see the relic of St. Jude.\footnote{his arm. I'm not sure which arm, but I think the left.} 
It was a beautiful experience, made more so by the fact that I got to sing at a Mass led by the Bishop.\footnote{who now knows my name! He recognized my face from one of the previous times that he's met me, which is nice.}
Unfortunately, that did mean that it's later now than I'd like it to be, and continuing to blog will take more time than I think that I want to spend.
 
\begin{itemize}
\item No progress on eclipse talks. 
\item The fight was slightly improved, if only because I ran into stuff. 
\item Let's go! Continuing to blog 
\item I stretched this morning. I had planned to stretch again tonight, but it seems a little late for that. 
\item No exercise outside of walking around. 
\item I woke up before seven again, which is nice. I'll also sleep in tomorrow, because I'm still recovering a bit. 
\item I woke before my alarm! 
\item In addition to praying in front of the relic, going to Mass, and spending some time praying after Mass, I also spent fifteen minutes in silent prayer at the chapel on my walk to work. I forgot how much that really makes my entire day better. I left and just felt better. 
\item I finished tomorrow's chapter today! 
\item I don't know if the net progress on plotting question is relevant anymore. 
\item No poetry. 
\item No album work. 
\item After going to the chapel, writing things I like about myself was much easier.
\item Three things I'm excited for was also easier. 
\item Gratitude journaling was as well. 
\item I think that I tried to cultivate joy. 
\end{itemize}

\end{document}