\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{storms.html}{On Storms}}
First Published: 2022 July 5
\section{Draft 1}
I completely forgot about this yesterday,\footnote{or maybe it hadn't happened by posting time} but the sky turned the violent yellow-green of a serious storm.
It was extra shocking to me because I don't remember any serious storm last night.

Today, on the other hand, was like walking through soup.
It was miserably hot and humid all day, and there's been a massive storm on the radar.
As I was sitting, reflecting on my day, flashes of lightning and distant thunder have been slowly building.

I'm still not sure whether it's going to hit here badly, but I hope it doesn't.

Now that I've reflected on the direct storm experience, I'd like to talk more about how I feel about storms.
In general, I really love the rain.
Sure, it's inconvenient to be caught out in it when I have a backpack or something I don't want getting wet, but when I don't, I absolutely love it.
The feeling of rain pouring down on me never ceases to brighten what should be a gloomy day.

More than that, though, I love the thunder and lightning.
The bright arcs across the sky which illuminate billowing clouds.
Sounds so deep and booming that they connect you to the oldest parts of humanity.
Plus, it's super fun to do the whole \say{Light and sound move at different speeds so calculate how far away it is.}

The times when strike after strike comes in quick succession, so the thunderclaps overlap and you end up with a heavy roar in the air are beautiful.

Anyways, storms are pretty, and that's all I've got today.
\end{document}