\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{theology-question.html}{Theology Question}}
First Published: 2022 October 5
\section{Draft 1}
Currently I'm struggling with a theology question.
Apparently animals don't have immortal souls.
So far as I can tell, we know this to be true that because:
\begin{itemize}
\item St. Thomas Aquinas said so
\item The Church has generally agreed about it
\end{itemize}

Neither of those is sufficient in my mind to require my submission.

My logic for why I would believe animals have souls which go to heaven is\footnote{at least to me} a relatively straightforward logical chain.\footnote{I'm currently writing this without wifi, so I cannot fact check my claims currently.}

\begin{enumerate}
\item Prior to Original Sin there was no death
\item We die because our ancestors, Adam and Eve, committed the sin, and we inherit it as their children. This has been stated by a Pope as necessary to belief, though in the context of whether we can believe humanity sprang from multiple sources.
\item There were animals in the Garden
\end{enumerate}
There are only a few conclusions I can draw from this chain. 
Either:\footnote{or multiple, I suppose}
\begin{itemize}
\item There was death before Original Sin, and that Bible verse means something different in context/doesn't exist.\footnote{again, I'm writing without access to internet}
\item We have dominion over other animals, so when we became mortal, so did they. Lacking anything else immortal, they were then condemned to destruction
\item The Lord chose to create beings that would die in the Garden
\item When we were forced out of the Garden, the Lord created new animals which were mortal and lacked souls
\end{itemize}
Anyways, fixing my router just now took out most of my interest in solving my theological quandry, so off it goes into the ether of thoughts I sometimes have.
I may revisit this some other time.
\end{document}
