\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{twenty-five-html}{25 for Twenty Five}}
First Published: 2023 August 23


\section{Draft 1}
\href{twenty-four.html}{last year} I tried to do twenty four things between my twenty fourth and twenty fifth birthday.
I had hoped that setting that goal would have two major effects on my life.
First, I had hoped that it would make me more intentional about what I spend my time on.
After all, even though I do not know what the number is, I do know that I only have a finite amount of time on this earth.
While that has never meant\footnote{for me at least} maximizing the utility of every single fleeting moment, I do find that I prefer to look back on my time when I have been more intentional with it, rather than less.
?The second goal, obviously, was to encourage me to try new things.
I don't know how successful, if at all, that goal was.
After all, as I have been told many times by far too many people, I am generally a person who is open to trying new things.
That's certainly something I strive to be, at least.
That being said, I was at least more aware of things I had done for the first time, at least in my\footnote{admittedly spotty} memory.
?So, since I enjoyed the challenge, I decided that I'd try it again.
n for n is now being rebranded as my attempt to do more new things each passing calendar year.
Since there are an infinite number of activities I can try, that should remain doable, especially if I start lowering my standards.
?This post also feels like a good place to reflect on the first quarter century of my life.
There are arguments to be made that nothing before I have concrete memory should really count, which I have mixed feelings about, and so will ignore.
I've gotten a Master's\footnote{I can never remember if that's a possessive or not} Degree, graduated a college with a double major, and earned my Eagle Scout.
Those seem like sort of the big three in terms of explicit and externally validated life accomplishments, but there are far more things that I've done.
I have received five of seven sacraments, which I'm beyond grateful for.
?
I've also grown a lot, both physically and mentally.
Most importantly, while I don't think that any age\footnote{excluding the past year or so of my life} of previous me would have foreseen me being where I am right now, I also don't think any of the past mes would be unhappy with it.
I am grateful for the time I have had and look forward to the time to come.
My fingers are crossed that I will get more than another quarter century on this earth, and I hope to use it well.
?
Maudlin musing aside, there are some things that I want to do in this year.
I think that updates for this post will be coming in two forms: things that I have done, and things that I want to do.
There were things I wanted to do last year that I kept forgetting about, and so never did.\footnote{chief among them: taking an improv class}
With that in mind:
?
Things that I want to do before my quarter century year is gone:?
\begin{itemize}
\item Learn how to weave.
I don't really care if that's card weaving, tablet weaving,\footnote{which may not be different? I'm only half remembering words anymore} floor loom, rigid handle, tapestry weaving, or rug.
What's important to me is that I make the time to make at least a single woven object.
Truthfully, getting back into basket weaving would even be good enough for me.
\item Take an improv class.
It seems fun, and that's an activity that will be important to me going forward.
\item I'd like to learn a polka on the accordion.
It seems like the music most associated with the instrument, at least to most, and it's something that a lot of people I know like.
\item I want to record an album.\foonote{and release, I suppose}?
It doesn't need to be anything incredible, but I want to be able to point to a collection of songs and music\footnote{since I'm sure some of the pieces I put out will be instrumental} that I have made and that others can view and access.
\item I want to get back into book binding.\footnote{hmm back into may be wrong.} I have bound in my life, a single book.
It was the sketch book we were required to use in the introductory art class I took.
I remember loving the book, and equally importantly, loving the process of making it.
\item I want to finally learn how to spin yarn.
A good friend gifted me with a starting set last year for my birthday, and I never got around to it.
\item I want to be able to swim a continuous mile.
I don't know if I ever have been able to before, and it seems like the sort of thing that I would like to be able to do.?
\end{itemize}
Huh, I hadn't realized some of the things I wanted to do.
I don't know if I've ever articulated, to myself, at least, a desire to record an album.
Apparently all those people who say that giving yourself space is good are true.
Anyways, I have also done new things since turning twenty five!
?
\begin{itemize}
\item I \href{pinball.html}{competed in a pinball league!}\footnote{and won my section no less!}
\item I swam in Lake Superior!\footnote{it was absolutely beautiful}
\end{itemize}
?
Anyways, I hope to keep both of these lists updated, and hopefully I'll be able to start moving things from the want to do list to the have done list.
I have an awesome set of amazing friends, and I'm beyond grateful that they also do many fantastic things.
Relevant to this post, one friend wants to do a good number of the things I want to do as well, which will be nice.
?
Since this is going to be a constantly updated draft, it feels a little strange to do my daily reflection in it, but c'est la vie.\footnote{the only french phrase my family uses.}
?
\begin{itemize}
\item Still haven't worked on the eclipse talk, though I'm still thinking of ways to make the animations I know that I'll want.
\item Once again, the slightest progress against entropy, which is still something I suppose
\item Wow three for three blogging!
\item Wrote this again first thing in the morning. Yesterday I finished a chapter and began the next one 2.1/4+
\item Wrote no poetry since the last post
\item Shoot, still no journaling.\footnote{for all that this musing felt a whole lot like a journal}
\item Stretched again this morning, but also woke up feeling very stiff which isn't ideal.
\item Went to bed unreasonably early last night, but listening to my body is probably never a bad idea
\item I need to pray again?\end{itemize}?
Oh fun! I posted this a year and a day later!
\end{document}