\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{twenty-six.html}{26 for Twenty Six}}
First Published: 27 March 2025
\section{Draft 1: 27 March 2025}  
This will officially be my \href{twenty-four.html}{third} \href{twenty-five.html}{year} attempting to do a number of new tasks over the course of the year.\footnote{Apparently I never updated the twenty five for twenty five, so it's anyone's guess whether or not I made it!}  
I more and more realize that this has become less of a way for me to start doing more new things and much more a way of making sure that I recognize the many ways that I'm continuing to grow as a person.

Even though I'm well into this year of my life, I still want to have finished with this by the time I turn twenty seven!  
Let's see what things I've already done, and then start to consider what else I want to do:\footnote{I generally want to do less lists in my blogging and writing generally, but this feels like an ok place to do so}

\begin{enumerate}  
\item Learned to live with a single living parent.\footnote{we all knew that I was going to start here, since it's obviously the point that is the biggest change}  
\item Saw Hozier live in concert\footnote{which was a great time}  
\item Checked in with most of my friends to make sure that I was communicating appropriately. That's really mostly me accepting that I like to have expectations explicitly stated and trusting my friends enough to do so.  
\item Officially gave up on my web novel.\footnote{the day that I have in my notes is, perhaps unsurprisingly, the day I made the post on the site}  
\item Seasoned a wok!\footnote{or, at least, attempted to}  
\item Sharpened my own knives at home\footnote{or, at least, ran my knife over a sharpening stone. In doing so, I realized that my standard for sharpness is actually relatively dull, which is kind of nice}  
\item Sat Shiva! It was a really fantastic experience, in as much as anything about grieving can be good. Watching someone else near to me deal with the loss of a parent without Shiva\footnote{do I capitalize it???} really highlighted just how beneficial it was in terms of my ability to process my grief and accept the way that life is forever going to be different for me.  
\item Did a large embroidery pattern\footnote{which I'm actually really proud of}  
\item Was the entirety of the stage crew for a cabaret. I don't quite know how to phrase this one, but it's mostly that I was the sole person for staging all the props and scenes for a number of small acts. It was kind of weird having such responsibility  
\item Joined a book club with some church friends\footnote{and unfortunately had to stop the book club because I then joined a community choir}  
\item Joined a community choir! It's TTBB which is also really cool  
\item Went to adult night at the local conservatory (nature not music)  
\item Started going to a weekly watch party for a television show. I really don't think that I've ever really kept up with a show as it aired each week  
\item Did an unassisted downward dog!\footnote{there's a chance that I did this before, but I cannot remember a time when I did}  
\item Tried a bunch of different fitness classes!\footnote{barre, rhythm cycle, zumba, HIIT}  
\item Started teaching children's religious education  
\item Designed a novel search pattern\footnote{I think, at least, and we'll see whether or not it ends up working}  
\item Was explicitly acknowledged in a Ph.D. defense not as a formality\footnote{i.e. not a member of my research group, who is obligated to do so}  
\item Started using the university-wide high throughput computing center  
\item Got an award for service: I apparently gave talks in the greatest number of counties through the university's talk program  
\item Learned how to crochet flowers  
\item Realized that my life is better when I wear good noise cancelling headphones, bought a pair, and became comfortable wearing them in public  
\item Will\footnote{in about a week} lead an interactive science demo with children.  
\end{enumerate}

Wildly, that's already twenty three items.  
Many of them are things that I don't really think that I would count if given the option, and so let's pare the list down to things that I actually consider novel:

\begin{enumerate}  
\item Learned to live with a single living parent.  
\item Saw Hozier live in concert  
\item Seasoned a wok!  
\item Sharpened my own knives at home  
\item Sat shiva\footnote{turns out it is not supposed to be capitalized! Who'd've thunk? Thunk is a weird word, now that I think about it even a little bit}  
\item Did a large embroidery pattern\footnote{I feel like I should justify this one more, also maybe I should blog about the fact that I actively hate the idea of anyone caring about it? apparently at least}  
\item Did the entire stage managing and crewing for a small cabaret production  
\item Joined a community choir! It's TTBB which is also really cool  
\item Went to adult night at the local conservatory (nature not music)  
\item Started going to a weekly watch party for a television show. I really don't think that I've ever really kept up with a show as it aired each week  
\item Did an unassisted downward dog!\footnote{there's a chance that I did this before, but I cannot remember a time when I did}  
\item Started teaching children's religious education  
\item Got an award for service: I apparently gave talks in the greatest number of counties through the university's talk program  
\item Learned how to crochet flowers  
\item Will\footnote{in about a week} lead an interactive science demo with children.  
\end{enumerate}

That's still 15!  
That means I need to do eleven in the next four months, which is more than doable, hopefully!  
That's a relief, honestly, and really points out just how much my mind lies to me.  
I did really believe that I had not done anything novel this year, entirely because I thought that my mom's death had been all consuming.  
It's nice to know that that isn't true!  
Only two and a half of the items are explicitly related to that, and the rest I don't think were impacted at all!  
Wild how life continues to go on even when I want it to stop, and wild that I continued to actively live even when I felt like I was behind a curtain watching life pass me by.

N.B. This is the living list of ways that I want to take care of myself and/or goals that I have and/or things that I want to do. I'm planning to start adding the shorter term goals that I have to this as well.

\begin{itemize}   
\item Professional:   
\begin{itemize}   
\item Continue to work at work  
\item Work towards future career:   
\begin{itemize}   
\item Read the recommended readings about science communication.  
\item Do the reflections that were recommended to me (mostly focused around why I care about science communication)   
\item Figure out the difference between my public-facing and field-facing presentation affects. As I focus on becoming a better presenter, I need to become aware of the difference and how to switch them   
\item Need to look for jobs  
\end{itemize}   
\end{itemize}   
\item Health:  
\begin{itemize}   
\item Spiritual:   
\begin{itemize}   
\item Get back into the Lenten goals (pray chaplet of St. Michael, give money equal to amount I'm spending on myself, stop scrolling social media, stop playing video games)  
\item Be intentional about prayer. That means both making time for prayer and actually doing it.  
\end{itemize}   
\item Mental:   
\begin{itemize}   
\item Clean my Life:   
\begin{itemize}   
\item Remove dirt and clutter from physical spaces (standard definition of clean). I'm going to change this goal to:  
\begin{itemize}  
\item At least once a week, each room has nothing on the floor  
\item At least once a week, all surfaces which are not inherently storage are cleared off  
\item At least once every two weeks, each room is vacuumed  
\item At least once every month, all non-storage surfaces are explicitly washed/cleaned  
\item At least once a week, I get rid of at least one item that I notice (meaning throw away or in rare circumstances gift or donate)  
\end{itemize}  
\item Spend time each day thinking about the goals for the day, and getting them out of my head and onto the page. I still don't know how to do this, but I also feel like I have less explicit goals these days.  
\item Start reading and returning the library books I have. I'm going to try to do better at this, but I don't know how  
\item Don't waste time, and in particular, be mindful about making sure to take breaks and rest. Especially make sure to do rest which revitalizes the me of tomorrow, rather than rest which simply keeps me in stasis  
\item Clean sight lines. Is my space set up in a way that orients me towards my goals for the space? If not, how can I make it so? Darn curse of entropy.  
\end{itemize}   
\item Interpersonal Relationships:  
\begin{itemize}   
\item Figure out what belongs in a normal letter to a friend.  
\item Get back into writing letters.   
\item Continue to explicitly confront the voice in my head that says that people hate me  
\item Work to message friends at desired intervals.  
\item Potentially start giving small gifts, though many people also dislike clutter, so think carefully about that one. Have started giving friends things as I have them, and they're well received. Thoughtfulness is the key.  
\end{itemize}  
\end{itemize}   
\item Physical:   
\begin{itemize}   
\item Go to group fitness classes more regularly and more often. Gym is closed this week, I learned yesterday. I really need to start going to yoga in the mornings, especially since my afternoons and evenings are about to get really full.  
\item Feed myself simply and healthily. Healthy here means trying to generally avoid processing.  
\end{itemize}   
\end{itemize}   
\item Other:   
\begin{itemize}   
\item Music:   
\begin{itemize}   
\item Work on guitar  
\item Learn the songs that jam partner suggested and/or requested I learn  
\item Get back into the album. I was jamming with the friend on Saturday and they talked me up to their partner about having written music. I couldn't remember the chords for one of the songs, and that's kind of sad to me.  
\end{itemize}   
\item Writing:  
\begin{itemize}   
\item Write poetry more often, ideally nightly. Wrote some free prose yesterday!  
\item Find a way to add meta data to my blog posts and then add the meta data\footnote{at least moving forwards and hopefully also working backwards through the many posts that I have}  
\item Not only write blogs, but also post them. Ideas include:\footnote{as a living list!}  
\begin{itemize}   
\item 26 for 26 Wow! Lookie here  
\item Listening to an album and writing about my experience with it. Unsure if this is best done with one I have prior knowledge of or a new one, but regardless, sit and listen without other stimuli. One of my lab mates and I have been exchanging albums, so this could be fun  
\item The arts I've been doing lately  
\item Why I care about science and communicating it\footnote{ties into the professional goal}  
\item My general disposition to authority. I'm not entirely sure what that meant, but it was a note I wrote to myself while half asleep, so I'll leave it here.  
\item How to feed myself. How I am, how I would like to, and what the difference is  
\item Motivation, autotelic motivation, etc. etc.  
\item The idea I have that knowledge (music, writing, science, etc.) is revealed, not acquired  
\item Understanding the human experience, esp. in/re. writing  
\item Doing the work to improve myself and time discount  
\item My writing style(s) and what they show  
\item The four levels of mastery  
\item \say{the only way out is through, and the only way through is forward}  
\item Internal and External Arguments within and without\footnote{what's the term for not just within?}  
\item Curse of knowledge, esp re. Music Theory  
\item What does it mean to succeed at a creation? (reception, viewership, etc.)  
\item Inertia (re: my mind sticking to the thought patterns I have at a moment)  
\item Why I feel the way that I do about the art I create and work on.\footnote{e.g. why am I so opposed to framing the embroidery or giving it to someone who would cherish it? Why is it that I told a friend yesterday that I don't like using extant embroidery/cross stitch patterns because I think that most art should be created a single time, and what does that mean? Where is the line between art and functional things (e.g. I love crocheting the same flower a hundred times or the same hat a million (exaggeration for literary effect) times}  
\item I know that I have a musing somewhere about flavors of truth. Revisit it  
\item Generally revisit the old blog posts  
\end{itemize}   
\item Get back into writing the web novel  
\item Write other fiction. Ideas include:  
\begin{itemize}  
\item The book I made a document about in late January  
\item A story told through bullet points  
\end{itemize}  
\end{itemize}   
\item Other creation ideas (that I'm going to keep here so I don't lose them and so that maybe someone will steal them and I can consume without having to create)\footnote{hint hint}:  
\begin{itemize}  
\item A short film: watching the screen as a breakup letter is written  
\item Embroidery pattern  
\item Embroidery physical relic  
\end{itemize}  
\end{itemize}   
\item Upcoming self imposed deadlines (within the ten days):\footnote{OOf this is a \textbf{lot}}  
\begin{itemize}  
\item Brain dump about science communication (due 3/24)\footnote{brain dump meaning I sit down at my computer and start typing until the well runs dry in regards to the idea. Avoid significant editing or revising wherever possible}  
\item Brain dump a publicly accessible chapter (due 3/31)  
\item Revise the overview of my program, which also means finishing writing it up\footnote{something I just realized is that I never added time to make graphics, or a stage where I would explicitly put them in. I think that I plan to do so after the first time my advisor looks at the drafts, because no point making something she thinks is pointless} (due 3/31)  
\item Have final convergences for the results I'm trying to reproduce (due 4/4)\footnote{I know this is more than a week away, leave me alone}  
\item Write next week's plans (due today)  
\end{itemize}  
\end{itemize}
\end{document}