\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{twenty-four-html}{24 for Twenty Four}}
First Published: 2022 August 22
\section{Draft 1}
This year I chose not to participate in a yearly tradition that was titled \textit{n} for \textit{n}.\footnot{e.g. 21 for 21, 22 for 22}
While what that initially meant is unimportant, what's important is that I've decided to reincorporate the name.
Instead of meaning whatever it used to,\footnote{truthfully, who can remember what it meant?} I'm going to try to learn 24 new skills while I'm 24.
These can be actual skills, like an instrument or language, or things I just had never done and so had no way to do them.
I'll also include skills I once had but no longer do, such as picking up an instrument I've forgotten or doing some athletic feat that I needed to retrain for.
I'll keep this list updated with them, and may remove them depending on how things go.
Thus far I really only have one, but I'm hopeful to add more.

\begin{enumerate}
\item As I've alluded too \href{open-mic-2.html}{before}, I've started playing at open mics.
I'm going to put the skills of \say{playing with a partner} and \say{regularly doing an open mic}\footnote{I'm not counting the ones I did in college because the only people who came to them were open-mic performers (open mic-performers?), and I never prepared for them} together, since each is really only half of a new skill.\footnote{I've done lots of me singing with a piano and the open mic as mentioned above}
\end{enumerate}

Thanks for following me on this journey!
I'm hopeful that this will let me reflect on the passage of time more intentionally.
I'm also hopeful that it will mean that next summer, when I\footnote{likely} have far too few entries, I'll use some time to branch out and try new things.
\end{document}