\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{universe-3.html}{Universe in the Park Part 3}}
First Published: 2023 July 18
\section{Draft 1}
The \href{universe.html}{time} between \href{universe-2.html}{UitP} posts is decreasing.
Thankfully,\footnote{for my sanity and research productivity, not for the sake of this blog. I would happily make this blog about the many wonderful talks and people I get to give and meet respectively (the talks are rarely wonderful, though the parks always are. I suppose I should've said parks I've seen)}
I've got a fairly long break before the next one.

This past trip was two State Parks, one of which I spoke at last year, and the other of which I had never been to before.
The talks contained identical slides\footnote{barring date, as before}, but some lovely people\footnote{read: my family} who went to both said that the content of the talks was wildly different.
There were fewer questions, though the attendance was worse than before, so that makes some amount of sense.
In defense of the world: the first talk happened just after a thunderstorm that took out power in the entire area and downed a tree near where I was speaking.
The second talk was double booked against a number of concerts.

I still had a fantastic time, though.
I got to spend time beside a fantastic body of water.\footnote{a lake some could even call pretty great}
Both nights managed to clear up in time for star gazing, which means that I went from being one in four talks successfully stargazing to three of six.
One more and I hit a majority.

Iteration continues to be true, and I've now done four of nine for the summer.
There's a tenth that remains tempting, and a tentative winter talk, but those shall come or not as they're meant to.\footnote{I started the sentence so well with T but that fell apart.}

For monthly goals:
\begin{itemize}
\item I did not clean much today, though I'm about to do a bit.
\item I wrote a whole chapter today, this post, and yesterday a song draft.\footnote{technically I sang a song draft but}
\item I still haven't been as active as I'd like to, but wow am I exhausted.
\item I woke at six today, which was fantastic. Tomorrow I hope I can do the same.
\item I did CCCiaY on the walk to work today, and I'm planning to do a rosary tonight.
\item I wrote a\footnote{overly long} chapter today, which was great. If I can keep this up for the rest of the month, I'll be ahead.
\item As mentioned, I wrote a song yesterday. I'll hopefully remember a poem tonight.
\item I wrote a fourth letter and posted them all today. I've forgotten entirely who one of the people I promised a letter to was, which is a major shame. I will keep hoping to find them.
\end{itemize}

364/87
\end{document}