\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{universe-2.html}{Universe in the Park Part 2}}
First Published: 2023 July 2
\section{Draft 1}
Wild.

It was \href{universe.html}{exactly a month ago today} that I last blogged about doing a Universe in the Park.
I won't rehash the entirety of the program this time, since that's already been done.

This time, I went to a State Park\footnote{interesting that I also didn't give the location last month} that my group had gone to for a canoe day last year.
It was fun seeing some of the same sights as I canoed on the same path, though changed with a year.
There's also a restaurant which overlooks the lake, and last year my group and I wanted to try it.
This year, I did.\footnote{it was fine, I definitely wouldn't say the best in the state, but I suppose that I'm not the judges}

My slides were identical to last talk's, with the exception of the date, which\footnote{obviously} changed.
I got a few questions about the title.
One was why we work in the coldest areas, rather than the hottest.\footnote{I used the analogy of a smore. If you let your marshmallow catch on fire, it turns into carbon.
Fire is much colder than the hottest regions of space.}
The other is if it's actually the coldest regions of space.\footnote{I said no, but I was allowing some creative liberties fora  more engaging title.
That got a laugh.}

I learned that I am absolutely terrible at estimating attendance.
Last talk I thought hat I had thirty or so people and had fifty three.
This time I thought I had exactly twenty eight and apparently had sixty eight.\footnote{also a dog? Everyone assures me it was adorable.}
Unlike last time, it was too cloudy for observations, so when the talk and\footnote{incredibly numerous. There were five or so children who were absolutely filled with questions and two twenty somethings with a good number as well} questions ended, I was free for the night.
Also unlike last time, I did not spend the night in a dormitory.
Instead, I got to camp.

As of the last post, I had given one of six for the summer.
As of this post, I have given two\footnote{good that iteration still works} of nine talks.
The extra three came because I remembered just how much I really love camping.
If the university and state want to pay me to go camp, I'm absolutely going to take advantage of that.

\begin{itemize}
\item I've done a quantum of cleaning, which is not as much as I wanted, but the day escaped me.\footnote{note to self, do not expect to be productive the day after camping}
\item I managed to blog, which is great!
\item Before posting, i said I would do a 5K. That's incredibly untrue, as the sudden wave of exhaustion that just hit me would tell us.
\item I woke up today at six, because I was outside and that's when the sun rose.
\item I made time to pray at the chapel before and after Mass, which is always really nice.
\item I am intentionally taking today off of writing the book, because it's already lateish and I value sleep more.
\item When I return from the run\footnote{and shower, obviously}, I plan to write a sonnet.\footnote{since no run, now I suppose}
\item I addressed two and a half more letters today\footnote{three, but one was a duplicate of an already addressed envelope, so it gets to hang out for a while} and wrote a letter.
I tried to post it, but the post office was closed.\footnote{and doesn't have any sort of while they're gone slot which is strange to me}
\end{itemize}


407/167
\end{document}