\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{universe-4.html}{Universe in the Park Part 4}}
First Published: 2023 August 21
\section{Draft 1}
It's been a fair minute since the last time that I wrote this blog.?Sorry for that!?Hopefully future delays will happen with far less frequency and length.
So, since my last posting, I've actually gone on more than one UitP.
I've given five over the course of three events.
They've all been incredible, though each in their own way.
?The first one I gave since accidentally giving up was at what I have to assume is the most popular state park in the state.
It was scheduled for a Tuesday, and I even still had more than twenty people show up.
Apparently in an average year, they get more than three million visitors, which is wild to me.
?The viewing of stars from that talk wasn't the best I've ever had.
Unfortunately, the place they recommended I set up was somewhat obscured by trees and the surrounding cliff.
That isn't too much of an issue, though, because historically most of the stars and other celestial bodies I care about seeing are in the upper portion of the sky anyways.
It was also beside one of the shelters, which remains lit apparently all night long.
That made it a little bit harder to see the stars.
A number of my friends made it up to the talk, which was really nice!?
After that, I had a brief few days off.
That Friday and Saturday, though, I drove up to the northern part of the state.
While there, I made a quick detour to drop off my accordion at the\footnote{as far as I can tell, only,} accordion repair school.
They had a museum, which I'll hopefully find the time to blog about in the future.
The talks were hosted by a pair of sister parks, and so they asked me to prepare multiple different presentations.
Despite the fact that I've been assured each instance of my usual talk is different, I still made a new slide deck.\footnote{I'd call it a powerpoint, but I'm producing PDFs in LaTeX, which I then present in a PDF viewer, so powerpoint feels fully wrong to use as a descriptor}
Since my talks were scheduled during the peak of the Perseid\footnote{I think that's how it's spelled} meteor shower, I made the new slide deck about that.\footnote{I suppose that I've blogged about it in the past, so that should not be a surprise.}
Both nights, unfortunately, we were rained out from observing.
Even more unfortunately, both nights the rain was completely unforeseen\footnote{unforecasted?}.
The second talk proceeded much like the first, though with far more questions.?
There was a camp of high schoolers who were very interested in black holes.
As it turns out, one of the counselors for that camp is a rising student in the Astronomy PhD program at my university.
It was great to meet him.
A whole week went by without doing anything with the talks, since I planned to reuse my slides again this past weekend.
At the end of the week, I drove just about as far north, though slightly further east this time, to give another two talks.
Both nights had perfectly clear skies, which was fantastic.
On the first night, my audience was primarily older people, members of the friends of the state park, which was cool.
It was also by far the best prepared audience I've ever had.
When I asked my standard starting question of \say{who has heard the term astrochemistry before?} most of them actually raised their hands.
That was a surprise, but did mean that I had a number of great questions.
After that, we looked at Mizar,\footnote{a double star in the big dipper} which I'm going to more and more use as a staple star.
It's really cool that it's a double star.\footnote{two stars that are visually very close together on the sky.}
When that talk ended, I went to sleep and woke up, excited for my second talk of the weekend.
I took a leisurely drive up another hour north, stopping at a coffee shop, a few bakeries, and a farmer's market.
I also got to\footnote{was required to? I suppose there wasn't another real option in terms of making the voyage} take a ferry up to the island my next talk was on.
It was apparently not advertised at all until five or so minutes before the talk began.
Despite that, there were around thirty people at my talk, which is still great.
?Since I made it to the island plenty early, I had time to go swim in another Great Lake.?That was really fun and cool,\footnote{almost icy, in fact} and the water was so clear.
It was a really fun trip, for all that the seven hour drive the next day was less than my favorite thing to have ever done.
?I think that I only have one more of these talks scheduled for the summer, which is really weird.
It both feels like too many and too few.
I do regret not blogging at all during the five talks, but life got in the way.\footnote{primarily, I went to a concert and a birthday party on the fifth, celebrated on the sixth, and did not have access to my main computer from the ninth through the seventeenth.}
I'm also sorry if this post is far more verbose and rambly than normal.
I'm trying out a \href{4thewords.com}{new word processor}, and it encourages high word counts.

\begin{itemize}
\item I finished the talk I needed to do, and have been doing a lot of research about eclipses.
\item I think entropy is currently winning. I wan to start beating it back, but.
\item Whoops, minimal blogs.
\item I've written a little over a chapter today 1/4+
\item I think I gave up on sonnets around when I gave up on blogging.
\item I also gave up on this.
\item During the first weekend of talks, I did write out lyrics to a potential first draft of a song. I also sang myself another song while driving this past weekend.
\item Still no stretching.
\item I have been trying to prioritize sleep more. I have certainly been needing it.
\item I have been so bad about the rosary/prayer in general lately. I'd like to recenter it this week.
\end{itemize}
918/130
\end{document}