\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{walking-blind.html}{Walking Blind}}
First Published: 2018 November 13

\section{Draft 1}
As most of you alleged readers know, I have somewhat bad vision.
And, since we live in the future, we have wearable technology that corrects for that.
Most of the time, I correct my vision with glasses.
On occasion, I correct it with contacts.
And then there are the nights like tonight.

While going about my day, I paused in my room to do some homework.\footnote{and take a nap}
Upon preparing to leave the dorm for a talk about maps that shaped America,\footnote{so British, I know} I realized I couldn't find my glasses.
So, knowing that I knew how to get to the talk fine without seeing detail, I set off.

London is a much different city with poor vision.
Crowds of people, who normally I didn't register, suddenly seemed so much more sinister.
My own shadow, distorted by street lights, gave me pause, as I thought I had a pursuer.

But, I made it to the talk safe, oddly enough.
Today was nice, if only to remind myself both how blessed I am to have correctable vision, and how even the smallest of changes can drastically affect how we see the world.
\end{document}