\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{wedding.html}{Wedding Recap}}
First Published: 2023 June 13
\section{Draft 1}
Well, it's been almost a week since my last blog post.
Instead of excuses, I think I'll make what has become a rarity amongst my blog posts\footnote{honestly, it may have always been a rarity} and give a quick recap of where I've been.

Last Friday, I woke up at 2 am to start a four hour drive to an airport.
From there, I traveled across the country to go to a friend's wedding.
While I could have made time during that day, I did not have the mental energy to do so.
It ended up being more packed of a day than I expected, though I should have expected more, given that there was a rehearsal dinner and wedding.
The rehearsal dinner was held overlooking a beautiful gorge with a fantastic waterfall.\footnote{that in retrospect, I should have taken photos of. I should have taken a lot of photos this past weekend and took as far as I can tell (almost) none}

What I'm assured was six hours of sleep later, I woke to Saturday.
On that day, two of my dear friends got married.
It was a lovely ceremony and day.
I don't know what the bride did to get ready, but the groom spent much of his morning in prayer with his groomsmen.\footnote{and me, who was tagging along}
At the wedding, I had been asked to sing and I volunteered\footnote{or was asked, or threatened, depending on which subjective history you listen to} to play the bagpipes.

After the wedding, I had a wonderful time at the reception, meeting the newlyweds' friends and family and dancing.\footnote{I got to teach a shocking number of people country swing which was really fun for all that I absolutely should not be trusted to teach.}
It ended two or so hours later than expected, and the groomsmen\footnote{and me} spent some time that night bonding without the groom.

In the morning, even more sleep deprived, I went to Mass with some of the bridal party who were still in the town.
The Parish was hosting a pancake breakfast, so I went to that with some friends who met the bride and groom at a similar time.\footnote{and therefore in the same town.}
Following that, I rode the two hours back to the airport with one of the bridesmaids and her partner.
That was a really fun car ride!
We bonded over a love of fantasy and other things.\footnote{I cannot remember}
I taught them \say{my cows,} which is truly the pinnacle of car games.

At the airport, I ran into another friend who was at the wedding.
We were scheduled to take the same flight back.
As it was ready to board, though, we were told that it was delayed for seven hours.

Three hours later, after waiting through the entire line to die, we went to ask for a meal voucher.
Instead, we were given hotel rooms and new flights.
I was scheduled to fly out yesterday,\footnote{via another airport, adding a full twenty four hours to my ETa back home} and he was scheduled for today.
Thankfully, we were able to reschedule to the same flight.

We carpooled in a Lyft to the hotel,\footnote{with an interesting driver} ate dinner,\footnote{at an Olive Garden, where we managed to pay the bill with the meal vouchers} and went to sleep.
In the morning, I realized it was Monday, rushed to finish the chapter of my web serial, posted it, and ate breakfast.
Back at the airport, I ran into the newlyweds, wished them congratulations, and saw that there was a flight boarding to my destination.

Thankfully, they were willing and able to seat my friend and I on this earlier flight, and we made it back a full three hours earlier than expected, which was great.
On the downside, I'm now exhausted and missed the only full day of lab work I had the chance for this week.\footnote{because today was a group big picture planning meeting, tomorrow we have practice talks, and I leave again on Thursday.}
Still, I'm far too glad with the fact that I was able to share my music with my friends at their wedding to mind.

\begin{itemize}
\item Friends coming over is on indefinite hold
\item Took a five day hiatus from blogging
\item Danced so much that my entire body was sore for two days
\item Woke up at six most of the days in the interim, for all that I did not want to.
\item The groom and wedding made prayer easy, but I really fell off of it when the air travel got delayed.
\item I fell technically a little behind, and posted a too short chapter. I'm almost finished with tomorrow's though, which is nice. I'm hopeful I can get Friday's cleared out by the end of tomorrow.
\item I want to write a dumb song so started writing a new song.\footnote{procrastination who?}
\item I have another name on the list of potential people to send a letter to!\footnote{which was originally phrased as an overly hyphenated phrase instead}
\end{itemize}

684/159
\end{document}