\documentclass[12pt]{article}  
\newcommand{\say}[1]{``#1''}  
\newcommand{\nsay}[1]{`#1'}  
\usepackage{endnotes}  
\newcommand{\B}{\backslash{}}  
\renewcommand{\,}{\textsuperscript{,}}  
\usepackage{setspace}   
\usepackage{tipa}  
\usepackage{hyperref}  
\begin{document}  
\doublespacing  
\section{\href{what-we-dont-post.html}{What We Don't Post}}  
First Published: 2025 May 21

\section{Draft 1: 21 May 2025}

I have, not infrequently, written an entire blog post only to realize that it had no place on this site.  
That can happen for various reasons, and I've more recently started thinking about how I can still reference that I did do writing even if I'm not posting the results.  
So, with that in mind, let's talk about what we don't post.

Most often, what I don't post is either overly political or overly personal.  
That which is overly personal often includes vulnerability that does not feel appropriate\footnote{see the daily reflections!}, and more often than not these days focuses around my mother.  
From here on out, I'd like to make a new draft of this with each post that I don't make.

Yesterday I got most of the way through a reflection about morality and the role of women in the Church, before realizing that I didn't really care about it any more.  
More than that, though, I think that I forgot what I wanted to say in the post at all.  
I hadn't, and haven't, reflected about the meta-reasoning behind each folly, and don't really know if this is the space I want to use for to do so.\footnote{if only because I'm at writing camp and am currently at a weird mental and physical space where I both feel productive but also as though there's nothing I want to do. It's a really nice stage, because my thoughts feel like they're under my command, which is not something that I am at all used to.

Turns out it was a prelude to feeling tired, which I guess makes sense.}

Anyways, all this to say, there is much that I do not post, even though this is something that I will

\section{Daily Reflection: 21 May 2025}

\begin{enumerate}

\item Top Priorities:

\begin{itemize}

\item Sleep:

\begin{itemize}

\item Keeping sleep time sacred?

Yeah! Went to bed at like 8 again last night. Felt great, somehow actually slept through my alarm though!

\item Good sleep hygiene?

Eh, I have to imagine so.

\item Sleeping enough?

Slept through alarm which implies no, but idk, maybe it's also just the whole \say{I'm getting up earlier than I am used to}.

\item How well rested do I feel?

Eh, decently. I get exhausted easily, but that's the nature of life

\end{itemize}

\item Feed myself:

\begin{itemize}

\item Did I eat breakfast?

I'm about to! Yesterday I ate a breakfast equivalent.

\item Did I eat a second meal?

I did yesterday! I went for a long-ish walk and got the cheap overly large chinese-american lunch that is popular amongst a demographic of students here.

\item Did I eat dinner?

I think so! i honestly don't remember what happened when I got home last night, I was just so tired.

\item Water?

Nowhere near enough yesterday, today is another day, though. Goal is to finish the whole water bottle and all of the tea.

\end{itemize}

\item Family:

\begin{itemize}

\item Am I neglecting any familial obligations?

I guess I'm not listening to the new album quite as much as I maybe should be.

\end{itemize}

\item Movement:

\begin{itemize}

\item Am I stretching at least 5 minutes per hour of computer time?

I did not, though I did get far closer yesterday. If anything, the fact that I had such limited motivation really helped with that, because I could always use stretching as a way to be productive while procrastinating

\item Am I generally making efforts to be limber?

I think so! I spent a solid 20 minutes stretching last night and a few minutes this morning vaguely stretching. I know that I'm slowly tightening up again, which I don't like, though.

\end{itemize}

\item Spirituality:

\begin{itemize}

\item Time for prayer?

No

\item Prayer?

No

\item Time for sacred silence?

No

\item Deep breaths?

I'm generally doing it, at least as I read these daily reflections. Outside of that, though, I don't know.

\end{itemize}

\end{itemize}

\item Secondary Priorities:

\begin{itemize}

\item Thesis/ Ph.D. work:

\begin{itemize}

\item Keeping up on the writing deadlines?

I realized yesterday that I don't really have an internal image of where my thesis currently stands and what it needs.  
With that in mind, I printed out a copy of the thesis as it stood yesterday to see what I have.

\item Reading the necessary things?

I brought more textbooks to the camp today, which might help.

\item Making graphs?

No.

\begin{itemize}

\item Visual depiction of Latin Hypercube

\item Visual depiction of Grid Search

\item Visual depiction of random search

\item Visual depiction of Loomis-Wood Diagrams

\item Visual depiction of Spectral Stacking

\item Visual depiction of how the fitness of the spectral stacks is really reliant on the graphs being the right height

\item I guess that the stuff for intro to quantum video counts here.

\item Plots from the actual results of the runs, to make sure that it worked out.\footnote{SSC, AAT, if any vib states were good, what happened to the computations, etc}.

\end{itemize}

\item Organizing citations?

I spent a little bit of time yesterday, and I also realized that I had not ever actually made the .bib file for the thesis, so set that up as well.

\end{itemize}

\item Love:

\begin{itemize}

\item Taking risks?

Marginally!

\item Making efforts?

Minimally!

\item Showing affection?

Yeah!

\item Being honest?

Trying to

\item Being open?

Eh.

\item Being appropriately vulnerable?

Yeah

\end{itemize}

\end{itemize}

\item Adjacent to Primary and Secondary:

\begin{itemize}

\item Typing Practice?

Yeah! I like doing it first thing in the morning. However, I do also know that the morning is my most productive time, so a large part of me feels some bits of guilt about not using the time to be productive. Hard to know what the correct thing to do is, though.

\item Applying to jobs?

Not so much. I have a meeting with the career office this afternoon about an application which is due tomorrow, so that's existentially terrifying.

What if they don't want me?  
Even worse, what if they do!

\item Reading the things I think could be good?

Eh, not as much as might be good. I want to understand how rotational transitions work, and I want to describe that in my thesis. I'm just not sure how much of an explicit derivation I should/want to/can have. It's certainly a lower priority than other things I could be doing.

\item Making manim videos?

Nope! That's something I could work on when I run out of energy today though!

\end{itemize}

\item Cleaning?

\begin{itemize}

\item Office

Remains fine because I'm not there.

\item Home

Minor efforts, and I found out that Monday is Memorial day, so that should help!  
Nominally not allowed to be at work, which means that I can really focus on cleaning the home.\footnote{or other things, as needed, I guess}

\item Car

Shoot! I'm giving an outreach talk on Friday and Saturday, which means that I need to have it cleaned.

\item Computer

Not a ton, but a little bit last night.

\item Other as needed

I don't think that there's much else. I guess my thoughts and life and thesis, which I have done a little bit of.

\end{itemize}

\item External Obligations:

\begin{itemize}

\item Guitar for wedding?

I realized yesterday that I want stepwise and fourth-wise motions.  
If I limit myself to major chords, that means that I only have twelve chords at most, and since most of them are symmetric\footnote{going from A to B is the same as B to A in reverse, give or take}, there's really not that much to do.  
Since I don't realllly want to be moving all around the neck, that limits the chords even further.  
That being said, I do still need to be spending time on it.

\item Travel plans?

Nope!

\item Talks for parks?

Signed up for a few more, so I think that I've officially set up at least as many talks this summer as I have before this summer.

\item Other requested talks?

Not at all!

\item Talks for conferences?

Yesterday while in my mood of existential dread I made the \say{dream talk, minimal viable talk, realistic talk, stretch talk} outline.\footnote{read: this is what I need to do in order to have the content for the talk which satisfies each of the sets of goals}  
I have about a month until the conference, which is both too long to feel urgent and also not long enough to be able to feel comfortable with procrastinating it in full.

\end{itemize}

\item Tertiary Goals:\footnote{mmmm off by N numbering}

\begin{itemize}

\item Blogging?

I'm going to get this post out today, and I will commit to that.

\item Reading?

I have been churning through the Cradle series again, which is fun.

\item Web Noveling?

As with blogging, I'm going to get a chapter done today.  
I will also do everything in my power to get another chapter done tomorrow, and a third done Friday.  
I don't know when, exactly, would be best for me to do that, but we'll see if it's possible.  
I think that I really need to just accept that even though they tell us to stop working after boot camp ends, it's only 4pm which means that I do, in fact, have a lot of the day left to do things.  
Might also want to go on a long walk tonight!  
Oh wait, today is burger night, hmm.

\item Guitar?

Played three fishers this morning, which was fun.  
I love the way that things sound when I'm still primarily asleep.

\item Other hobbies?

\end{itemize}

\item Quaternary Goals:

\begin{itemize}

\item Letter writing

Nope!

\item Handwriting/penmanship

This week is dissertation camp, and I realize that I've been doing a lot of handwriting.  
I'm not totally sure why it is that writing things by hands makes my life go better, but wow do I need things to be hand written.

\item Picking a new signature

Honestly, I don't think that this should be an entry any longer, because wow I do not make progress on it.

\end{itemize}

\end{enumerate}

\end{document}