\documentclass[a4paper]{article}
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\newcommand{\<}{\textless}
\renewcommand{\>}{\textgreater}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{will-he-or-wont-he.html}{Will He or Won't He?}}
\section{Draft 1}
Today, as you might have noticed, is Thursday.\footnote{well, as of writing this, it's AD 2018, 20 September}
On Thursdays,\footnote{Thursday's?} I've kept meaning to go to a Baptist Church somewhere in London, but haven't for a variety of reasons.

So, there's a reason for me to be at the Baptist Church, and it isn't that I've had a sudden change of faith.
Instead, there's an Irish Bagpiping group that meets there every Thursday night.
They're an Irish Bagpiping group in the sense that they play the Irish Bagpipes,\footnote{Uilleann Pipes} not the \say{normal} Scottish Pipes.\footnote{Great Highland Pipes}
Uilleann Pipes are objectively better as an instrument in many regards.
So, I've been excited to try them, but haven't yet.

The first week I was here, they didn't meet, as it was Summer vacation in London.
The second was the same.
Last week, I was locked out of my dorm, so needed to find a way back into it.\footnote{spoilers, I got in}
And this week, some members of the group decided to do a movie night, so I attended that instead.\footnote{it was fun}
Maybe next week?
\end{document}