\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{writers-block.html}{Writer's Block}}
First Posted: 2018 October 19
\section{Draft 2}
One of the most dreaded occurrences in a writer's life is writer's block.
Now, I never really have that problem.
I never look at a blank page thinking \say{I have nothing to say.}
What I get instead,\footnote{like today} is the idea that nothing I have to say can be expressed in less time than I want to spend expressing it.

That happened a few times for me today.
I'm working on another paper about diaries,\footnote{stay tuned!} and in theory working on a paper about theatre.
My creative juices are flowing, just not how I'd like.
I thought about trying to teach what I've learned in my Polymers class, but that seemed like the wrong idea for a Friday.\footnote{the fact that it would have been effort to get the notes was a contributing factor}
So, I decided that I would write about writer's block.
Of course, as I did so, I realized that I could do a journalling prompt that I'd been given, and so did it.
It's in Draft 1, if you'd like to read it.
I expect this will happen again.
\section{Draft 1}
In what's likely to be the first of many installments, today I couldn't think of anything to write.
Now, other days that has also been true.
Somehow I persevered and found a topic to write about.
Not so today.

Anywho, time to try out some writing prompts I've been given.
One is to describe an old barn as if you are an old man whose recently learned that his son died in the war, but not mentioning the son, war, or death.
Here we go!

The barn looked much like it always had, and yet somehow different.
The bright red had faded over the years, into the color of dust.
Strange how dust was featuring so much in his mind today.

The doors creaked when you opened them, as if they'd been forgotten about over the years of milling the field.
Vines had started growing up the sides, unchecked by their normal pruning.

What used to seem as a deep, dark black roof had shifted overnight.
Whether it was the dust in the air or something else, they'd faded almost instantly into a grey, almost unnoticeable color.

Ok wow that was a downer.
But, I got almost 200 words out of that whole shebang.\footnote{more if we include the text following, like this}
So yeah, if I run out of things to write about in the future, I'll likely try creative writing prompts.
Sorry in advance to future readers.
\end{document}