\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{writers-block-2.html}{More Writer's Block}}
First Published: 2022 February 11

\section{Draft 1}
Apparently I've only had writer's block \href{writers-block.html}{once before} writing this blog, which is really nice.
It's very sad that I have it right now, though.

Last time I had it, I apparently debated doing some class notes, so maybe that's not a bad idea.
Then again, I've already decided on the title and url for today, which means I cannot really do that anymore.
So instead of writing anything that could have come up before I had writer's block\footnote{very much a chicken and egg problem? in that I don't really believe someone can have writer's block before they try writing}, I will instead be musing on the nature of writer's block.

Last time I had this issue, I apparently did some of this above complaining and griping about my own self-imposed issues.
I then followed a creative writing prompt.
This time, however, I lack any creative writing prompts.

Writer's block is definitely something that I've been told all writers need to work past.
Since I'm not a writer, I shouldn't have to worry about this issue, but I will operate under the assumption that having a daily writing goal is enough for the same issue to occur.\footnote{I don't really know if anyone cares about whether or not I'm a writer, but if you're curious what about me isn't a writer, please do let me know}
Failing to write has struck me the past few days.
I managed to work on the novel\footnote{since I would like to be very generous} that I wanted to write only for two days.
Coincidentally, those two days were the first two days I was writing the novel.
At this point I'm really wondering whether it's better to keep free-writing or whether I should try editing for a few minutes before I write any day, so that I know where I'm trying to work forward from in a given day's writing.
I have to assume that the amount of time it will take me is going to increase linearly, though one must wonder whether it'll increase more than linearly because of something that I cannot think of, or slower than linearly because each day's editing work will go faster due to my knowing and having already made the edits that it needs.
Who can say, but I guess I should work on it now, if only because I think I can find the energy to do my creative fiction writing even if my creative nonfiction won't work.

360
59
\end{document}