\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{writathon-23-april.html}{Writathon Retrospective}}
First Published: 2023 May 3

\section{Draft 1}
Twice a year, the website I've been self publishing my web serials on has a competition: write 55,555 words in 5 weeks.
The latest one began this year on the first of April, and I set a variety of goals related to it.
As I mentioned \href{writing-3.html}{in my last writing post}, I wanted to write more words each day that I wrote.
That goal didn't end up panning out, though I did end up still writing 78010 words in April.\footnote{where I only counted text that I physically wrote as content for chapters, one book review, and the occasional blog posts. I didn't include titles, the cases where I have macros defined for words (I use tables that have \say{Congratulations!} in them often enough that it seemed worthwhile to define a table that says congratulations), or any other writing I needed to do for life and whatnot}

Another goal I had was posting a chapter for the new book every day at 2:08 PM CST until I hit the word count for the challenge.
I accomplished that, though I did become far looser on my personal idiolectal usage of hyphens.\footnote{read: I stopped using hyphens because brain-dead is one word but brain dead is two}

I also had the goal of maintaining my 3/week schedule of the book I had started before Writathon.
I accomplished that.

I had the goal of completing Writathon, which I tangentially answered as having done above.
To be clear, i did it.

Finally, I had a goal of learning to write combat scenes.
I still don't know if I'm fantastic at it, but I think that the scenes I wrote were at least serviceable.

I certainly feel like I grew a lot as a writer, if only in terms of learning to write content I am willing to put out into the world faster.
Partially that was lowering my standards, but I also think that I grew a lot as a writer in terms of thinking in a way that transfers to the page more easily.
These past few days in particular, I noticed that I was restarting sentences two or three times as I saw how they wouldn't end correctly.
Historically, I would have needed to reread the entire chapter to notice that mistake.

So, while I'm still unsure if I plan to do Writathon ever again, I'm certainly glad that I took part in it.
If I can maintain my average of over 2700\footnote{holy crud that's a lot of words (also this post technically counts towards the average. It was 2740 before posting this, and would be 2755 after} words every day that I write\footnote{basically 6 days per week}, I think that it would remain a very doable activity.
\end{document}