\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{writing-6.html}{On Writing Again}}
First Published: 2023 July 26

\section{Draft 1}
Wow one month \href{writing-5.html}{to the day} since my last post on writing.
I guess I should look at what I thought then, before entering into what I wanted to write about.\footnote{fountain pen}

I still use Stimuwrite for my writing, and it remains a really good motivator.
It's somehow good enough that it's kept me going this whole summer.
I am absolutely more efficient with it now, because the numbers going up give me dopamine rushes, which are really nice.

I am still absolutely atrocious at writing poetry.\footnote{I mean atrocious to modify the action of creating, which I do not do, not the quality of the product (which is also low I feel like)}
I should figure out why that is.
I'm sure that it has something to do with my lack of schedule anymore, but that's just an idea.

I have continued writing letters to friends, which has been great.\footnote{I feel like it might have been smart to record who all I sent letters to, though that obviously didn't happen}
I've stopped counting those words in my word goals, which feels healthy.

I also have absolutely not been journaling in the slightest.
I don't really think that's an issue, though, because I haven't felt particularly disconnected from myself lately.
I think the grounding of writing to friends helps a lot.

Interestingly, every sentence in this musing, other than the first, begins with the letter \say{I}, and almost all of them are the word.
I guess it is a self reflection, so that makes some amount of sense.

Anyways, on to the real content of this musing.
I recently got a fountain pen, and have been using it for the analog writing I do.
It's an interesting transition, for a few reasons.

First, it's a little thicker than the utensils i've been using lately.
Despite being labeled as ultrafine, it's still about thirty percent wider than the nibs I'm used to.
It's also a lot heavier than my pencils and pens, which is a welcome change, though one that takes some adjustment.
Getting ink to run has been a little more difficult than expected, though I'm hopeful that will change in the future.
All in all, I'm very excited to see what comes of my new writing implement.\footnote{Maybe I'll even be inspired to write more.}

\begin{itemize}
\item I cleaned a fair amount today, though that was mainly because it was necessary to clean space in order to move the things I needed to move. I also washed some objects that had an indeterminate need to be washed, though since I plan on using them soon, it's likely good that they're clean now.
\item I am about to write a chapter, which I began this morning.
\item My \href{conference-2.html}{last musing's} Tuesday next has come and past, and I have not made time for exercise.
I guess that's something I need to start slotting back in.
\item I woke up at six and immediately returned to sleep, which is a choice.
\item I have been listening to CCCiaY, though not today. Prayer has been slipping again, so I should probably try to pray tonight before bed.
\item Today's chapter came up on time, and I need to write Friday's now. I did write the first few hundred words of it for today's chapter, before realizing it was best served as a cliffhanger.
\item Once more, today will be a day without poetry.
\item I wrote and gave a letter today. The friend appreciated it, and I heard that another letter was delivered, and yet another was appreciated as well.
I also addressed around five new ones since my last posting, which means the pile is in no risk of emptying.\footnote{at some point I'm going to worry that I've thought I sent a letter but didn't or that someone will see that I've sent everyone around them a letter but not them and they'll think I don't value them. That is absolutely a problem for J(I don't know if my first name is explicitly associated with this blog yet) when that occurs.}
\end{itemize}

554/121
\end{document}