\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{writers-block-3.html}{Even More Writer's Block}}
First Published: 2022 February 26

\section{Draft 1}
Today as I tried to write this post I felt a different sort of writer's block than the \href{writers-block.html}{other} \href{writers-block-2.html}{two} times that I've had it for the blog.
In both of those cases, I felt as though I had no ideas for what to write.

Today, that does not feel true for me.
I have a couple of ideas for posts I could write, but they don't feel like they belong here.

I read through an \href{silly-putty-and-pitch.html}{old post} where I mentioned that I might want to write a musical piece featuring silly putty.
I'm sure that writing about that could be interesting, but I don't have silly putty with me to write the post.
My group did all get slime for Valentine's Day, so I guess I'm now within easy access of that, though I no longer plan to write that piece.

I thought about writing about the way my life is different than how I think of it.
I never really consciously chose to move away from music in the way that I have, so it makes me really sad that music has become such a\footnote{relatively, I am still in 3 choirs and tend to make music 4-6 days a week for and with other people} small part of my life.
Thoughts have yet to percolate enough in my mind for the coffee of that idea to be worth drinking.\footnote{wow that's a forced metaphor}

I thought about reflecting on the way that I very much did not follow what I said I would do at the end of January, but that should really wait for the end of month reflection.

Finally, I thought about another update on the book I'm writing, but not a lot has really changed there, and I don't really like this blog being a commentary on that writing as I do it.
So, despite the 292\footnote{yes, I waited to write that number until I had the correct count} non-footnoted words, I don't really know what to say here.
I guess I do find it interesting which of my posts get more and less footnoted.
I have been relying less on footnotes in recent posts, which is either a good sign that I am maturing as a writer and no longer feel the need for gimmicks, or a sign that I've been mentally exhausted constantly.
I'm personally really hoping it's the former not the latter.
\end{document}