\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{writing-a-song.html}{Writing a Song}}
First Published: 2018 October 27
\section{Draft 2}
Like I've mentioned before, I\footnote{attempt to} compose.
But, that composition is always alyrical or setting words to music.
But, today on the bus I was playing with the\footnote{because there's only one in my life} ukulele.\footnote{as I always do when given an instrument}
Someone asked me to sing a song about them, so I tried to make one up.

Unsurprisingly, I thought it was better than those around me.
A heckler told me that I needed rhymes.
There I remembered I do horribly under pressure.
But, as I pushed through, I remembered how to think of rhymes and rhythms in real time.

Then the ride ended and we got off the bus.

So, on the journey home, my mind was running with creative song ideas.
Since pop country is the furthest acceptable genre from pure country music allowed in rural Iowa, I decided that I would write in that genre.
The fact that there aren't many genres that you can do\footnote{well, do well at least} with male voice and ukulele helped me come to that conclusion/

As I started writing though, I'd get stuck about one couplet\footnote{two lines} into each set of lyrics.
Every so often I'd end up with a whole verse\footnote{four lines} before realizing that I had nowhere to go with the lyrics.

Finally, I got a verse and chord progression that sounded nice and left me room to grow.\footnote{yay!}
Now all I need is another verse, a chorus, and a second set of verses.
Easy.\footnote{?}
\section{Draft 1}
Like I've mentioned before, I\footnote{attempt to} compose.
And, today on the bus I was playing with the ukulele.\footnote{as I do when given an instrument}
Someone asked me to sing a song about them, so I tried to make one up.

I thought it was ok, until someone yelled that it needed to rhyme.
I then learned that I can't think of rhymes when put under pressure.\footnote{so there goes my rap career}
But, right as the ride ended, my creative flow kicked in.
That meant that my head started thinking of music.

And, since everyone loves a good country song,\footnote{don't lie, \textit{Take Me Home, Country Roads} is the best song around} my mind started thinking of country music.
But, I can't write a \textit{normal} country song.
Despite living in what the Census defines as a \say{rural} area, I didn't have the experiences that a country song tends to need.
I didn't have a dog that I loved and lost, or a heartbreak, or an unhealthy relationship with alcohol or a car.
To rebut the comment about singing anyways, I can't be that fake.
My high school friends would find out.

So, about one couplet\footnote{two lines} into each set of lyrics, I'd get stuck.
Finally, I got a whole verse out.
Now I'm stuck.
But, I figured out the melody,\footnote{and wrote it down, which is more important} which is good because I tend to forget melodies.
So, I've got four lines, a melody, and a chord progression.
If I can just get four more lines and a chorus, I'm cooking.
\end{document}