\documentclass[12pt]{article}[titlepage]
\newcommand{\say}[1]{``#1''}
\newcommand{\nsay}[1]{`#1'}
\usepackage{endnotes}
\newcommand{\1}{\={a}}
\newcommand{\2}{\={e}}
\newcommand{\3}{\={\i}}
\newcommand{\4}{\=o}
\newcommand{\5}{\=u}
\newcommand{\6}{\={A}}
\newcommand{\B}{\backslash{}}
\renewcommand{\,}{\textsuperscript{,}}
\usepackage{setspace}
\usepackage{tipa}
\usepackage{hyperref}
\begin{document}
\doublespacing
\section{\href{writing-3.html}{On Writing (Redux)}}
First Published: 2023 April 9

\section{Draft 1}
\href{writing-2.html}{Fourteen months later}, another musing on writing.
This month I've set the goal of writing more each day.
In retrospect, setting that goal on the third of the month, when your first two days were 2494 and 3087 words may not have been the best choice.
But, today is also Easter.\footnote{Read: my schedule today was Mass, calling a friend for 90 minutes, and then spending from 1pm to 9 pm with another friend and their family. It was a great day, but oh boy did I do absolutely nothing approaching work today (which, to be fair, is an explicit goal that I've been told I should have on Sundays).}
\footnote{I kind of think that my footnotes might be longer than the actual text of this post (especially given this one), but they don't explicitly relate to writing, so it's fine.}

I realized that there's value in living a life outside of just writing for the sake of writing.
So, while the goal continues, I'm going to be taking Sundays off.
Tomorrow I will find the time to write 3600 words\footnote{of varying quality.}.
\end{document}